### 2017-03-15 paper/paper.tex
Added paper

\input{config.tex}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}
\usepackage{pseudocode}

\addbibresource{sample.bib}

\begin{document}

\begin{titlepage}
	\centering
	\vspace{2cm}
	{\Huge Analysis of voting systems: What should I call it? \par}
	\vspace{0.6cm}
	{\LARGE Adrian Salamon\par}

	\vspace{0.6cm}
 	{\Large Kungsholmens gymnasium\par}
	\vspace{0.4cm}
	{\large Senior thesis\par}
	\vspace{0.6cm}
	\includegraphics[width=0.3\textwidth]{kg}\par\vspace{1cm}
	\vspace{4cm}
	\vfill
	Supervised by: \par
	Maja Kankaanranta

	\vfill

% Bottom of the page
	{\large \today\par}
\end{titlepage}

\pagebreak

\begin{abstract}
The abstract text goes here.
\end{abstract}

\pagebreak

\tableofcontents

\pagebreak

\section{Introduction}
\subsection{Background}
Taking a collective decision as a population is difficult. To solve this issue, voting systems with defined rules are used. They are used to show common preferences within a population, for example what politician a population wants to see elected. Several types of systems have been designed and there are a myriad of variations of those systems. They range from simple methods such as “most votes win” to complex processes that can only be practically carried out by a computer. However, practically all voting systems are algorithmic in nature, which makes them interesting to study for both Computer Scientists and Mathematicians. When deciding on what systems that shall be used, it is useful to know what differences and similarities they have.
\subsection{Purpouse}
The purpose of this essay is to evaluate differences and similarities in terms of election results in three different voting systems: Single Transferable Vote (STV), First-Past-The-Post (FPTP) and the Schulze Method. I will only be investigating and discussing differences and similarities in the results of the methods, not touching on how practically feasible the systems are in an actual election.
\pagebreak
\section{Theory}
Theory will be here some day
\section{Methodology}
Methodology here
All voting methods have been implemented in Typescript – mostly due to the author having previous experience with JavaScript. Typescript is a superset of JavaScript and compiles down to it. Typescript has some extra features compared to JavaScript but most importantly it has optional static type checking. Here is some example code in typescript:
\begin{lstlisting}
let helloWorld: string = 'Hello World' // This is a comment
console.log(helloWorld)
\end{lstlisting}
\subsection{Modeling test data}

\pagebreak
\section{Specification of voting methods}
This paper compares the results of theese voting methods
\subsection{First-past-the-post}
\subsubsection{Description}
The first-past-the-post voting method is a method desiged for electing one or several candidates out of a set of candidates. In a first-past-the-post election the N candidates with most votes get elected.
\subsubsection{Justification}
The method is simple and can easily be understood. The first-past-the-post method is widely used in for example the United Kingdom and United States. Comparisons with this method can also be easily made.
\subsubsection{Pseudocode}
let $V$ be the set of votes with $V_{i}$ meaning votes for candidate $i$ \\
let $N$ be number of candidates to be elected \\
sort $V$ based on $V_{i}$\\
slice $V$ between $0$ and $N$
\subsubsection{Implementation}
The first-past-the-post program is implemented in a single file. It takes the following inputs:
\begin{lstlisting}
ballots: Array<Array<number>> // Ex. [[0,1,2],[1,0,2],...]
seats: number // Ex. 2
\end{lstlisting}
The ballot data is first mapped to only include first prefrences. Then the algorithm loops over the ballots and adds the votes for each candidate together:
\begin{lstlisting}
let results: Array<Result> = []
// Loops over prefrences and adds/increments result
for (var i = 0; i < firstPrefrences.length; i++) {
    // Finds index in results array of candidate at i
    let index = results.findIndex(obj => obj.cand === firstPrefrences[i])
    // If candidate is not added to results
    if (index === -1) {
        results.push({ cand: firstPrefrences[i], votes: 1 })
    } else {
        // Increment count if already added in results
        results[index].votes += 1;
    }
}
\end{lstlisting}
The results array is sorted and sliced to only include the $N$ candidates with most votes:
\begin{lstlisting}
// Sorts array by number of votes
results.sort((a, b) => {
    if (a.votes > b.votes) {
        return -1
    } else if (a.votes < b.votes) {
        return 1
    }
    return 0
})
// Gets the first elements in the sorted array i.e the winners
let winners = results.slice(0, seats)
// Returns array of winners
return winners.map(cand => cand.cand)
\end{lstlisting}
\subsection{Single transferable vote}
\subsubsection{Description}
\subsubsection{Justification}
\subsubsection{Pseudocode}
\subsubsection{Implementation}
\subsection{Schulze}
\subsubsection{Description}
\subsubsection{Justification}
\subsubsection{Pseudocode}
\subsubsection{Implementation}

\section{Evaluation of methods}
\subsection{Sample I}
\subsection{Sample II}
\subsection{Sample III}

\section{Conclusion}

%\subsection{ Heading Here}
%This is some code.
%\lstinputlisting[language=JavaScript]{code/examples/example.js}

%\section{Conclusion}
%Write your conclusion here. And here is a citation:
%\textcite{sigfridsson2}

%And another one here (\textcite{sigfridsson})

%\section{Source code}
%\lstinputlisting[language=JavaScript]{code/test.js}

\pagebreak

\printbibliography

\section{Appendix}
First-past-the-post program
\lstinputlisting[language=JavaScript]{code/index.ts}

\end{document}

### 2017-03-15 generator/index.ts
Added check

@@ -9,7 +9,7 @@ import { createAllBallots } from './ballots'
 export default function generateInput(ideologies: Array<Ideology>, numberOfParties: number, numberOfBallots: number): Array<Array<number>> {
     
     const parties = createParties(numberOfParties, ideologies)
-    
+
     const ideologyProbabilities: Array<IdeologyWithProbabilities> = assignProbabilityToIdeology(ideologies, parties)
     
     const result = createAllBallots(ideologies, ideologyProbabilities, numberOfBallots)

### 2017-03-15 generator/parties.ts

@@ -9,13 +9,15 @@ export function createParties(numberOfParties: number, ideologies: Array<Ideolog
 
     let parties: Array<Party> = []
     const initialNumberOfParties = numberOfParties
-
     // Loops while not every party has an ideology
     while (numberOfParties > 0) {
         // Loops though all future party indexes
         for (let partyIndex = 0; partyIndex < initialNumberOfParties; partyIndex++) {
+
             // Loops through all ideologies
             for (let ideologyIndex = 0; ideologyIndex < tempIdeologies.length; ideologyIndex++) {
+                if(numberOfParties <= 0)
+                    break
                 // Current ideology in loop
                 const ideology = tempIdeologies[ideologyIndex]
                 //Gets the number of parties that should belong to an ideology

### 2017-03-15 schulze/index.ts

@@ -36,6 +36,7 @@ function getPairs(ballots: Array<Array<number>>): Array<Pair> {
         }
 
     }
+  
     return result
 }
 
@@ -67,6 +68,18 @@ function getStrongestPath(a: number, b: number, strongestPaths: Array<Pair>): nu
 }
 
 function getResult(strongestPaths: Array<Pair>, seats: number, c: number): Array<number> {
+    /*
+    let fullResult: Array<Object> = []
+    for (var i = 0; i < c; i++) {
+        for (var j = 0; j < c; j++) {
+            fullResult.push({a:i,b:j, val: getStrongestPath(i, j, strongestPaths) })
+        }
+    }
+    var fs = require('fs')
+    fs.writeFile('res.json', JSON.stringify(fullResult))
+    */
+    
+    
     let wins: Object = {}
     // Loops through strongest paths and adds results onto the wins object
     for (var i = 0; i < c; i++) {

### 2017-03-15 test.ts

@@ -7,8 +7,8 @@ import schulze from './schulze'
 
 const seats = 3;
 
-const parties = 12
-const ballots = 1200
+const parties = 9
+const ballots = 500
 
 const ideologies: Array<Ideology> = [{
     size: 0.2,
@@ -24,9 +24,18 @@ const ideologies: Array<Ideology> = [{
     ideologyPower: 0.7,
 }]
 
-let input = createInput(ideologies, parties, ballots)
 
-let results = {stv: stv(input, seats).winners, fptp: fptp(input, seats), schulze: schulze(input, seats) }
+let results: Array<Object> = []
 
+for (var i = 0; i <= 100; i++) {
+    console.log(i)
+    let input = createInput(ideologies, parties, ballots)
+    results.push({stv: stv(input, seats).winners, fptp: fptp(input, seats), schulze: schulze(input, seats)})
+}
+
+
+ /*
+ let input = createInput(ideologies, parties, ballots)
+ results.push({stv: stv(input, seats).winners, fptp: fptp(input, seats), schulze: schulze(input, seats)})
+*/
 console.log(results)
-// Hello worlds

### 2017-03-18 fptp/index.ts
Changed array type syntax

@@ -1,19 +1,17 @@
-let input = [[0, 2, 3, 1, 5, 4, 6, 7], [2, 1, 0, 3, 5, 7, 6, 4], [5, 0, 3, 1, 2, 4, 6, 7], [0, 3, 4, 2, 1, 5, 6, 7], [0, 3, 2, 1, 5, 4, 6, 7], [3, 0, 6, 2, 1, 4, 5, 7], [0, 2, 3, 1, 5, 4, 6, 7], [1, 3, 2, 0, 7, 5, 6, 4], [0, 1, 3, 2, 4, 5, 6, 7], [5, 3, 0, 2, 7, 1, 6, 4], [0, 2, 3, 1, 5, 6, 4, 7], [3, 0, 2, 1, 6, 5, 7, 4], [3, 0, 2, 6, 1, 5, 4, 7], [1, 0, 3, 6, 5, 2, 4, 7], [0, 2, 1, 3, 4, 5, 7, 6], [3, 2, 0, 5, 1, 6, 7, 4], [3, 0, 1, 2, 5, 6, 4, 7], [6, 3, 2, 1, 0, 7, 5, 4], [0, 6, 5, 2, 3, 1, 4, 7], [0, 2, 3, 5, 1, 4, 7, 6], [0, 3, 5, 2, 1, 7, 6, 4], [0, 2, 1, 3, 5, 4, 6, 7], [3, 0, 2, 5, 1, 6, 4, 7], [3, 0, 5, 6, 1, 2, 7, 4], [2, 0, 3, 1, 7, 5, 4, 6], [0, 2, 5, 1, 3, 6, 7, 4], [1, 0, 2, 3, 5, 7, 6, 4], [1, 3, 0, 2, 6, 5, 7, 4], [3, 0, 2, 5, 1, 6, 7, 4], [0, 3, 2, 1, 5, 4, 6, 7], [2, 5, 0, 3, 1, 4, 7, 6], [3, 2, 0, 1, 4, 5, 6, 7], [0, 1, 3, 2, 6, 5, 4, 7], [0, 3, 1, 2, 5, 7, 4, 6], [0, 5, 3, 1, 2, 4, 7, 6], [0, 5, 2, 4, 3, 6, 1, 7], [0, 3, 2, 1, 6, 5, 4, 7], [0, 3, 2, 1, 5, 6, 7, 4], [3, 0, 2, 1, 5, 6, 4, 7], [0, 1
[…]

### 2017-03-18 generator/ballots.ts

@@ -2,9 +2,9 @@ import { Ideology, IdeologyWithProbabilities } from './interfaces'
 
 
 // Generates the ballots, essentially the output of the program
-export function generateBallots(numberOfBallots: number, prob: Array<number>, parties: Array<number>): Array<Array<number>> {
+export function generateBallots(numberOfBallots: number, prob: number[], parties: number[]): number[][] {
     // Create temp array combining probability and possib
-    let temp: Array<Array<number>> = []
+    let temp: number[][] = []
     for (var i = 0; i < parties.length; i++) {
         temp.push([prob[i], parties[i]])
     }
@@ -27,7 +27,7 @@ export function generateBallots(numberOfBallots: number, prob: Array<number>, pa
         return val
     })
 
-    let ballots: Array<Array<number>> = []
+    let ballots: number[][] = []
 
     for (var i = 0; i < numberOfBallots; i++) {
         const votes = distributeVotes(temp)
@@ -39,8 +39,8 @@ export function generateBallots(numberOfBallots: number, prob: Array<number>, pa
     return ballots
 }
 
-export function createAllBallots(ideologies: Array<Ideology>, ideologyProbabilities: Array<IdeologyWithProbabilities>, ballots: number): Array<Array<number>> {
-    let result: Array<Array<number>> = []
+export function createAllBallots(ideologies: Ideology[], ideologyProbabilities: IdeologyWithProbabilities[], ballots: number): number[][] {
+    let result: number[][] = []
 
     for (var i = 0; i < ideologies.length; i++) {
         const ideology = ideologies[i]
@@ -55,10 +55,10 @@ export function createAllBallots(ideologies: Array<Ideology>, ideologyProbabilit
 
 
 
-function distributeVotes(temp: Array<Array<number>>): Array<number> {
+function distributeVotes(temp: number[][]): number[] {
     let parties = [ ...temp ]
     let index = parties.length
-    let result: Array<number> = []
+    let result: number[] = []
 
     while (index > 0) {
         const rand = Math.random()

### 2017-03-18 generator/index.ts

@@ -6,11 +6,11 @@ import { Ideology, IdeologyWithProbabilities } from './interfaces'
 import { createParties, assignProbabilityToIdeology } from './parties'
 import { createAllBallots } from './ballots'
 
-export default function generateInput(ideologies: Array<Ideology>, numberOfParties: number, numberOfBallots: number): Array<Array<number>> {
+export default function generateInput(ideologies: Ideology[], numberOfParties: number, numberOfBallots: number): number[][] {
     
     const parties = createParties(numberOfParties, ideologies)
 
-    const ideologyProbabilities: Array<IdeologyWithProbabilities> = assignProbabilityToIdeology(ideologies, parties)
+    const ideologyProbabilities: IdeologyWithProbabilities[] = assignProbabilityToIdeology(ideologies, parties)
     
     const result = createAllBallots(ideologies, ideologyProbabilities, numberOfBallots)
 

### 2017-03-18 generator/interfaces.ts

@@ -13,8 +13,8 @@ export interface IdeologyWithParties {
 }
 
 export interface IdeologyWithProbabilities {
-    probabilities: Array<number>,
-    parties: Array<number>
+    probabilities: number[],
+    parties: number[]
 }
 
 export interface Party {

### 2017-03-18 generator/parties.ts

@@ -1,13 +1,13 @@
 import {Ideology, IdeologyWithProbabilities, IdeologyWithParties, Party} from './interfaces'
 
 // Creates the parties and assigns them an ideology based on their relative sizes.
-export function createParties(numberOfParties: number, ideologies: Array<Ideology>): Array<Party> {
+export function createParties(numberOfParties: number, ideologies: Ideology[]): Party[] {
 
-    const tempIdeologies: Array<IdeologyWithParties> = ideologies.map((ideology) => {
+    const tempIdeologies: IdeologyWithParties[] = ideologies.map((ideology) => {
         return Object.assign({}, ideology, { numberOfParties: 0 })
     })
 
-    let parties: Array<Party> = []
+    let parties: Party[] = []
     const initialNumberOfParties = numberOfParties
     // Loops while not every party has an ideology
     while (numberOfParties > 0) {
@@ -39,8 +39,8 @@ export function createParties(numberOfParties: number, ideologies: Array<Ideolog
 
 
 // Assigns the probability of the voters within an ideology
-export function assignProbabilityToIdeology(ideologies: Array<Ideology>, parties: Array<Party>): Array<IdeologyWithProbabilities> {
-    let result: Array<IdeologyWithProbabilities> = []
+export function assignProbabilityToIdeology(ideologies: Ideology[], parties: Party[]): IdeologyWithProbabilities[] {
+    let result: IdeologyWithProbabilities[] = []
 
     // Loops through each ideology
     for (var ideologyIndex = 0; ideologyIndex < ideologies.length; ideologyIndex++) {
@@ -70,7 +70,7 @@ export function assignProbabilityToIdeology(ideologies: Array<Ideology>, parties
 
 
 // Assigns relative sizes to all parties based on their ideologies
-function assignPartySizes(parties: Array<Party>, ideologies: Array<IdeologyWithParties>): Array<Party> {
+function assignPartySizes(parties: Party[], ideologies: IdeologyWithParties[]): Party[] {
     // Loops through all ideologies
     for (var ideologyIndex = 0; ideologyIndex < ideologies.length; ideologyIndex++) {
         const ideology = ideologies[ideologyIndex]
@@ -103,14 +103,14 @@ function fy (y: number, k: number): number {
 }
 
 // Normalizes an array of numbers so that the sum is 1
-function normalize(array: Array<number | undefined>): Array<number> {
+function normalize(array: (number | undefined)[]): number[] {
[…]

### 2017-03-18 schulze/index.ts

@@ -1,4 +1,5 @@
 //let fakeData = [[0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [2, 0, 1, 4, 3], [2, 0, 1, 4, 3], [2, 0, 1, 4, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 1, 0, 3, 4], [2, 1, 0, 3, 4], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2]]
+var fs = require('fs')
 
 interface Pair {
     a: number,
@@ -7,13 +8,13 @@ interface Pair {
 }
 
 // Gets the pairwise comparison between all candidates and the number of prefrences. Ex. 120 ballots prefer a > b
-function getPairs(ballots: Array<Array<number>>): Array<Pair> {
-    let result: Array<Pair> = []
+function getPairs(ballots: number[][]): Pair[] {
+    let result: Pair[] = []
     // Loops throug all ballots
     for (var k = 0; k < ballots.length; k++) {
         var ballot = ballots[k];
         // Temp array that stores which candidates are prefered over current candidate in the loop
-        let preferred: Array<number> = []
+        let preferred: number[] = []
[…]

### 2017-03-18 stv/candidate.ts

@@ -2,7 +2,7 @@
 export default class CandidateNode {
     public cand: number
     public count: number
-    public children: Array<CandidateNode>
+    public children: CandidateNode[]
 
     constructor(cand: number, count: number) {
         this.cand = cand;
@@ -45,7 +45,7 @@ export default class CandidateNode {
 }
 
 // Combines children for two arrays at a specific child and returns a node
-function addChildren(aChildren: Array<CandidateNode>, bChildren: Array<CandidateNode>, child: number): CandidateNode {
+function addChildren(aChildren: CandidateNode[], bChildren: CandidateNode[], child: number): CandidateNode {
     // A has the child and B has the child
     const aHas = aChildren.some(obj => obj.cand === child)
     const bHas = bChildren.some(obj => obj.cand === child)

### 2017-03-18 stv/election.ts

@@ -1,24 +1,27 @@
 import { buildTree, eliminate, isSurplus, transferSurplus } from './tree'
 
 interface Result {
-    log: Array<string>,
-    winners: Array<number>
+    log: string[],
+    winners: number[]
 }
 
 // Calculates election result in an STV election
-export function runElection(input: Array<Array<number>>, seats: number): Result {
-    let winners: Array<number> = []
-    let log: Array<string> = []
+export function runElection(input: number[][], seats: number): Result {
+    let winners: number[] = []
+    let log: string[] = []
     // Droop quota
     const quota =  Math.floor((input.length / (seats + 1)) + 1)
     log.push(`Quota: ${quota}`)
     // Build the base tree based in input
     let tree = buildTree(input)
 
+    var fs = require('fs')
+    fs.writeFile('tree.json', JSON.stringify(tree))
+
     // Loop through while all seats are not filled
     while(seats > winners.length) {
         // Check for winners
-        let newWinners: Array<number> = []
+        let newWinners: number[] = []
         // Loops through tree
         for (var i = 0; i < tree.length; i++) {
             const cand = tree[i]
@@ -35,7 +38,7 @@ export function runElection(input: Array<Array<number>>, seats: number): Result 
             continue
         }
         // Check for surplus
-        let hadSurplus: Array<number> = []
+        let hadSurplus: number[] = []
         // Loop while there is a surplus of votes for a candidate
         while(isSurplus(tree, quota)) {
             // Loop through tree 

### 2017-03-18 stv/tree.ts

@@ -1,13 +1,13 @@
 import CandidateNode from './candidate'
 
 // Builds the initial tree structure
-export function buildTree(ballots: Array<Array<number>>): Array<CandidateNode> {
+export function buildTree(ballots: number[][]): CandidateNode[] {
 
     // Reduces the ballots into a tree via the addBallot function
     const trees = ballots.reduce(addBallot, [])
 
     // Reducer function for the ballots
-    function addBallot(tree: Array<CandidateNode>, ballot: Array<number>) {
+    function addBallot(tree: CandidateNode[], ballot: number[]) {
         let level = tree
 
         // For each vote in ballot, call the addVote function
@@ -34,12 +34,12 @@ export function buildTree(ballots: Array<Array<number>>): Array<CandidateNode> {
 }
 
 // Checks if candidate has a node already at a level.
-function hasCandidateNode(level: Array<CandidateNode>, cand: number): boolean {
+function hasCandidateNode(level: CandidateNode[], cand: number): boolean {
     return level.some(obj => obj.cand === cand)
 }
 
 // Eliminates a candidate, returns a new tree.
-export function eliminate(lowestRanked: number, tree: Array<CandidateNode>, winners: Array<number>): Array<CandidateNode> {
+export function eliminate(lowestRanked: number, tree: CandidateNode[], winners: number[]): CandidateNode[] {
     // New tree
     let newTree = [...tree]
     // Save the children for transfering
@@ -51,14 +51,14 @@ export function eliminate(lowestRanked: number, tree: Array<CandidateNode>, winn
 }
 
 // Checks if any candidate has surplus votes
-export function isSurplus(tree: Array<CandidateNode>, quota: number): boolean {
+export function isSurplus(tree: CandidateNode[], quota: number): boolean {
     // Maps array and compares count to quota and then reduces to find if any comparison retured true.
     let surplus = tree.map(cand => (cand.count > quota)).reduce((a,b) => a || b)
     return surplus
 }
 
 // Transfers the surplus from a candidate. Returns a new tree.
-export function transferSurplus(candNumber: number, tree: Array<CandidateNode>, quota: number, winners: Array<number>): Array<CandidateNode> {
+export function transferSurplus(candNumber: number, tree: CandidateNode[], quota: number, winners: number[]): CandidateNode[] {
     // Find index of candidate in tree
     let candIndex = tree.findIndex(cand => cand.cand === candNumber)
[…]

### 2017-03-18 test.ts

@@ -2,15 +2,15 @@ import { Ideology } from './generator/interfaces'
 import createInput from './generator'
 
 import fptp from './fptp'
-import { runElection as stv} from './stv'
+import { runElection as stv } from './stv'
 import schulze from './schulze'
 
 const seats = 3;
 
-const parties = 9
-const ballots = 500
+const parties = 7
+const ballots = 100
 
-const ideologies: Array<Ideology> = [{
+const ideologies: Ideology[] = [{
     size: 0.2,
     partyPower: 0.2,
     ideologyPower: 1.2
@@ -25,17 +25,130 @@ const ideologies: Array<Ideology> = [{
 }]
 
 
-let results: Array<Object> = []
+let results: Array<{ stv: number[], fptp: number[], schulze: number[], }> = []
+const input = createInput(ideologies, parties, ballots)
 
-for (var i = 0; i <= 100; i++) {
-    console.log(i)
-    let input = createInput(ideologies, parties, ballots)
-    results.push({stv: stv(input, seats).winners, fptp: fptp(input, seats), schulze: schulze(input, seats)})
+for (var j = 0; j <= 0; j++) {
+    console.log(j)
[…]

### 2017-03-18 paper/paper.tex
Wrote some stuff

@@
 \usepackage{hyperref}
+\usepackage{float}
+\usepackage{amsmath}
+\usepackage{mathtools}
+
+\newcommand\tab[1][1cm]{\hspace*{#1}}
+
 \hypersetup{
@@
 \usepackage{pseudocode}
+
+\usepackage{xcolor}
+\usepackage{tikz}
+\usepackage{pgfplots}
+\pgfplotsset{compat=1.14}
 
@@
 The first-past-the-post voting method is a method desiged for electing one or several candidates out of a set of candidates.
+Each voter has one (1) vote which may be allocated to any candidate.
 In a first-past-the-post election the N candidates with most votes get elected.
@@
 \subsubsection{Pseudocode}
-let $V$ be the set of votes with $V_{i}$ meaning votes for candidate $i$ \\
+let $V$ be the set of votes with $V_{i}$ being the number of votes for candidate $i$ \\
 let $N$ be number of candidates to be elected \\
@@
 \begin{lstlisting}
-ballots: Array<Array<number>> // Ex. [[0,1,2],[1,0,2],...]
+ballots: number[][] // Ex. [[0,1,2],[1,0,2],...]
 seats: number // Ex. 2
 \end{lstlisting}
-The ballot data is first mapped to only include first prefrences. Then the algorithm loops over the ballots and adds the votes for each candidate together:
+The ballot data is first mapped to only include first prefrences. Then the algorithm loops over the ballots and gets the sum of votes for each candidate:
 \begin{lstlisting}
-let results: Array<Result> = []
+let results: Result[] = []
 // Loops over prefrences and adds/increments result
@@
 \subsubsection{Description}
+The Single Transferable Vote method is a more complicated algorithm than the first-past-the-post method.
+Voters are given ballots where they are supposed to rank candidates in order.
+The specific rules for if you need to rank all candidates or rank several candidates at the same value not can vary.
+For the sake of simplicity, in this implementation, all candidates must be ranked at unique and linear values.
+A ballot may look like this:
+\begin{figure}[H]
+	\centering
+	\includegraphics[height=140px]{ballot}
+	\caption{Sample STV ballot}
+	\label{STV ballot}
+\end{figure}
+This means that there is more data availible for detrermining the result of the election which the method can take advantage of.
+Votes are, if needed, transfered between choices within a ballot, hence the name Single Transferable Vote.
+The method relies on the concept of a quota, the number of votes you need to be elected.
+The Droop-Quota, defined as $(\frac{\text{total valid poll}}{\text{seats} + 1})+1$, is often used.
+If a candidate recieves equal or more votes than the quota, he/she is elected.
+If the number of votes exxeed the quota, a fraction of the votes are transfered to the next choice on the ballots that voted for the elected candidate.
+This process is repeated until there are no candidates with more votes than the quota.
+If there still are seats yet to be filled, the candidate with fewest votes is eliminated and his/her votes are transfered to the next choice on those ballots.
+This process is repeated until all seats are filled.
+The process can become quite complex with many ballots and transfering fractional votes.
+In order to resolve large scale elections, a computer in essential.
 \subsubsection{Justification}
+STV is an established voting method in use in several countries.
+It is used for parlimentary elections in Ireland, Malta and Australia as well as being used in local and regional elections across the world.
 \subsubsection{Pseudocode}
+let $quota$ be the quota \\
+let $seats$ be the number of seats \\
+let $winners$ be the list of elected candidates \\
+let $votes$ be the set of votes with $votes_{i}$ signinfying votes for candidate $i$\\\\
+while $\left\vert{winners}\right\vert < seats$\\
+\tab if any candidate $i \notin winners$ and $votes_{i} \geq quota$ \\
+\tab\tab add $i$ to $winners$ \\
+\tab\tab continue \\
+\tab end if \\
+\tab if any candidate $i$ where $votes_{i} > quota$\\
+\tab\tab multiply $votes_{i}$ with $(1 - \frac{\text{surplus votes}_{i}}{votes_{i}})$ \\
+\tab\tab multiply next prefrencences for $votes_{i}$ with $\frac{\text{surplus votes}_{i}}{votes_{i}}$ and \\ \tab\tab distribute into $votes$\\
+\tab\tab continue \\
+\tab end if \\
+\tab if $\left\vert{votes}\right\vert = seats$ \\
+\tab\tab add all $votes \notin winners$ to $winners$ \\
+\tab\tab continue \\
+\tab end if \\
+\tab $k \coloneqq$ index of smallest $votes_{i}$ \\
+\tab eliminate $votes_{k}$ and distribute all next-prefrence votes for candidate $k$ \tab into $votes$\\
+end while
 \subsubsection{Implementation}
+The single transferable vote algorithm uses a tree structure to represent the state of the election.
+Every candidate is a top-level node with an attribute showing the number of current votes for the candidate.
+Each node has child nodes that show the next-prefrences of the voters for a particular candidate.
+By multiplying and merging branches it is simple to transfer votes.
+\begin{figure}
+	\centering
+	\includegraphics[height=200px]{Tree}
+	\caption{This is a tree}
+	\label{Tree structure}
+\end{figure}
+
 \subsection{Schulze}
@@
 
+\begin{figure}
+	\centering
+	\begin{tikzpicture}
+		\begin{axis}[
+			ybar stacked,
+			width = 0.9\textwidth,
+			height = 0.5\textwidth,
+			cycle list = {black!80,black!50,black!20},
+			legend style={at={(0.5,-0.25)},
+			anchor=north,legend columns=-1},
+      x tick style = transparent,
+			ylabel = {Elections won},
+			xlabel = {Party},
+			ymajorgrids = true,
+			every axis plot/.append style={fill,draw=none,no markers},
+      ymin = 0
+      ]
+			\addplot coordinates
+			{(0, 1)(1, 1)(2, 1)(3, 0)(4, 0)(5, 0)(6, 0)};
+			\addplot coordinates
+			{(0, 1)(1, 1)(2, 1)(3, 0)(4, 0)(5, 0)(6, 0)};
+			\addplot coordinates
+			{(0, 0)(1, 1)(2, 1)(3, 0)(4, 1)(5, 0)(6, 0)};
+			\legend{FPTP, STV, Schulze}
+		\end{axis}
+	\end{tikzpicture}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\begin{tikzpicture}
+		\begin{axis}[
+			ybar,
+			width = 0.9\textwidth,
+			height = 0.5\textwidth,
+			legend style={at={(0.5,-0.25)},
+			anchor=north,legend columns=-1},
+      x tick style = transparent,
+			ylabel = {First prefrence votes},
+			xlabel = {Party},
+			ymajorgrids = true,
+			every axis plot/.append style={fill,draw=none,no markers},
+      ymin = 0
+      ]
+			\addplot coordinates
+			{(0, 17)(1, 36)(2, 32)(4, 9)(5, 5)(6, 1)};
+		\end{axis}
+	\end{tikzpicture}
+\end{figure}
+
 \printbibliography

### 2017-03-18 schulze/index.ts
Complete refactor of schulze program

@@ -1,15 +1,68 @@
 //let fakeData = [[0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [2, 0, 1, 4, 3], [2, 0, 1, 4, 3], [2, 0, 1, 4, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 1, 0, 3, 4], [2, 1, 0, 3, 4], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2]]
-var fs = require('fs')
 
-interface Pair {
-    a: number,
-    b: number,
-    num: number
+interface PairMap {
+    [key: number]: {
+        [key: number]: number
+    }
+}
+
+// Calculates  result in a Schulze method election
+export default function calculateResult(input: number[][], seats: number): number[] {
+    // Gets the pairs of candidates and their count
+    // Ex 120 votes prefer a > b
+
+    // d[i][j] gives the number of ballots prefering i > j
+    let d: PairMap = getPairs(input)
+    // o[i][j] stores the strongest path between i and j
+    let p: PairMap = {}
+    // Number of candidates
+    let c = input[0].length
+
+    // Fills p with a bunch of zeroes
[…]

### 2017-03-18 paper/paper.tex
Wrote more on schulze

@@
 \usepackage{pseudocode}
-
-\usepackage{xcolor}
 \usepackage{tikz}
@@
 \subsection{Modeling test data}
-
 \pagebreak
@@
 \subsubsection{Pseudocode}
+\label{Stv psuedocode}
 let $quota$ be the quota \\
@@
 let $winners$ be the list of elected candidates \\
-let $votes$ be the set of votes with $votes_{i}$ signinfying votes for candidate $i$\\\\
+let $votes$ be the set of votes with $votes_{i}$ signinfying votes for candidate $i$\\
 while $\left\vert{winners}\right\vert < seats$\\
@@
 Every candidate is a top-level node with an attribute showing the number of current votes for the candidate.
-Each node has child nodes that show the next-prefrences of the voters for a particular candidate.
-By multiplying and merging branches it is simple to transfer votes.
-\begin{figure}
+Each node has child nodes that show the next prefrences of the voters for that particular candidate, see figure \ref{Tree structure}.
+It is easy to manipulate branches via recursion.
+Merging and multiplying branches is used when transfering votes from one candidate node to another.
+A candidate node is a Typescript class.
+It can be found in the \texttt{stv/candidate.ts} file and has the following properties and functions:
+\lstinputlisting[language=JavaScript]{code/candidateNode.ts}
+\begin{figure}[H]
 	\centering
 	\includegraphics[height=200px]{Tree}
-	\caption{This is a tree}
+	\caption{Simplified and shortened version of the tree structure. Each candidate is a top-level node with children, signifying the prefrences of the voters for that candidate.}
 	\label{Tree structure}
 \end{figure}
+With those functions, we can recursively manipulate branches and trees.
+In order to distribute the child nodes of an eliminated candidate, we just need to add each of those nodes to the corresponding top level nodes.
+In order to transfer surplus votes, we can multiply each child node with a factor and then distribute those nodes onto the top level nodes.
+The full source code for the tree manipuation functions can be found in \texttt{stv/tree.ts}.
+
+The input into the algorithm is a set of ballots.
+A ballot consists of an ordered list of candidates according to prefrence.
+Every candidate is represented by an integer.
+The input data is converted into the tree structure via the \texttt{buildTree} function.
+It can also be found in the \texttt{stv/tree.ts} file.
+
+The main procces of the program is found in the \texttt{stv/election.ts} file and runs the process defined in the psuedocode on page \pageref{Stv psuedocode}.
+The program takes the input defined above and a number representing the number of seats to elect as inputs.
+The process outputs an array of winning candidates as well as a log file.
 
@@
 \subsubsection{Description}
+The Schulze Method is a method used mainly to determine results in a single-winner election but can also be used to provide rankings and elect multiple candidates in a single election.
+Ballots are identical to those of the single transferable vote, see figure \ref{STV ballot} on page \pageref{STV ballot}.
+The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate wins.
+As mentioned, this method relies on comparing the prefrences of every candidate to one another as shown in table \ref{Pairwise comparison matrix}.
+If there is a condorcet winner the process is simple: declare the condorcet winner a winner and run another iteration without that candidate.
+Repeat this process until all seats are filled.
+However, there can be condorcet ties, where there is no condorcet winner.
+There are multiple ways of resolving the tie, one of them being the Schulze Method.
+
+The Schulze Method resolves ties by investigating possible paths between candidates.
+For example, if out of a total of 50 ballots 30 ballots prefer $B>A$, 28 ballots prefer $A>C$ and 27 ballots prefer $C>B$, a path from $A$ to $B$ can be created by going $A \rightarrow C \rightarrow B$.
+The path is said to have the $strength$ of the weakest link in the path.
+In this example, the path strenght between A and B is 27 due to the link between $C$ and $B$ having a strenght of 27.
+There may be several paths between two candidates and the goal of the process is to find the strongest path between any candidate $A$ and $B$, written as $p[A,B]$.
+By finding the strongest path between all nodes a result can be obtained where $p[X,Y] \geq p[Y,X]$ wich means that candidate $X$ wins.
+The Shulze Method also provides a linear ranking between all candidates, for example that $E > B > A > C > D$.
+By selecting the $N$ top candidates you can use the method for a multi-seat election.
+As the process can become very complex as the number of candidates grow, a computer is needed to resolve large elections.
+
+The difficult problem in this method is finding the strongest path between candidates.
+The problem is called the widest path problem in graph theory.
+An efficent and relatively simple way to compute this problem is via the Floyd-Warshall algorithm which is used in the implementation.
+See \ref{Schulze psuedocode} for the full algorithm.
+
+\begin{table}[H]
+\centering
+\begin{tabular}{l|c|c|c|c|c|}
+\cline{2-6}
+ & \multicolumn{1}{l|}{A} & \multicolumn{1}{l|}{B} & \multicolumn{1}{l|}{C} & \multicolumn{1}{l|}{D} & \multicolumn{1}{l|}{E} \\ \hline
+\multicolumn{1}{|l|}{A} & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}17 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{DDFFDD}35 & \cellcolor[HTML]{DDFFDD}30 \\ \hline
+\multicolumn{1}{|l|}{B} & \cellcolor[HTML]{DDFFDD}33 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}24 & \cellcolor[HTML]{DDFFDD}47 & \cellcolor[HTML]{DDFFDD}36 \\ \hline
+\multicolumn{1}{|l|}{C} & \cellcolor[HTML]{DDFFDD}36 & \cellcolor[HTML]{DDFFDD}26 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{DDFFDD}40 & \cellcolor[HTML]{DDFFDD}42 \\ \hline
+\multicolumn{1}{|l|}{D} & \cellcolor[HTML]{FFDDDD}15 & \cellcolor[HTML]{FFDDDD}3 & \cellcolor[HTML]{FFDDDD}10 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}18 \\ \hline
+\multicolumn{1}{|l|}{E} & \cellcolor[HTML]{FFDDDD}20 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{FFDDDD}8 & \cellcolor[HTML]{DDFFDD}32 & \cellcolor[HTML]{9B9B9B} \\ \hline
+\end{tabular}
+\caption{Pairwise comparison matrix used in the Schulze Mehtod. For example, 17 ballots prefer $A>B$ and 33 ballots prefer $B>A$.}
+\label{Pairwise comparison matrix}
+\end{table}
 \subsubsection{Justification}
+The Shulze Method is used by multiple organisations around the world.
+It has been used by various software organisations such as The Wikimedia Foundation, The Debian Project and Ubuntu.
+It is also used by political parties such as the Pirate Party in Sweden and various other countries.
+The process also differs greatly in both method and implementation from the two other voting methods used in this paper.
 \subsubsection{Pseudocode}
+\label{Schulze psuedocode}
+let $d[i,j]$ be the number of ballots that prefer candidate $i$ to candidate $j$\\
+let $p[i,j]$ be the strength of the strongest path from candidate $i$ to candidate $j$\\
+for $i$ from 1 to $C$\\
+\tab for $j$ form 1 to $C$\\
+\tab\tab if ($i \ne j$)\\
+\tab\tab\tab if ($d[i,j] > d[j,i]$)\\
+\tab\tab\tab\tab $p[i,j] \coloneqq d[i,j]$\\
+\tab\tab\tab else\\
+\tab\tab\tab\tab $p[i,j] \coloneqq 0$\\
+\tab\tab\tab endif \\
+\tab\tab endif \\
+\tab endfor \\
+endfor\\
+for $i$ from 1 to $C$\\
+\tab for $j$ form 1 to $C$\\
+\tab\tab if ($i \ne j$)\\
+\tab\tab\tab for $k$ from 1 to $C$\\
+\tab\tab\tab\tab if ($i \ne k \text{ and } j \ne k$)\\
+\tab\tab\tab\tab\tab $p[j,k] \coloneqq \text{max }(p[j,k], \text{ min }(p[j,k], p[i,k]))$\\
+\tab\tab\tab\tab endif \\
+\tab\tab\tab endfor \\
+\tab\tab endif \\
+\tab endfor \\
+endfor\\
+
 \subsubsection{Implementation}
@@
 First-past-the-post program
-\lstinputlisting[language=JavaScript]{code/index.ts}
 

### 2017-03-18 paper/code/candidateNode.ts

@@ -1,0 +1,13 @@
+class CandidateNode {
+  public cand: number
+  public count: number
+  public children: CandidateNode[]
+  // Add this and another branch together. Returns a new branch
+  add(other: CandidateNode): CandidateNode {
+    //...
+  }
+  // Multilies the count of this node and all its children and returns the new branch
+  multiply(factor: number): CandidateNode {
+    //...
+  }
+}

### 2017-03-18 stv/election.ts

@@ -15,9 +15,6 @@ export function runElection(input: number[][], seats: number): Result {
     // Build the base tree based in input
     let tree = buildTree(input)
 
-    var fs = require('fs')
-    fs.writeFile('tree.json', JSON.stringify(tree))
-
     // Loop through while all seats are not filled
     while(seats > winners.length) {
         // Check for winners

### 2017-03-18 test.ts

@@ -7,8 +7,8 @@ import schulze from './schulze'
 
 const seats = 3;
 
-const parties = 7
-const ballots = 100
+const parties = 5
+const ballots = 50
 
 const ideologies: Ideology[] = [{
     size: 0.2,
@@ -27,6 +27,9 @@ const ideologies: Ideology[] = [{
 
 let results: Array<{ stv: number[], fptp: number[], schulze: number[], }> = []
 const input = createInput(ideologies, parties, ballots)
+
+var fs = require('fs')
+fs.writeFile('input.json', JSON.stringify(input))
 
 for (var j = 0; j <= 0; j++) {
     console.log(j)

### 2017-03-19 paper/paper.tex
Wrote more on schulze implementation
Found minted!

@@
 It can be found in the \texttt{stv/candidate.ts} file and has the following properties and functions:
-\lstinputlisting[language=JavaScript]{code/candidateNode.ts}
+\lstinputlisting[language=JavaScript, label=some-code, caption=Some Code]{code/candidateNode.txt}
 \begin{figure}[H]
@@
 endfor\\
-
 \subsubsection{Implementation}
-
+The Shulze Method is implemented within the file \texttt{schulze/index.ts}.
+It takes two inputs: a list of ballots and the number of seats to be elected.
+A ballot is an ordered list of candidates.
+The output of the program is a list of winners.
 \section{Evaluation of methods}

### 2017-03-19 paper/test.tex
Found minted!

\documentclass{article}
\usepackage{minted}
\usepackage{xcolor}
\usemintedstyle{vs}
\definecolor{bg}{rgb}{0.95,0.95,0.95}
\begin{document}
\begin{minted}[mathescape,
               linenos,
               numbersep=5pt,
               tabsize=4,
               label=Helloworld,
               bgcolor=bg,
               breaklines]{TypeScript}
interface Result {
   cand: number,
   votes: number
}
// Calculates the winners in a First-past-the-post election
export default function calculateWinners(input: number[][], seats: number) {

   // Maps input to first prefrences
   let firstPrefrences = input.map(el => {
       return el[0]
   })

   let results: Result[] = []
   // Loops over prefrences and adds/increments result
   for (var i = 0; i < firstPrefrences.length; i++) {
       // Finds index in results array of candidate at i
       let index = results.findIndex(obj => obj.cand === firstPrefrences[i])
       // If candidate is not added to results
       if (index === -1) {
           results.push({ cand: firstPrefrences[i], votes: 1 })
       } else {
           // Increment count if already added in results
           results[index].votes += 1;
       }
   }

   // Sorts array by number of votes
   results.sort((a, b) => {
       if (a.votes > b.votes) {
           return -1
       } else if (a.votes < b.votes) {
           return 1
       }
       return 0
   })

   // Gets the first elements in the sorted array i.e the winners
   let winners = results.slice(0, seats)

   // Returns array of winners
   return winners.map(cand => cand.cand)
}

\end{minted}
\end{document}

### 2017-03-19 paper/paper.tex
Minted

@@
-\input{config.tex}
+\documentclass[12pt]{article}
+\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
+\usepackage[table,xcdraw]{xcolor}
 \usepackage{hyperref}
@@
 \usepackage{mathtools}
+\usepackage{tikz}
+\usepackage{pgfplots}
 
-\newcommand\tab[1][1cm]{\hspace*{#1}}
+\pgfplotsset{compat=1.14}
 
@@
 }
-\usepackage{pseudocode}
-\usepackage{tikz}
-\usepackage{pgfplots}
-\pgfplotsset{compat=1.14}
+
+\usepackage[backend=biber,style=authoryear]{biblatex}
+\usepackage[newfloat]{minted}
+\usepackage{csquotes}
+
+\graphicspath{ {images/} }
+
+\usemintedstyle{vs}
+
+\newcommand\tab[1][1cm]{\hspace*{#1}}
+\SetupFloatingEnvironment{listing}{name=Code example}
+\definecolor{bg}{rgb}{0.95,0.95,0.95}
+\newcounter{codecounter}
+\newenvironment{code}{\captionsetup{type=listing}}{}
+
+\newcommand\codeblock[3]{%
+\begin{code}
+	\caption{#3}
+	\inputminted[%
+	    mathescape,
+	    linenos,
+	    numbersep=5pt,
+	    tabsize=4,
+	    label=Helloworld,
+	    bgcolor=bg,
+	    breaklines%
+	]{TypeScript}{#1}
+	\label{#2}
+\end{code}
+}
 
 \addbibresource{sample.bib}
+\usepackage{caption}
 
@@
 Here is some example code in typescript:
-\begin{lstlisting}
-let helloWorld: string = 'Hello World' // This is a comment
-console.log(helloWorld)
-\end{lstlisting}
+\codeblock{code/typescriptexample.ts}{code:typescript example}{Basic Typescript syntax}
 \subsection{Modeling test data}
@@
 The first-past-the-post program is implemented in a single file. It takes the following inputs:
-\begin{lstlisting}
-ballots: number[][] // Ex. [[0,1,2],[1,0,2],...]
-seats: number // Ex. 2
-\end{lstlisting}
+\codeblock{code/fptp/inputs.ts}{code:fptp inputs}{Inputs for FPTP program}
 The ballot data is first mapped to only include first prefrences. Then the algorithm loops over the ballots and gets the sum of votes for each candidate:
-\begin{lstlisting}
-let results: Result[] = []
-// Loops over prefrences and adds/increments result
-for (var i = 0; i < firstPrefrences.length; i++) {
-    // Finds index in results array of candidate at i
-    let index = results.findIndex(obj => obj.cand === firstPrefrences[i])
-    // If candidate is not added to results
-    if (index === -1) {
-        results.push({ cand: firstPrefrences[i], votes: 1 })
-    } else {
-        // Increment count if already added in results
-        results[index].votes += 1;
-    }
-}
-\end{lstlisting}
+\codeblock{code/fptp/processing.ts}{code:fptp processing}{Processing and formatting of data}
 The results array is sorted and sliced to only include the $N$ candidates with most votes:
-\begin{lstlisting}
-// Sorts array by number of votes
-results.sort((a, b) => {
-    if (a.votes > b.votes) {
-        return -1
-    } else if (a.votes < b.votes) {
-        return 1
-    }
-    return 0
-})
-// Gets the first elements in the sorted array i.e the winners
-let winners = results.slice(0, seats)
-// Returns array of winners
-return winners.map(cand => cand.cand)
-\end{lstlisting}
+\codeblock{code/fptp/result.ts}{code:fptp result calculation}{Finding and returning winning candidates}
 \subsection{Single transferable vote}
@@
 It can be found in the \texttt{stv/candidate.ts} file and has the following properties and functions:
-\lstinputlisting[language=JavaScript, label=some-code, caption=Some Code]{code/candidateNode.txt}
+%\lstinputlisting[language=JavaScript, label=some-code, caption=Some Code]{code/candidateNode.txt}
 \begin{figure}[H]

### 2017-03-19 paper/test.tex
Minted

@@
 \usemintedstyle{vs}
+
+\renewcommand{\listingscaption}{Code example}
+\newcommand{\codeblock}[3]{%
 \definecolor{bg}{rgb}{0.95,0.95,0.95}
-\begin{document}
-\begin{minted}[mathescape,
+
+\begin{listing}[H]
+  \inputminted[
+    mathescape,
     linenos,
@@
     bgcolor=bg,
-               breaklines]{TypeScript}
-interface Result {
-   cand: number,
-   votes: number
-}
-// Calculates the winners in a First-past-the-post election
-export default function calculateWinners(input: number[][], seats: number) {
-
-   // Maps input to first prefrences
-   let firstPrefrences = input.map(el => {
-       return el[0]
-   })
-
-   let results: Result[] = []
-   // Loops over prefrences and adds/increments result
-   for (var i = 0; i < firstPrefrences.length; i++) {
-       // Finds index in results array of candidate at i
-       let index = results.findIndex(obj => obj.cand === firstPrefrences[i])
-       // If candidate is not added to results
-       if (index === -1) {
-           results.push({ cand: firstPrefrences[i], votes: 1 })
-       } else {
-           // Increment count if already added in results
-           results[index].votes += 1;
-       }
+    breaklines
+  ]{TypeScript}{#1}
+  \caption{#3}
+  \label{#2}
+\end{listing}
 }
 
-   // Sorts array by number of votes
-   results.sort((a, b) => {
-       if (a.votes > b.votes) {
-           return -1
-       } else if (a.votes < b.votes) {
-           return 1
-       }
-       return 0
-   })
-
-   // Gets the first elements in the sorted array i.e the winners
-   let winners = results.slice(0, seats)
-
-   // Returns array of winners
-   return winners.map(cand => cand.cand)
-}
-
-\end{minted}
+\begin{document}
+\codeblock{code/candidateNode.ts}{code: global data structure}{This is an example}
 \end{document}

### 2017-03-19 paper/code/fptp/inputs.ts

@@ -1,0 +1,2 @@
+ballots: number[][] // Ex. [[0,1,2],[1,0,2],...]
+seats: number // Ex. 2

### 2017-03-19 paper/code/fptp/processing.ts

@@ -1,0 +1,13 @@
+let results: Result[] = []
+// Loops over prefrences and adds/increments result
+for (var i = 0; i < firstPrefrences.length; i++) {
+    // Finds index in results array of candidate at i
+    let index = results.findIndex(obj => obj.cand === firstPrefrences[i])
+    // If candidate is not added to results
+    if (index === -1) {
+        results.push({ cand: firstPrefrences[i], votes: 1 })
+    } else {
+        // Increment count if already added in results
+        results[index].votes += 1;
+    }
+}

### 2017-03-19 paper/code/fptp/result.ts

@@ -1,0 +1,13 @@
+// Sorts array by number of votes
+results.sort((a, b) => {
+    if (a.votes > b.votes) {
+        return -1
+    } else if (a.votes < b.votes) {
+        return 1
+    }
+    return 0
+})
+// Gets the first elements in the sorted array i.e the winners
+let winners = results.slice(0, seats)
+// Returns array of winners
+return winners.map(cand => cand.cand)

### 2017-03-19 paper/code/typescriptexample.ts

@@ -1,0 +1,2 @@
+let helloWorld: string = 'Hello World' // This is a comment
+console.log(helloWorld)

### 2017-03-19 generator/ballots.ts
Renamed parties to candidates

@@ -2,11 +2,11 @@ import { Ideology, IdeologyWithProbabilities } from './interfaces'
 
 
 // Generates the ballots, essentially the output of the program
-export function generateBallots(numberOfBallots: number, prob: number[], parties: number[]): number[][] {
+function generateBallots(numberOfBallots: number, prob: number[], candidates: number[]): number[][] {
     // Create temp array combining probability and possib
     let temp: number[][] = []
-    for (var i = 0; i < parties.length; i++) {
-        temp.push([prob[i], parties[i]])
+    for (var i = 0; i < candidates.length; i++) {
+        temp.push([prob[i], candidates[i]])
     }
 
     //Sorts the temp array
@@ -46,7 +46,7 @@ export function createAllBallots(ideologies: Ideology[], ideologyProbabilities: 
         const ideology = ideologies[i]
         const ideologyProbability = ideologyProbabilities[i]
 
-        const arrOfBallots = generateBallots(ideology.size*ballots, ideologyProbability.probabilities , ideologyProbability.parties)
+        const arrOfBallots = generateBallots(ideology.size*ballots, ideologyProbability.probabilities , ideologyProbability.candidates)
 
         result = result.concat(arrOfBallots)
     }
@@ -56,23 +56,23 @@ export function createAllBallots(ideologies: Ideology[], ideologyProbabilities: 
 
 
 function distributeVotes(temp: number[][]): number[] {
-    let parties = [ ...temp ]
-    let index = parties.length
+    let candidates = [ ...temp ]
+    let index = candidates.length
     let result: number[] = []
 
     while (index > 0) {
         const rand = Math.random()
         // Loops through the temp array
-        for (var i = 0; i < parties.length; i++) {
+        for (var i = 0; i < candidates.length; i++) {
             // Gets the value of the party size
-            const val = parties[i][0]
+            const val = candidates[i][0]
             // The first value that is greater than the random number 
             if (val > rand) {
                 // Checks if party has already been voted for
-                if (!parties[i][2]) {
+                if (!candidates[i][2]) {
                     // Makes sure that the party isn't voted for again
-                    parties[i] = [ ...parties[i], 1]
-                    result.push(parties[i][1])
+                    candidates[i] = [ ...candidates[i], 1]
+                    result.push(candidates[i][1])
                     index--
                 }
                 // Breaks the loop so that only the first value greater than the random number is added

### 2017-03-19 generator/candidates.ts

@@ -1,66 +1,73 @@
-import {Ideology, IdeologyWithProbabilities, IdeologyWithParties, Party} from './interfaces'
+import {Ideology, IdeologyWithProbabilities, IdeologyWithCandidates, Candidate} from './interfaces'
 
 // Creates the parties and assigns them an ideology based on their relative sizes.
-export function createParties(numberOfParties: number, ideologies: Ideology[]): Party[] {
-
-    const tempIdeologies: IdeologyWithParties[] = ideologies.map((ideology) => {
-        return Object.assign({}, ideology, { numberOfParties: 0 })
+export function createCandidates(numberOfCandidates: number, ideologies: Ideology[]): Candidate[] {
+    const tempIdeologies: IdeologyWithCandidates[] = ideologies.map((ideology) => {
+        return Object.assign({}, ideology, { numberOfCandidates: 0 })
     })
 
-    let parties: Party[] = []
-    const initialNumberOfParties = numberOfParties
+    let candidates: Candidate[] = []
+    const initialNumberOfCandidates = numberOfCandidates
     // Loops while not every party has an ideology
-    while (numberOfParties > 0) {
+    while (numberOfCandidates > 0) {
         // Loops though all future party indexes
-        for (let partyIndex = 0; partyIndex < initialNumberOfParties; partyIndex++) {
+        for (let candidateIndex = 0; candidateIndex < initialNumberOfCandidates; candidateIndex++) {
 
             // Loops through all ideologies
             for (let ideologyIndex = 0; ideologyIndex < tempIdeologies.length; ideologyIndex++) {
-                if(numberOfParties <= 0)
+                if(numberOfCandidates <= 0)
                     break
+                
                 // Current ideology in loop
                 const ideology = tempIdeologies[ideologyIndex]
                 //Gets the number of parties that should belong to an ideology
-                const size = Math.round(initialNumberOfParties * ideology.size)
+                const size = Math.round(initialNumberOfCandidates * ideology.size)
                 // An ideology needs to have at least one party
-                if ((size === 0 ? 1 : size) > ideology.numberOfParties) {
-                    ideology.numberOfParties++
-                    numberOfParties--
+                if ((size === 0 ? 1 : size) > ideology.numberOfCandidates) {
+                    ideology.numberOfCandidates++
+                    numberOfCandidates--
                     // Pushes thae new party to the array
-                    parties.push({ ideology: ideologyIndex, size: undefined })
+                    candidates.push({ ideology: ideologyIndex, size: undefined })
[…]

### 2017-03-19 generator/index.ts

@@ -3,15 +3,14 @@
 */
 
 import { Ideology, IdeologyWithProbabilities } from './interfaces'
-import { createParties, assignProbabilityToIdeology } from './parties'
+import { createCandidates, assignProbabilityToIdeology } from './candidates'
 import { createAllBallots } from './ballots'
 
-export default function generateInput(ideologies: Ideology[], numberOfParties: number, numberOfBallots: number): number[][] {
-    
-    const parties = createParties(numberOfParties, ideologies)
+export default function generateBallots(ideologies: Ideology[], numberOfcandidates: number, numberOfBallots: number): number[][] {
+    const candidates = createCandidates(numberOfcandidates, ideologies)
 
-    const ideologyProbabilities: IdeologyWithProbabilities[] = assignProbabilityToIdeology(ideologies, parties)
-    
+    const ideologyProbabilities: IdeologyWithProbabilities[] = assignProbabilityToIdeology(ideologies, candidates)
+
     const result = createAllBallots(ideologies, ideologyProbabilities, numberOfBallots)
 
     return result

### 2017-03-19 generator/interfaces.ts

@@ -1,23 +1,23 @@
     
 export interface Ideology {
     size: number,
-    partyPower: number,
+    candidatePower: number,
     ideologyPower: number
 }
 
-export interface IdeologyWithParties {
+export interface IdeologyWithCandidates {
     size: number,
-    partyPower: number,
+    candidatePower: number,
     ideologyPower: number,
-    numberOfParties: number
+    numberOfCandidates: number
 }
 
 export interface IdeologyWithProbabilities {
     probabilities: number[],
-    parties: number[]
+    candidates: number[]
 }
 
-export interface Party {
+export interface Candidate {
     ideology: number,
     size: number | undefined
 }

### 2017-03-19 test.ts

@@ -1,54 +1,53 @@
 import { Ideology } from './generator/interfaces'
-import createInput from './generator'
+import generateBallots from './generator'
 
 import fptp from './fptp'
 import { runElection as stv } from './stv'
 import schulze from './schulze'
 
-const seats = 3;
 
-const parties = 5
-const ballots = 50
+const ballots = 500
+
+const candidates = 8
+const seats = 1
 
 const ideologies: Ideology[] = [{
-    size: 0.2,
-    partyPower: 0.2,
-    ideologyPower: 1.2
+    size: 0.3,
+    candidatePower: 0.6,
+    ideologyPower: 0.8
 }, {
     size: 0.3,
-    partyPower: 2,
-    ideologyPower: 1.6
+    candidatePower: 0.8,
+    ideologyPower: 0.7
 }, {
-    size: 0.5,
-    partyPower: 1.3,
-    ideologyPower: 0.7,
+    size: 0.4,
+    candidatePower: 0.5,
+    ideologyPower: 0.8,
 }]
 
 
[…]

### 2017-03-19 paper/paper.tex
Wrote more

@@
 
+W
 \hypersetup{
@@
 \usepackage{csquotes}
+\usepackage{caption}
 
@@
 \definecolor{bg}{rgb}{0.95,0.95,0.95}
-\newcounter{codecounter}
 \newenvironment{code}{\captionsetup{type=listing}}{}
@@
 
+\newcommand\Code[1]{\texttt{#1}}
+
 \addbibresource{sample.bib}
-\usepackage{caption}
 
@@
 The purpose of this essay is to evaluate differences and similarities in terms of election results in three different voting systems: Single Transferable Vote (STV), First-Past-The-Post (FPTP) and the Schulze Method.
-I will only be investigating and discussing differences and similarities in the results of the methods, not touching on how practically feasible the systems are in an actual election.
+This paper will only be examining and discussing differences and similarities in the results of the methods, not touching on how practically feasible the methods might be in actual election.
 \pagebreak
@@
 \section{Methodology}
-Methodology here
 All voting methods have been implemented in Typescript – mostly due to the author having previous experience with JavaScript.
-Typescript is a superset of JavaScript and compiles down to it.
-Typescript has some extra features compared to JavaScript but most importantly it has optional static type checking.
+Typescript is a superset of JavaScript with multiple extra feautures.
+Most importantly Typescript has optional static type checking.
 Here is some example code in typescript:
@@
 \subsection{Modeling test data}
+In order to test the methods and their implementations, test data is needed.
+There are cases where extensive election data is published, such as in maltese elections, but full ballot data, which is needed for the implementations has not been found.
+Instead, the implementations will be tested with data generated from a simple computer algorithm.
+The algorithm used in this paper is highly primitive, as modeling prefrences within a population is far beyond this paper.
+The full ballot generation program can be found in the \Code{/generator/} folder.
+The goal of the program is to produce ballots that rank every candidate in order of prefrence (see figure \ref{STV ballot} on page \pageref{STV ballot}).
+The program represents each voter in a population as belonging to a certain ideology.
+Each ideology has has a list of weighted prefrences indicating how a voter for this ideology is likely to vote.
+The weighed prefrences are generated via an abstraction.
+A single config object is used to create all ideologies.
+\codeblock{code/generator/ideologyConfig.ts}{code:ideology config}{Configuration object for creating ideologies}
+The program then works via 4 major steps:
+\begin{enumerate}
+	\item It relates each candidate to an ideology based on the size of the ideology. A larger ideology has more candidates.
+	\item It assigns a base size for each candidate.
+Each ideology has a different spread of votes generated by a negative exponential function with a different constant.
+The size of each candidate is then multiplied with the size of their ideology and normalized.
+This gives a base size of all candidates.
+	\item Based on the base size of each candidate, a probability-list of voting for each candidate is created for every ideology.
+An ideology's probability-list represents how a voter aligned the ideology is expected to vote.
+	\item It creates a certain number of individual ballots.
+Each ballot is given an ideology and creates its own list prefrences based via weighted random number generaton according to the probability-list of the assigned ideology.
+\end{enumerate}
+The output of the program is a set of ballots, where each ballot is an ordered set of prefrences.
+The implementation is highly arbitrary and all constants in the program even more so.
+However, expanding on the generator program would be beyond the scope of this project.
+The program works in that it is possible to control variables to test for different election scenarios.
+\subsection{Constructing test scenarios}
+Constructing test scenarios is difficult task.
+Due to there being so many variables both in real elections and the simulated elections in the generator program, it makes it practically inpossible to control all variables.
+Instead, 3 arbitrary test scenarios will be used.
+The election will be simulated 1000 times for each scenario and the election data will then run through the different voting methods and the results will be compared.
+The simulation scenarios are arbitrary but should allow for comparison of the different voting methods.
+All simulations will have 3 ideologies and 500 voters.
+\subsubsection{Scenario 1}
+Scenario 1 is this:
+\codeblock{code/generator/scenario1.ts}{code:scenario 1}{Scenario 1}
+
 \pagebreak
@@
 Every candidate is a top-level node with an attribute showing the number of current votes for the candidate.
-Each node has child nodes that show the next prefrences of the voters for that particular candidate, see figure \ref{Tree structure}.
+Each node has child nodes representing the next prefrences of the voters for that particular candidate, see figure \ref{Tree structure}.
 It is easy to manipulate branches via recursion.
@@
 A candidate node is a Typescript class.
-It can be found in the \texttt{stv/candidate.ts} file and has the following properties and functions:
-%\lstinputlisting[language=JavaScript, label=some-code, caption=Some Code]{code/candidateNode.txt}
-\begin{figure}[H]
+It can be found in the \Code{stv/candidate.ts} file and has the following properties and functions:
+\begin{figure}
 	\centering
@@
 \end{figure}
-With those functions, we can recursively manipulate branches and trees.
-In order to distribute the child nodes of an eliminated candidate, we just need to add each of those nodes to the corresponding top level nodes.
-In order to transfer surplus votes, we can multiply each child node with a factor and then distribute those nodes onto the top level nodes.
-The full source code for the tree manipuation functions can be found in \texttt{stv/tree.ts}.
+\codeblock{code/stv/candidateNode.ts}{code:stv candidate node}{The CandidateNode class}
+With the \Code{add()} and \Code{multiply()} functions it is possible to recursively modify branches.
+There are two different manipulations that need to be preformed on the tree: tansfering surplus votes and eliminating candidates.
+Both functions rely on the \Code{distribute()} function wich is used to distribute a set of nodes onto the tree.
+\codeblock{code/stv/distribute.ts}{code:stv distribute function}{The distribute function}
+In order to eliminate and transfer surplus votes from any candidate node $A$, the children of $A$ are passed into the distribute function.
+In the case of transfering surplus votes, the votes for each child node is first multiplied by $\frac{\text{surplus votes}}{\text{total votes}}$ as outlined in the psuedocode in section \ref{Stv psuedocode}.
+The full source code for funcions that manipulate the tree structure can be found in \Code{/stv/tree.ts}.
 
-The input into the algorithm is a set of ballots.
-A ballot consists of an ordered list of candidates according to prefrence.
-Every candidate is represented by an integer.
-The input data is converted into the tree structure via the \texttt{buildTree} function.
-It can also be found in the \texttt{stv/tree.ts} file.
-
-The main procces of the program is found in the \texttt{stv/election.ts} file and runs the process defined in the psuedocode on page \pageref{Stv psuedocode}.
-The program takes the input defined above and a number representing the number of seats to elect as inputs.
-The process outputs an array of winning candidates as well as a log file.
+The main procces of the program is found in the \Code{stv/election.ts} file and runs the process defined in the psuedocode in section \ref{Stv psuedocode} on page \pageref{Stv psuedocode}.
 
@@
 \subsubsection{Implementation}
-The Shulze Method is implemented within the file \texttt{schulze/index.ts}.
+The Shulze Method is implemented within the file \Code{schulze/index.ts}.
 It takes two inputs: a list of ballots and the number of seats to be elected.
@@
 The output of the program is a list of winners.
+The program first creates the matrices for both the prefrences and paths between candidates.
+\codeblock{code/schulze/maps.ts}{code:schulze maps}{Data representation}
+The program then runs the algorithm outlined in the psuedocode in section \ref{Schulze psuedocode}.
+\codeblock{code/schulze/algorithm.ts}{code:schulze algorithm}{Main algorithm}
 \section{Evaluation of methods}
@@
 		\begin{axis}[
-			ybar stacked,
+			ybar,
 			width = 0.9\textwidth,
 			height = 0.5\textwidth,
-			cycle list = {black!80,black!50,black!20},
 			legend style={at={(0.5,-0.25)},
@@
 			ylabel = {Elections won},
-			xlabel = {Party},
+			xlabel = {Candidate},
 			ymajorgrids = true,
-			every axis plot/.append style={fill,draw=none,no markers},
-      ymin = 0
+			every axis plot/.append style={draw=none,fill,no markers},
+      ymin = 0,
+			symbolic x coords={0,1,2,3,4,5,6,7,8},
+			bar width=0.25cm
       ]
 			\addplot coordinates
-			{(0, 1)(1, 1)(2, 1)(3, 0)(4, 0)(5, 0)(6, 0)};
+{(0, 563)(1, 337)(2, 100)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)};
 \addplot coordinates
-			{(0, 1)(1, 1)(2, 1)(3, 0)(4, 0)(5, 0)(6, 0)};
+{(0, 323)(1, 203)(2, 474)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)};
 \addplot coordinates
-			{(0, 0)(1, 1)(2, 1)(3, 0)(4, 1)(5, 0)(6, 0)};
+{(0, 333)(1, 255)(2, 412)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)};
+
 			\legend{FPTP, STV, Schulze}
@@
 			ylabel = {First prefrence votes},
-			xlabel = {Party},
+			xlabel = {Candidate},
 			ymajorgrids = true,

### 2017-03-19 paper/code/generator/ideologyConfig.ts

@@ -1,0 +1,14 @@
+const ideologyConfig: Ideology[] = [{
+    // The size of the ideology
+    size: 0.2,
+    // Spread of votes between candidates within ideology
+    // Large -> steep spread, Small -> flat spread
+    candidatePower: 0.2,
+    // How inclined voters of this ideology are to vote for a candidate of this ideology
+    // Higer -> more inclined
+    ideologyPower: 1.2
+}, {
+//  ...
+},
+// ...
+]

### 2017-03-19 paper/code/generator/scenario1.ts

@@ -1,0 +1,15 @@
+const candidates = 8
+const seats = 1
+const ideologies: Ideology[] = [{
+    size: 0.3,
+    candidatePower: 0.6,
+    ideologyPower: 0.8
+}, {
+    size: 0.3,
+    candidatePower: 0.8,
+    ideologyPower: 0.7
+}, {
+    size: 0.4,
+    candidatePower: 0.5,
+    ideologyPower: 0.6,
+}]

### 2017-03-19 paper/code/schulze/algorithm.ts

@@ -1,0 +1,24 @@
+// Computing strongest path strength. Variant of the Floyd-Warshall algorithm
+for (var i = 0; i < c; i++) {
+    for (var j = 0; j < c; j++) {
+        if (i !== j) {
+            if (d[i][j] > d[j][i]) {
+                p[i][j] = d[i][j]
+            } else {
+                p[i][j] = 0
+            }
+        }
+    }
+}
+
+for (var i = 0; i < c; i++) {
+    for (var j = 0; j < c; j++) {
+        if (i !== j) {
+            for (var k = 0; k < c; k++) {
+                if (i !== k && j !== k) {
+                    p[j][k] = Math.max(p[j][k], Math.min(p[j][i], p[i][k]))
+                }
+            }
+        }
+    }
+}

### 2017-03-19 paper/code/schulze/maps.ts

@@ -1,0 +1,6 @@
+// d[i][j] gives the number of ballots prefering i > j
+let d: PairMap = getPairs(input)
+// o[i][j] stores the strongest path between i and j
+let p: PairMap = {}
+// Number of candidates
+let c = input[0].length

### 2017-03-19 paper/code/stv/candidateNode.ts

@@ -2,11 +2,11 @@ class CandidateNode {
   public cand: number
   public count: number
   public children: CandidateNode[]
-  // Add this and another branch together. Returns a new branch
+  // Add this and another branch together. Returns a new branch.
   add(other: CandidateNode): CandidateNode {
     //...
   }
-  // Multilies the count of this node and all its children and returns the new branch
+  // Multiplies the count of this node and all its children and returns the new branch
   multiply(factor: number): CandidateNode {
     //...
   }

### 2017-03-19 paper/code/stv/distribute.ts

@@ -1,0 +1,21 @@
+// Distributes a list of nodes onto the tree. Returns a new tree.
+function distribute(nodeList: CandidateNode[], tree: CandidateNode[], winners: number[]): CandidateNode[] {
+    // Loops through each candidate node in the list
+    for (let i = 0; i < nodeList.length; i++) {
+        let cand = nodeList[i];
+        // Find if candidate is in the tree and/or is a winner
+        let itExistsInTree = tree.some(obj => obj.cand === cand.cand)
+        let isWinner = winners.includes(cand.cand)
+
+        // If it doesn't exist in tree (eliminated or no votes) or is a winner, distribute its children instead (recursive).
+        if (!itExistsInTree || isWinner) {
+            tree = distribute(cand.children, tree, winners)
+        } else {
+            // Find the index of candidate in tree
+            let treeIndex = tree.findIndex(item => item.cand === cand.cand)
+            // Add the trees/branches together
+            tree[treeIndex] = tree[treeIndex].add(nodeList[i])
+        }
+    }
+    return tree
+}

### 2017-03-19 schulze/index.ts

@@ -11,9 +11,9 @@ export default function calculateResult(input: number[][], seats: number): numbe
     // Gets the pairs of candidates and their count
     // Ex 120 votes prefer a > b
 
-    // d[i][j] gives the number of ballots prefering i > j
+    // d[i][j] gives the number of ballots prefering candidate i > j
     let d: PairMap = getPairs(input)
-    // o[i][j] stores the strongest path between i and j
+    // o[i][j] stores the strongest path between candidate i and j
     let p: PairMap = {}
     // Number of candidates
     let c = input[0].length

### 2017-03-19 stv/tree.ts

@@ -81,11 +81,11 @@ export function transferSurplus(candNumber: number, tree: CandidateNode[], quota
 
 }
 
-// Distributes votes from a list onto the tree. Returns a new tree.
-function distribute(treeList: CandidateNode[], tree: CandidateNode[], winners: number[]): CandidateNode[] {
-    // Loops through each candidate in the list
-    for (let i = 0; i < treeList.length; i++) {
-        let cand = treeList[i];
+// Distributes a list of nodes onto the tree. Returns a new tree.
+function distribute(nodeList: CandidateNode[], tree: CandidateNode[], winners: number[]): CandidateNode[] {
+    // Loops through each candidate node in the list
+    for (let i = 0; i < nodeList.length; i++) {
+        let cand = nodeList[i];
         // Find if candidate is in the tree and/or is a winner
         let itExistsInTree = tree.some(obj => obj.cand === cand.cand)
         let isWinner = winners.includes(cand.cand)
@@ -97,7 +97,7 @@ function distribute(treeList: CandidateNode[], tree: CandidateNode[], winners: n
             // Find the index of candidate in tree
             let treeIndex = tree.findIndex(item => item.cand === cand.cand)
             // Add the trees/branches together
-            tree[treeIndex] = tree[treeIndex].add(treeList[i])         
+            tree[treeIndex] = tree[treeIndex].add(nodeList[i])         
         }
     }
     return tree

### 2017-03-19 testmethod.ts

@@ -1,0 +1,12 @@
+export function findVariance(numbers: number[]): number {
+    let n = numbers.length
+    let s = (numbers.reduce((a,b) => a+b)**2)/n
+    let sSquared = numbers.map(a => a**2).reduce((a,b) => a+b)
+
+    let d = sSquared - s
+
+    let variance = (d/(n-1))
+
+    return variance
+}
+

### 2017-03-19 test.ts
Changed variance to standard deviation

@@ -117,15 +117,15 @@ for (var i = 0; i < 3; i++) {
     plots += '};\n'
 }
 
-import { findVariance } from './testmethod';
+import { findStandardDeviation } from './testmethod';
 
-let variacnes: number[] = []
+let standardDeviations: number[] = []
 
-variacnes.push(findVariance(formattedResults.fptp.map(res => res.wins)))
-variacnes.push(findVariance(formattedResults.stv.map(res => res.wins)))
-variacnes.push(findVariance(formattedResults.schulze.map(res => res.wins)))
+standardDeviations.push(findStandardDeviation(formattedResults.fptp.map(res => res.wins)))
+standardDeviations.push(findStandardDeviation(formattedResults.stv.map(res => res.wins)))
+standardDeviations.push(findStandardDeviation(formattedResults.schulze.map(res => res.wins)))
 
-console.log(variacnes)
+console.log(standardDeviations)
 
[…]

### 2017-03-19 testmethod.ts

@@ -1,12 +1,12 @@
-export function findVariance(numbers: number[]): number {
+export function findStandardDeviation(numbers: number[]): number {
     let n = numbers.length
     let s = (numbers.reduce((a,b) => a+b)**2)/n
     let sSquared = numbers.map(a => a**2).reduce((a,b) => a+b)
 
     let d = sSquared - s
 
-    let variance = (d/(n-1))
+    let standardDeviation = (d/(n-1))**0.5
 
-    return variance
+    return standardDeviation
 }
 

### 2017-03-21 paper/paper.tex
Compiled and wrote about results

@@
 
-W
 \hypersetup{
@@
 \usepackage[newfloat]{minted}
+\usemintedstyle{vs}
 \usepackage{csquotes}
 \usepackage{caption}
+\usepackage{booktabs}
 
 \graphicspath{ {images/} }
-
-\usemintedstyle{vs}
 
@@
 	\vspace{2cm}
-	{\Huge Analysis of voting systems: What should I call it? \par}
+	{\Huge Analysis of voting systems: title here\par}
 	\vspace{0.6cm}
 	{\LARGE Adrian Salamon\par}
-
 	\vspace{0.6cm}
@@
 Here is some example code in typescript:
-\codeblock{code/typescriptexample.ts}{code:typescript example}{Basic Typescript syntax}
+\codeblock{code/typescriptexample.ts}{lst:typescript example}{Basic Typescript syntax}
 \subsection{Modeling test data}
@@
 The full ballot generation program can be found in the \Code{/generator/} folder.
-The goal of the program is to produce ballots that rank every candidate in order of prefrence (see figure \ref{STV ballot} on page \pageref{STV ballot}).
+The goal of the program is to produce ballots that rank every candidate in order of prefrence (see figure \ref{fig:stv ballot} on page \pageref{fig:stv ballot}).
 The program represents each voter in a population as belonging to a certain ideology.
@@
 A single config object is used to create all ideologies.
-\codeblock{code/generator/ideologyConfig.ts}{code:ideology config}{Configuration object for creating ideologies}
+\codeblock{code/generator/ideologyConfig.ts}{lst:ideology config}{Configuration object for creating ideologies}
 The program then works via 4 major steps:
@@
 \subsubsection{Scenario 1}
-Scenario 1 is this:
-\codeblock{code/generator/scenario1.ts}{code:scenario 1}{Scenario 1}
+The scenario is built around electing one candidate out of eight.
+The spread of votes within ideologies is flat and all ideologies are "weak".
+This means that the general spread of votes will be even.
+An example of the distrubution of first-prefrence votes generated in this scenario can be seen in figure \ref{fig:example of scenario 1}.
+The full configuration object can be seen in code example \ref{lst:scenario 1}.
+\codeblock{code/generator/scenario1.ts}{lst:scenario 1}{Configuration object for scenario 1}
+\begin{figure}
+	\centering
+	\caption{Example distrubution of first-prefrence votes in scenario 1}
+	\begin{tikzpicture}
+		\begin{axis}[
+			ybar stacked,
+			width = 0.9\textwidth,
+			height = 0.5\textwidth,
+			legend style={at={(0.5,-0.25)},
+			anchor=north,legend columns=-1},
+      x tick style = transparent,
+			ylabel = {First prefrence votes},
+			xlabel = {Candidate},
+			ymajorgrids = true,
+      ymin = 0,
+			yticklabel={\pgfmathprintnumber\tick\%}
+      ]
+			\addplot coordinates
+			{(0, 20)(1, 0)(2, 0)(3, 9)(4, 0)(5, 0)(6, 0)(7, 0)};
+			\addplot coordinates
+			{(0, 0)(1, 19)(2, 0)(3, 0)(4, 8)(5, 0)(6, 0)(7, 0)};
+			\addplot coordinates
+			{(0, 0)(1, 0)(2, 22)(3, 0)(4, 0)(5, 12)(6, 6)(7, 4)};
+			\legend{Ideology 1, Ideology 2, Ideology 3}
+		\end{axis}
+	\end{tikzpicture}
+	\label{fig:example of scenario 1}
+\end{figure}
+\subsubsection{Scenario 2}
+The second scenario elects 3 candidates out of 9 total.
+It features a normal spread of votes between candidates.
+An example distribution of first-prefrence votes generated in this scenario can be seen in figure \ref{fig:example of scenario 2}.
+The full configuration can be seen in code example \ref{lst:scenario 2}.
+\codeblock{code/generator/scenario2.ts}{lst:scenario 2}{Scenario 2}
+\begin{figure}[H]
+	\centering
+	\caption{Example distrubution of first-prefrence votes in scenario 2}
+	\begin{tikzpicture}
+		\begin{axis}[
+			ybar stacked,
+			width = 0.9\textwidth,
+			height = 0.5\textwidth,
+			legend style={at={(0.5,-0.25)},
+			anchor=north,legend columns=-1},
+      x tick style = transparent,
+			ylabel = {First prefrence votes},
+			xlabel = {Candidate},
+			ymajorgrids = true,
+      ymin = 0,
+			yticklabel={\pgfmathprintnumber\tick\%}
+      ]
+			\addplot coordinates
+			{(0, 16)(1, 0)(2, 0)(3, 4)(4, 0)(5, 0)(6, 0)(7, 0)(8, 0)};
+			\addplot coordinates
+			{(0, 0)(1, 12)(2, 0)(3, 0)(4, 10)(5, 0)(6, 8)(7, 0)(8, 0)};
+			\addplot coordinates
+			{(0, 0)(1, 0)(2, 22)(3, 0)(4, 0)(5, 13)(6, 0)(7, 9)(8, 6)};
+			\legend{Ideology 1, Ideology 2, Ideology 3}
+		\end{axis}
+	\end{tikzpicture}
+	\label{fig:example of scenario 2}
+\end{figure}
+\subsubsection{Scenario 3}
+The second scenario elects 3 candidates out of 9 total.
+It features a steep spread of votes between candidates.
+An example distribution of first-prefrence votes generated in this scenario can be seen in figure \ref{fig:example of scenario 3}.
+The full configuration can be seen in code example \ref{lst:scenario 3}.
+\codeblock{code/generator/scenario3.ts}{lst:scenario 3}{Scenario 3}
+\begin{figure}[H]
+	\centering
+	\caption{Example distrubution of first-prefrence votes in scenario 3}
+	\begin{tikzpicture}
+		\begin{axis}[
+			ybar stacked,
+			width = 0.9\textwidth,
+			height = 0.5\textwidth,
+			legend style={at={(0.5,-0.25)},
+			anchor=north,legend columns=-1},
+      x tick style = transparent,
+			ylabel = {First prefrence votes},
+			xlabel = {Candidate},
+			ymajorgrids = true,
+      ymin = 0,
+			yticklabel={\pgfmathprintnumber\tick\%}
+      ]
+			\addplot coordinates
+			{(0, 17)(1, 0)(2, 0)(3, 1)(4, 0)(5, 0)(6, 0)(7, 0)(8, 0)};
+			\addplot coordinates
+			{(0, 0)(1, 25)(2, 0)(3, 0)(4, 4)(5, 0)(6, 1)(7, 0)(8, 0)};
+			\addplot coordinates
+			{(0, 0)(1, 0)(2, 40)(3, 0)(4, 0)(5, 10)(6, 0)(7, 2)(8, 0)};
+			\legend{Ideology 1, Ideology 2, Ideology 3}
+		\end{axis}
+	\end{tikzpicture}
+	\label{fig:example of scenario 3}
+\end{figure}
 
@@
 The first-past-the-post program is implemented in a single file. It takes the following inputs:
-\codeblock{code/fptp/inputs.ts}{code:fptp inputs}{Inputs for FPTP program}
+\codeblock{code/fptp/inputs.ts}{lst:fptp inputs}{Inputs for FPTP program}
 The ballot data is first mapped to only include first prefrences. Then the algorithm loops over the ballots and gets the sum of votes for each candidate:
-\codeblock{code/fptp/processing.ts}{code:fptp processing}{Processing and formatting of data}
+\codeblock{code/fptp/processing.ts}{lst:fptp processing}{Processing and formatting of data}
 The results array is sorted and sliced to only include the $N$ candidates with most votes:
-\codeblock{code/fptp/result.ts}{code:fptp result calculation}{Finding and returning winning candidates}
+\codeblock{code/fptp/result.ts}{lst:fptp result calculation}{Finding and returning winning candidates}
 \subsection{Single transferable vote}
@@
 	\caption{Sample STV ballot}
-	\label{STV ballot}
+	\label{fig:stv ballot}
 \end{figure}
@@
 \subsubsection{Pseudocode}
-\label{Stv psuedocode}
+\label{alg:stv psuedocode}
 let $quota$ be the quota \\
@@
 Every candidate is a top-level node with an attribute showing the number of current votes for the candidate.
-Each node has child nodes representing the next prefrences of the voters for that particular candidate, see figure \ref{Tree structure}.
+Each node has child nodes representing the next prefrences of the voters for that particular candidate, see figure \ref{fig:tree structure}.
 It is easy to manipulate branches via recursion.
@@
 	\caption{Simplified and shortened version of the tree structure. Each candidate is a top-level node with children, signifying the prefrences of the voters for that candidate.}
-	\label{Tree structure}
+	\label{fig:tree structure}
 \end{figure}
-\codeblock{code/stv/candidateNode.ts}{code:stv candidate node}{The CandidateNode class}
+\codeblock{code/stv/candidateNode.ts}{lst:stv candidate node}{The CandidateNode class}
 With the \Code{add()} and \Code{multiply()} functions it is possible to recursively modify branches.
@@
 Both functions rely on the \Code{distribute()} function wich is used to distribute a set of nodes onto the tree.
-\codeblock{code/stv/distribute.ts}{code:stv distribute function}{The distribute function}
+\codeblock{code/stv/distribute.ts}{lst:stv distribute function}{The distribute function}
 In order to eliminate and transfer surplus votes from any candidate node $A$, the children of $A$ are passed into the distribute function.
-In the case of transfering surplus votes, the votes for each child node is first multiplied by $\frac{\text{surplus votes}}{\text{total votes}}$ as outlined in the psuedocode in section \ref{Stv psuedocode}.
+In the case of transfering surplus votes, the votes for each child node is first multiplied by $\frac{\text{surplus votes}}{\text{total votes}}$ as outlined in the psuedocode in section \ref{alg:stv psuedocode}.
 The full source code for funcions that manipulate the tree structure can be found in \Code{/stv/tree.ts}.
 
-The main procces of the program is found in the \Code{stv/election.ts} file and runs the process defined in the psuedocode in section \ref{Stv psuedocode} on page \pageref{Stv psuedocode}.
+The main procces of the program is found in the \Code{stv/election.ts} file and runs the process defined in the psuedocode in section \ref{alg:stv psuedocode} on page \pageref{alg:stv psuedocode}.
 
@@
 The Schulze Method is a method used mainly to determine results in a single-winner election but can also be used to provide rankings and elect multiple candidates in a single election.
-Ballots are identical to those of the single transferable vote, see figure \ref{STV ballot} on page \pageref{STV ballot}.
+Ballots are identical to those of the single transferable vote, see figure \ref{fig:stv ballot} on page \pageref{fig:stv ballot}.
 The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate wins.
-As mentioned, this method relies on comparing the prefrences of every candidate to one another as shown in table \ref{Pairwise comparison matrix}.
+As mentioned, this method relies on comparing the prefrences of every candidate to one another as shown in table \ref{tab:pairwise comparison matrix}.
 If there is a condorcet winner the process is simple: declare the condorcet winner a winner and run another iteration without that candidate.
@@
 An efficent and relatively simple way to compute this problem is via the Floyd-Warshall algorithm which is used in the implementation.
-See \ref{Schulze psuedocode} for the full algorithm.
+See \ref{lst:schulze algorithm} for the full algorithm.
 
@@
 \caption{Pairwise comparison matrix used in the Schulze Mehtod. For example, 17 ballots prefer $A>B$ and 33 ballots prefer $B>A$.}
-\label{Pairwise comparison matrix}
+\label{tab:pairwise comparison matrix}
 \end{table}
@@
 \subsubsection{Pseudocode}
-\label{Schulze psuedocode}
+\label{alg:schulze psuedocode}
 let $d[i,j]$ be the number of ballots that prefer candidate $i$ to candidate $j$\\
@@
 The program first creates the matrices for both the prefrences and paths between candidates.
-\codeblock{code/schulze/maps.ts}{code:schulze maps}{Data representation}
-The program then runs the algorithm outlined in the psuedocode in section \ref{Schulze psuedocode}.
-\codeblock{code/schulze/algorithm.ts}{code:schulze algorithm}{Main algorithm}
-\section{Evaluation of methods}
-\subsection{Sample I}
-\subsection{Sample II}
-\subsection{Sample III}
-
-\section{Conclusion}
-
-%\subsection{ Heading Here}
-%This is some code.
-%\lstinputlisting[language=JavaScript]{code/examples/example.js}
-
-%\section{Conclusion}
-%Write your conclusion here. And here is a citation:
-%\textcite{sigfridsson2}
-
-%And another one here (\textcite{sigfridsson})
-
-%\section{Source code}
-%\lstinputlisting[language=JavaScript]{code/test.js}
-
-\pagebreak
-
+\codeblock{code/schulze/maps.ts}{lst:schulze maps}{Data representation}
+The program then runs the algorithm outlined in the psuedocode in section \ref{alg:schulze psuedocode}.
+\codeblock{code/schulze/algorithm.ts}{lst:schulze algorithm}{Main algorithm}
+\section{Evaluation of results}
+\subsection{Scenario 1}
+Scenario 1 featured 8 candidates where one was to be elected.
+Vote spread was flat, meaning that votes tend to be diverse in their prefrences.
+This means that there is not an abvious winner present.
+This can be seen from the first-prefrence votes in the scenario seen in figure \ref{fig:example of scenario 1}.
+The full result in this scenario can be seen in figure \ref{fig:scenario 1 results}.
+The outlier in this scenario seems to be the fptp method, electing candidate 0 more often than both other methods.
+Key metrics for the results in this scenario can be found in table \ref{tab:scenario 1 result}.
 \begin{figure}
@@
 			\addplot coordinates
-{(0, 563)(1, 337)(2, 100)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)};
+			{(0, 273)(1, 59)(2, 668)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)};
 			\addplot coordinates
-{(0, 323)(1, 203)(2, 474)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)};
+			{(0, 37)(1, 4)(2, 959)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)};
 			\addplot coordinates
-{(0, 333)(1, 255)(2, 412)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)};
-
+			{(0, 42)(1, 4)(2, 954)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)};
 			\legend{FPTP, STV, Schulze}
@@
 	\end{tikzpicture}
+	\caption{Figure thingy}
+	\label{fig:scenario 1 results}
 \end{figure}
 
-\begin{figure}
+\begin{table}[H]
+\centering
+\caption{Key metrics for result in scenario 1}
+\label{tab:scenario 1 result}
+\begin{tabular}{@{}lccc@{}}
+\toprule
+Method & Standard deviation & Missrepresentation & Most likely winners \\ \midrule
+FPTP & 223 & 67\% & 2 \\
+STV & 315 & 7\% & 2 \\
+Schulze & 313 & 9\% & 2 \\ \bottomrule
+\end{tabular}
+\end{table}
+% [ 223.39259164082, 315.44928276983, 313.6271671906]
+\subsection{Scenario 2}
+\begin{figure}[H]
 	\centering
@@
       x tick style = transparent,
-			ylabel = {First prefrence votes},
+			ylabel = {Elections won},
 			xlabel = {Candidate},
 			ymajorgrids = true,
-			every axis plot/.append style={fill,draw=none,no markers},
-      ymin = 0
+			every axis plot/.append style={draw=none,fill,no markers},
+      ymin = 0,
+			symbolic x coords={0,1,2,3,4,5,6,7,8},
+			bar width=0.25cm
       ]
 			\addplot coordinates
-			{(0, 17)(1, 36)(2, 32)(4, 9)(5, 5)(6, 1)};
+			{(0, 973)(1, 267)(2, 1000)(3, 0)(4, 12)(5, 743)(6, 0)(7, 5)(8, 0)};
+			\addplot coordinates
+			{(0, 456)(1, 808)(2, 1000)(3, 0)(4, 33)(5, 703)(6, 0)(7, 0)(8, 0)};
+			\addplot coordinates
+			{(0, 338)(1, 160)(2, 1000)(3, 0)(4, 0)(5, 1000)(6, 0)(7, 502)(8, 0)};
+			\legend{FPTP, STV, Schulze}
 		\end{axis}
 	\end{tikzpicture}
+	\caption{Figure thingy numero duo}
+	\label{fig:scenario 2 result}
 \end{figure}
+
+\begin{table}[H]
+\centering
+\caption{Key metrics for result in scenario 2}
+\label{tab:scenario 2 result}
+\begin{tabular}{@{}lccc@{}}
+\toprule
+Method & Standard deviation & Missrepresentation & Most likely winners \\ \midrule
+FPTP & 418 & 42\% & 0, 2 \& 5 \\
+STV & 388 & 14\% & 1, 2 \& 5 \\
+Schulze & 393 & 67\% & 2, 5 \& 7  \\ \bottomrule
+\end{tabular}
+\end{table}
+% [ 418.13628234977, 388.17206952015, 393.25535950293 ]
+\subsection{Scenario 3}
+\begin{figure}[H]
+	\centering
+	\begin{tikzpicture}
+		\begin{axis}[
+			ybar,
+			width = 0.9\textwidth,
+			height = 0.5\textwidth,
+			legend style={at={(0.5,-0.25)},
+			anchor=north,legend columns=-1},
+      x tick style = transparent,
+			ylabel = {Elections won},
+			xlabel = {Candidate},
+			ymajorgrids = true,
+			every axis plot/.append style={draw=none,fill,no markers},
+      ymin = 0,
+			symbolic x coords={0,1,2,3,4,5,6,7,8},
+			bar width=0.25cm
+      ]
+			\addplot coordinates
+			{(0, 994)(1, 1000)(2, 1000)(3, 0)(4, 0)(5, 6)(6, 0)(7, 0)(8, 0)};
+			\addplot coordinates
+			{(0, 1000)(1, 1000)(2, 1000)(3, 0)(4, 0)(5, 0)(6, 0)(7, 0)(8, 0)};
+			\addplot coordinates
+			{(0, 999)(1, 1000)(2, 1000)(3, 0)(4, 0)(5, 1)(6, 0)(7, 0)(8, 0)};
+			\legend{FPTP, STV, Schulze}
+			\end{axis}
+	\end{tikzpicture}
+	\caption{Figure thingy tré}
+	\label{fig:scenario 3 result}
+\end{figure}
+\begin{table}[H]
+\centering
+\caption{Key metrics for result in scenario 3}
+\label{tab:scenario 3 result}
+\begin{tabular}{@{}lccc@{}}
+\toprule
+Method & Standard deviation & Missrepresentation & Most likely winners \\ \midrule
+FPTP & 470 & 33\% & 0, 1 \& 2 \\
+STV & 471 & 33\% & 0, 1 \& 2 \\
+Schulze & 471 & 3\% & 0, 1 \& 2  \\ \bottomrule
+\end{tabular}
+\end{table}
+
+%[ 469.99669029568, 471.40452079103, 471.16899539573 ]
+\section{Conclusion}
+Proportionalities: 1:67,7,9 2:42,14,67, 3:33,33,33
+
+%\subsection{ Heading Here}
+%This is some code.
+%\lstinputlisting[language=JavaScript]{code/examples/example.js}
+
+%\section{Conclusion}
+%Write your conclusion here. And here is a citation:
+%\textcite{sigfridsson2}
+
+%And another one here (\textcite{sigfridsson})
+
+%\section{Source code}
+%\lstinputlisting[language=JavaScript]{code/test.js}
+
+\pagebreak
 

### 2017-03-21 paper/code/generator/scenario1.ts

@@ -2,14 +2,14 @@ const candidates = 8
 const seats = 1
 const ideologies: Ideology[] = [{
     size: 0.3,
-    candidatePower: 0.6,
+    candidatePower: 0.3,
     ideologyPower: 0.8
 }, {
     size: 0.3,
-    candidatePower: 0.8,
+    candidatePower: 0.3,
     ideologyPower: 0.7
 }, {
     size: 0.4,
     candidatePower: 0.5,
-    ideologyPower: 0.6,
+    ideologyPower: 0.8,
 }]

### 2017-03-21 paper/code/generator/scenario2.ts

@@ -1,0 +1,15 @@
+const candidates = 9
+const seats = 3
+const ideologies: Ideology[] = [{
+    size: 0.2,
+    candidatePower: 0.5,
+    ideologyPower: 1.2
+}, {
+    size: 0.3,
+    candidatePower: 0.2,
+    ideologyPower: 1
+}, {
+    size: 0.5,
+    candidatePower: 0.3,
+    ideologyPower: 0.8
+}]

### 2017-03-21 paper/code/generator/scenario3.ts

@@ -1,0 +1,15 @@
+const candidates = 9
+const seats = 3
+const ideologies: Ideology[] = [{
+    size: 0.2,
+    candidatePower: 1.8,
+    ideologyPower: 0.6
+}, {
+    size: 0.3,
+    candidatePower: 1.6,
+    ideologyPower: 0.6
+}, {
+    size: 0.5,
+    candidatePower: 2,
+    ideologyPower: 0.6
+}]

### 2017-03-21 test.ts

@@ -8,21 +8,20 @@ import schulze from './schulze'
 
 const ballots = 500
 
-const candidates = 8
-const seats = 1
-
+const candidates = 9
+const seats = 3
 const ideologies: Ideology[] = [{
-    size: 0.3,
-    candidatePower: 0.6,
-    ideologyPower: 0.8
+    size: 0.2,
+    candidatePower: 1.8,
+    ideologyPower: 0.6
 }, {
     size: 0.3,
-    candidatePower: 0.8,
-    ideologyPower: 0.7
+    candidatePower: 1.6,
+    ideologyPower: 0.6
 }, {
-    size: 0.4,
-    candidatePower: 0.5,
-    ideologyPower: 0.8,
+    size: 0.5,
+    candidatePower: 2,
+    ideologyPower: 0.6
 }]
 
 
@@ -128,7 +127,8 @@ standardDeviations.push(findStandardDeviation(formattedResults.schulze.map(res =
 console.log(standardDeviations)
 
[…]

### 2017-03-21 testmethod.ts

@@ -5,7 +5,7 @@ export function findStandardDeviation(numbers: number[]): number {
 
     let d = sSquared - s
 
-    let standardDeviation = (d/(n-1))**0.5
+    let standardDeviation = (d/(n))**0.5
 
     return standardDeviation
 }

### 2017-03-21 paper/paper.tex
Spellchecked

@@
 \documentclass[12pt]{article}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage[table,xcdraw]{xcolor}
-\usepackage{hyperref}
-\usepackage{float}
-\usepackage{amsmath}
-\usepackage{mathtools}
-\usepackage{tikz}
-\usepackage{pgfplots}
-
-\pgfplotsset{compat=1.14}
-
-\hypersetup{
-	colorlinks,
-	citecolor=black,
-	filecolor=black,
-	linkcolor=black,
-	urlcolor=black
-}
-
-\usepackage[backend=biber,style=authoryear]{biblatex}
-\usepackage[newfloat]{minted}
-\usemintedstyle{vs}
-\usepackage{csquotes}
-\usepackage{caption}
-\usepackage{booktabs}
-
-\graphicspath{ {images/} }
-
-\newcommand\tab[1][1cm]{\hspace*{#1}}
-\SetupFloatingEnvironment{listing}{name=Code example}
-\definecolor{bg}{rgb}{0.95,0.95,0.95}
-\newenvironment{code}{\captionsetup{type=listing}}{}
-
-\newcommand\codeblock[3]{%
-\begin{code}
-	\caption{#3}
-	\inputminted[%
-	    mathescape,
-	    linenos,
-	    numbersep=5pt,
-	    tabsize=4,
-	    label=Helloworld,
-	    bgcolor=bg,
-	    breaklines%
-	]{TypeScript}{#1}
-	\label{#2}
-\end{code}
-}
-
-\newcommand\Code[1]{\texttt{#1}}
+\input{config.tex}
 
@@
 
-\begin{titlepage}
-	\centering
-	\vspace{2cm}
-	{\Huge Analysis of voting systems: title here\par}
-	\vspace{0.6cm}
-	{\LARGE Adrian Salamon\par}
-	\vspace{0.6cm}
-	{\Large Kungsholmens gymnasium\par}
-	\vspace{0.4cm}
-	{\large Senior thesis\par}
-	\vspace{0.6cm}
-	\includegraphics[width=0.3\textwidth]{kg}\par\vspace{1cm}
-	\vspace{4cm}
-	\vfill
-	Supervised by: \par
-	Maja Kankaanranta
-
-	\vfill
-
-	% Bottom of the page
-	{\large \today\par}
-\end{titlepage}
+\input{titlepage.tex}
 
@@
 When deciding on what systems that shall be used, it is useful to know what differences and similarities they have.
-\subsection{Purpouse}
+\subsection{Purpose}
 The purpose of this essay is to evaluate differences and similarities in terms of election results in three different voting systems: Single Transferable Vote (STV), First-Past-The-Post (FPTP) and the Schulze Method.
@@
 Theory will be here some day
+\pagebreak
 \section{Methodology}
 All voting methods have been implemented in Typescript – mostly due to the author having previous experience with JavaScript.
-Typescript is a superset of JavaScript with multiple extra feautures.
+Typescript is a superset of JavaScript with multiple extra features.
 Most importantly Typescript has optional static type checking.
-Here is some example code in typescript:
+Sample code in typescript can be seen in code example \ref{lst:typescript example}.
 \codeblock{code/typescriptexample.ts}{lst:typescript example}{Basic Typescript syntax}
@@
 In order to test the methods and their implementations, test data is needed.
-There are cases where extensive election data is published, such as in maltese elections, but full ballot data, which is needed for the implementations has not been found.
+There are cases where extensive election data is published, such as in Maltese elections, but full ballot data, which is needed for the implementations has not been found.
 Instead, the implementations will be tested with data generated from a simple computer algorithm.
-The algorithm used in this paper is highly primitive, as modeling prefrences within a population is far beyond this paper.
+The algorithm used in this paper is highly primitive, as modeling preferences within a population is far beyond this paper.
 The full ballot generation program can be found in the \Code{/generator/} folder.
-The goal of the program is to produce ballots that rank every candidate in order of prefrence (see figure \ref{fig:stv ballot} on page \pageref{fig:stv ballot}).
+The goal of the program is to produce ballots that rank every candidate in order of preference (see figure \ref{fig:stv ballot} on page \pageref{fig:stv ballot}).
 The program represents each voter in a population as belonging to a certain ideology.
-Each ideology has has a list of weighted prefrences indicating how a voter for this ideology is likely to vote.
-The weighed prefrences are generated via an abstraction.
-A single config object is used to create all ideologies.
-\codeblock{code/generator/ideologyConfig.ts}{lst:ideology config}{Configuration object for creating ideologies}
+Each ideology has has a list of weighted preferences indicating how a voter for this ideology is likely to vote.
+The weighed preferences are generated via an abstraction.
+A single configuration object is used to create all ideologies.
+\codeblock{code/generator/ideologyConfig.ts}{lst:ideology configuration}{Configuration object for creating ideologies}
 The program then works via 4 major steps:
@@
 	\item It creates a certain number of individual ballots.
-Each ballot is given an ideology and creates its own list prefrences based via weighted random number generaton according to the probability-list of the assigned ideology.
+Each ballot is given an ideology and creates its own list preferences based via weighted random number generation according to the probability-list of the assigned ideology.
 \end{enumerate}
-The output of the program is a set of ballots, where each ballot is an ordered set of prefrences.
+The output of the program is a set of ballots, where each ballot is an ordered set of preferences.
 The implementation is highly arbitrary and all constants in the program even more so.
@@
 Constructing test scenarios is difficult task.
-Due to there being so many variables both in real elections and the simulated elections in the generator program, it makes it practically inpossible to control all variables.
+Due to there being so many variables both in real elections and the simulated elections in the generator program, it makes it practically impossible to control all variables.
 Instead, 3 arbitrary test scenarios will be used.
@@
 This means that the general spread of votes will be even.
-An example of the distrubution of first-prefrence votes generated in this scenario can be seen in figure \ref{fig:example of scenario 1}.
+An example of the distribution of first-preference votes generated in this scenario can be seen in figure \ref{fig:example of scenario 1}.
 The full configuration object can be seen in code example \ref{lst:scenario 1}.
 \codeblock{code/generator/scenario1.ts}{lst:scenario 1}{Configuration object for scenario 1}
-\begin{figure}
+\begin{figure}[H]
 	\centering
-	\caption{Example distrubution of first-prefrence votes in scenario 1}
 	\begin{tikzpicture}
@@
 	\end{tikzpicture}
+	\caption{Example distribution of first-preference votes in scenario 1}
 	\label{fig:example of scenario 1}
@@
 It features a normal spread of votes between candidates.
-An example distribution of first-prefrence votes generated in this scenario can be seen in figure \ref{fig:example of scenario 2}.
+An example distribution of first-preference votes generated in this scenario can be seen in figure \ref{fig:example of scenario 2}.
 The full configuration can be seen in code example \ref{lst:scenario 2}.
@@
 	\centering
-	\caption{Example distrubution of first-prefrence votes in scenario 2}
 	\begin{tikzpicture}
@@
 	\end{tikzpicture}
+	\caption{Example distribution of first-preference votes in scenario 2}
 	\label{fig:example of scenario 2}
@@
 It features a steep spread of votes between candidates.
-An example distribution of first-prefrence votes generated in this scenario can be seen in figure \ref{fig:example of scenario 3}.
+An example distribution of first-preference votes generated in this scenario can be seen in figure \ref{fig:example of scenario 3}.
 The full configuration can be seen in code example \ref{lst:scenario 3}.
@@
 	\centering
-	\caption{Example distrubution of first-prefrence votes in scenario 3}
 	\begin{tikzpicture}
@@
 	\end{tikzpicture}
+	\caption{Example distribution of first-preference votes in scenario 3}
 	\label{fig:example of scenario 3}
@@
 \section{Specification of voting methods}
-This paper compares the results of theese voting methods
 \subsection{First-past-the-post}
 \subsubsection{Description}
-The first-past-the-post voting method is a method desiged for electing one or several candidates out of a set of candidates.
+The first-past-the-post voting method is a method designed for electing one or several candidates out of a set of candidates.
 Each voter has one (1) vote which may be allocated to any candidate.
@@
 \subsubsection{Implementation}
-The first-past-the-post program is implemented in a single file. It takes the following inputs:
+The first-past-the-post program is implemented in a single file. The inputs of the program can be seen in code example \ref{lst:fptp inputs}.
 \codeblock{code/fptp/inputs.ts}{lst:fptp inputs}{Inputs for FPTP program}
-The ballot data is first mapped to only include first prefrences. Then the algorithm loops over the ballots and gets the sum of votes for each candidate:
+The ballot data is first mapped to only include first preferences.
+Then the algorithm loops over the ballots and gets the sum of votes for each candidate.
+This process is shown in code example \ref{lst:fptp processing}.
 \codeblock{code/fptp/processing.ts}{lst:fptp processing}{Processing and formatting of data}
-The results array is sorted and sliced to only include the $N$ candidates with most votes:
+The results array is sorted and sliced to only include the $N$ candidates with most votes as seen in code example \ref{lst:fptp result calculation}.
 \codeblock{code/fptp/result.ts}{lst:fptp result calculation}{Finding and returning winning candidates}
@@
 For the sake of simplicity, in this implementation, all candidates must be ranked at unique and linear values.
-A ballot may look like this:
-\begin{figure}[H]
+An example of a ballot can be seen in figure \ref{fig:stv ballot}.	This means that there is more data available for determining the result of the election which the method can take advantage of.
+Votes are, if needed, transfered between choices within a ballot, hence the name Single Transferable Vote.
+The method relies on the concept of a quota, the number of votes you need to be elected.
+The Droop-Quota, defined as $(\frac{\text{total valid poll}}{\text{seats} + 1})+1$, is often used.
+If a candidate receives equal or more votes than the quota, he/she is elected.
+If the number of votes exceed the quota, a fraction of the votes are transfered to the next choice on the ballots that voted for the elected candidate.
+This process is repeated until there are no candidates with more votes than the quota.
+If there still are seats yet to be filled, the candidate with fewest votes is eliminated and his/her votes are transfered to the next choice on those ballots.
+This process is repeated until all seats are filled.
+The process can become quite complex with many ballots and transferring fractional votes.
+A computer is therefore essential in order to resolve large scale elections.
+\begin{figure}
 	\centering
@@
 \end{figure}
-This means that there is more data availible for detrermining the result of the election which the method can take advantage of.
-Votes are, if needed, transfered between choices within a ballot, hence the name Single Transferable Vote.
-The method relies on the concept of a quota, the number of votes you need to be elected.
-The Droop-Quota, defined as $(\frac{\text{total valid poll}}{\text{seats} + 1})+1$, is often used.
-If a candidate recieves equal or more votes than the quota, he/she is elected.
-If the number of votes exxeed the quota, a fraction of the votes are transfered to the next choice on the ballots that voted for the elected candidate.
-This process is repeated until there are no candidates with more votes than the quota.
-If there still are seats yet to be filled, the candidate with fewest votes is eliminated and his/her votes are transfered to the next choice on those ballots.
-This process is repeated until all seats are filled.
-The process can become quite complex with many ballots and transfering fractional votes.
-In order to resolve large scale elections, a computer in essential.
 \subsubsection{Justification}
 STV is an established voting method in use in several countries.
-It is used for parlimentary elections in Ireland, Malta and Australia as well as being used in local and regional elections across the world.
+It is used for parliamentary elections in Ireland, Malta and Australia as well as being used in local and regional elections across the world.
 \subsubsection{Pseudocode}
@@
 let $winners$ be the list of elected candidates \\
-let $votes$ be the set of votes with $votes_{i}$ signinfying votes for candidate $i$\\
+let $votes$ be the set of votes with $votes_{i}$ signifying votes for candidate $i$\\
 while $\left\vert{winners}\right\vert < seats$\\
@@
 \tab\tab multiply $votes_{i}$ with $(1 - \frac{\text{surplus votes}_{i}}{votes_{i}})$ \\
-\tab\tab multiply next prefrencences for $votes_{i}$ with $\frac{\text{surplus votes}_{i}}{votes_{i}}$ and \\ \tab\tab distribute into $votes$\\
+\tab\tab multiply next preferences for $votes_{i}$ with $\frac{\text{surplus votes}_{i}}{votes_{i}}$ and \\ \tab\tab distribute into $votes$\\
 \tab\tab continue \\
@@
 \tab $k \coloneqq$ index of smallest $votes_{i}$ \\
-\tab eliminate $votes_{k}$ and distribute all next-prefrence votes for candidate $k$ \tab into $votes$\\
+\tab eliminate $votes_{k}$ and distribute all next-preference votes for candidate $k$ \tab into $votes$\\
 end while
@@
 Every candidate is a top-level node with an attribute showing the number of current votes for the candidate.
-Each node has child nodes representing the next prefrences of the voters for that particular candidate, see figure \ref{fig:tree structure}.
+Each node has child nodes representing the next preferences of the voters for that particular candidate, see figure \ref{fig:tree structure}.
 It is easy to manipulate branches via recursion.
-Merging and multiplying branches is used when transfering votes from one candidate node to another.
+Merging and multiplying branches is used when transferring votes from one candidate node to another.
 A candidate node is a Typescript class.
@@
 	\includegraphics[height=200px]{Tree}
-	\caption{Simplified and shortened version of the tree structure. Each candidate is a top-level node with children, signifying the prefrences of the voters for that candidate.}
+	\caption{Simplified and shortened version of the tree structure. Each candidate is a top-level node with children, signifying the preferences of the voters for that candidate.}
 	\label{fig:tree structure}
@@
 With the \Code{add()} and \Code{multiply()} functions it is possible to recursively modify branches.
-There are two different manipulations that need to be preformed on the tree: tansfering surplus votes and eliminating candidates.
-Both functions rely on the \Code{distribute()} function wich is used to distribute a set of nodes onto the tree.
+There are two different manipulations that need to be preformed on the tree: transferring surplus votes and eliminating candidates.
+Both functions rely on the \Code{distribute()} function which is used to distribute a set of nodes onto the tree.
 \codeblock{code/stv/distribute.ts}{lst:stv distribute function}{The distribute function}
 In order to eliminate and transfer surplus votes from any candidate node $A$, the children of $A$ are passed into the distribute function.
-In the case of transfering surplus votes, the votes for each child node is first multiplied by $\frac{\text{surplus votes}}{\text{total votes}}$ as outlined in the psuedocode in section \ref{alg:stv psuedocode}.
-The full source code for funcions that manipulate the tree structure can be found in \Code{/stv/tree.ts}.
+In the case of transferring surplus votes, the votes for each child node is first multiplied by $\frac{\text{surplus votes}}{\text{total votes}}$ as outlined in the pseudocode in section \ref{alg:stv psuedocode}.
+The full source code for functions that manipulate the tree structure can be found in \Code{/stv/tree.ts}.
 
-The main procces of the program is found in the \Code{stv/election.ts} file and runs the process defined in the psuedocode in section \ref{alg:stv psuedocode} on page \pageref{alg:stv psuedocode}.
+The main process of the program is found in the \Code{stv/election.ts} file and runs the process defined in the pseudocode in section \ref{alg:stv psuedocode} on page \pageref{alg:stv psuedocode}.
 
@@
 The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate wins.
-As mentioned, this method relies on comparing the prefrences of every candidate to one another as shown in table \ref{tab:pairwise comparison matrix}.
-If there is a condorcet winner the process is simple: declare the condorcet winner a winner and run another iteration without that candidate.
+As mentioned, this method relies on comparing the preferences of every candidate to one another as shown in table \ref{tab:pairwise comparison matrix}.
+If there is a Condorcet winner the process is simple: declare the Condorcet winner a winner and run another iteration without that candidate.
 Repeat this process until all seats are filled.
-However, there can be condorcet ties, where there is no condorcet winner.
+However, there can be Condorcet ties, where there is no Condorcet winner.
 There are multiple ways of resolving the tie, one of them being the Schulze Method.
@@
 The path is said to have the $strength$ of the weakest link in the path.
-In this example, the path strenght between A and B is 27 due to the link between $C$ and $B$ having a strenght of 27.
+In this example, the path strength between A and B is 27 due to the link between $C$ and $B$ having a strength of 27.
 There may be several paths between two candidates and the goal of the process is to find the strongest path between any candidate $A$ and $B$, written as $p[A,B]$.
-By finding the strongest path between all nodes a result can be obtained where $p[X,Y] \geq p[Y,X]$ wich means that candidate $X$ wins.
-The Shulze Method also provides a linear ranking between all candidates, for example that $E > B > A > C > D$.
+By finding the strongest path between all nodes a result can be obtained where $p[X,Y] \geq p[Y,X]$ which means that candidate $X$ wins.
+The Schulze Method also provides a linear ranking between all candidates, for example that $E > B > A > C > D$.
 By selecting the $N$ top candidates you can use the method for a multi-seat election.
@@
 The problem is called the widest path problem in graph theory.
-An efficent and relatively simple way to compute this problem is via the Floyd-Warshall algorithm which is used in the implementation.
+An efficient and relatively simple way to compute this problem is via the Floyd-Warshall algorithm which is used in the implementation.
 See \ref{lst:schulze algorithm} for the full algorithm.
 
-\begin{table}[H]
+\begin{table}
 \centering
+\caption{Pairwise comparison matrix used in the Schulze method. For example, 17 ballots prefer $A>B$ and 33 ballots prefer $B>A$.}
 \begin{tabular}{l|c|c|c|c|c|}
@@
 \end{tabular}
-\caption{Pairwise comparison matrix used in the Schulze Mehtod. For example, 17 ballots prefer $A>B$ and 33 ballots prefer $B>A$.}
 \label{tab:pairwise comparison matrix}
@@
 \subsubsection{Justification}
-The Shulze Method is used by multiple organisations around the world.
-It has been used by various software organisations such as The Wikimedia Foundation, The Debian Project and Ubuntu.
+The Schulze method is used by multiple organizations around the world.
+It has been used by various software organizations such as The Wikimedia Foundation, The Debian Project and Ubuntu.
 It is also used by political parties such as the Pirate Party in Sweden and various other countries.
@@
 \tab\tab\tab\tab $p[i,j] \coloneqq 0$\\
-\tab\tab\tab endif \\
-\tab\tab endif \\
-\tab endfor \\
-endfor\\
+\tab\tab\tab end if \\
+\tab\tab end if \\
+\tab end for \\
+end for\\
 for $i$ from 1 to $C$\\
@@
 \tab\tab\tab\tab\tab $p[j,k] \coloneqq \text{max }(p[j,k], \text{ min }(p[j,k], p[i,k]))$\\
-\tab\tab\tab\tab endif \\
-\tab\tab\tab endfor \\
-\tab\tab endif \\
-\tab endfor \\
-endfor\\
+\tab\tab\tab\tab end if \\
+\tab\tab\tab end for \\
+\tab\tab end if \\
+\tab end for \\
+end for\\
 \subsubsection{Implementation}
-The Shulze Method is implemented within the file \Code{schulze/index.ts}.
+The Schulze Method is implemented within the file \Code{schulze/index.ts}.
 It takes two inputs: a list of ballots and the number of seats to be elected.
@@
 The output of the program is a list of winners.
-The program first creates the matrices for both the prefrences and paths between candidates.
+The program first creates the matrices for both the preferences and paths between candidates.
 \codeblock{code/schulze/maps.ts}{lst:schulze maps}{Data representation}
-The program then runs the algorithm outlined in the psuedocode in section \ref{alg:schulze psuedocode}.
+The program then runs the algorithm outlined in the pseudocode in section \ref{alg:schulze psuedocode}.
 \codeblock{code/schulze/algorithm.ts}{lst:schulze algorithm}{Main algorithm}
@@
 Scenario 1 featured 8 candidates where one was to be elected.
-Vote spread was flat, meaning that votes tend to be diverse in their prefrences.
-This means that there is not an abvious winner present.
-This can be seen from the first-prefrence votes in the scenario seen in figure \ref{fig:example of scenario 1}.
+Vote spread was flat, meaning that votes tend to be diverse in their preferences.
+This means that there is not an obvious winner present.
+This can be seen from the first-preference votes in the scenario seen in figure \ref{fig:example of scenario 1}.
 The full result in this scenario can be seen in figure \ref{fig:scenario 1 results}.
@@
 Key metrics for the results in this scenario can be found in table \ref{tab:scenario 1 result}.
+Although the misrepresentation metric is not entirely accurate, especially when few seats are elected, it shows that fptp is not entirely representative.
+The STV and Schulze method seem to return very similar results.
 \begin{figure}
@@
 	\end{tikzpicture}
-	\caption{Figure thingy}
+	\caption{Results in scenario 1}
 	\label{fig:scenario 1 results}
@@
 
-\begin{table}[H]
+\begin{table}
 \centering
@@
 \toprule
-Method & Standard deviation & Missrepresentation & Most likely winners \\ \midrule
+Method & Standard deviation & Misrepresentation & Most likely winners \\ \midrule
 FPTP & 223 & 67\% & 2 \\
@@
 \subsection{Scenario 2}
-\begin{figure}[H]
+Scenario 2 featured 9 candidates of which 3 were to be elected.
+The distribution of votes was "normal", and as seen in figure \ref{fig:example of scenario 2}, the election is very close with many candidates having a similar percentage of first-preference votes.
+The results obtained in scenario 2 are very interesting.
+FPTP tended to underrepresent candidate 1, and elected a candidate from ideology 2 only in 28\% of elections, despite the ideology theoretically having 30\% of popular support.
+The Schulze method also tended to underrepresent ideology 2.
+It instead overrepresented ideology 2, electing 3 candidates of ideology 2 in 50\% of elections.
+This indicates that the Schulze method is not a representative method in a multi-seat election.
+The STV result showed less misrepresentation than the FPTP result, which was to be expected since the method has access to more data of any voter's preferences.
+The results in scenario 2 can be observed in figure \ref{fig:scenario 2 result} and the key metrics can be seen in table \ref{tab:scenario 2 result}.
+\begin{figure}
 	\centering
@@
 	\end{tikzpicture}
-	\caption{Figure thingy numero duo}
+	\caption{Results in scenario 2}
 	\label{fig:scenario 2 result}
@@
 \toprule
-Method & Standard deviation & Missrepresentation & Most likely winners \\ \midrule
+Method & Standard deviation & Misrepresentation & Most likely winners \\ \midrule
 FPTP & 418 & 42\% & 0, 2 \& 5 \\
@@
 \subsection{Scenario 3}
+Scenario 3 featured 9 candidates of which 3 were to be elected.
+The distribution of votes was steep.
+This can be seen by the first-preference votes in figure \ref{fig:example of scenario 3}.
+The results obtained with each method in this scenario are practically identical.
+From this, it can be inferred that the results of the methods converge as the preferences in a population become more clear.
+The results obtained in this scenario can be seen in figure \ref{fig:scenario 3 result}.
+The key metrics can be found in table \ref{tab:scenario 3 result}.
 \begin{figure}[H]
@@
 	\end{tikzpicture}
-	\caption{Figure thingy tré}
+	\caption{Results in scenario 3}
 	\label{fig:scenario 3 result}
@@
 		\toprule
-Method & Standard deviation & Missrepresentation & Most likely winners \\ \midrule
+		Method & Standard deviation & Misrepresentation & Most likely winners \\ \midrule
 		FPTP & 470 & 33\% & 0, 1 \& 2 \\
 		STV & 471 & 33\% & 0, 1 \& 2 \\
-Schulze & 471 & 3\% & 0, 1 \& 2  \\ \bottomrule
+		Schulze & 471 & 33\% & 0, 1 \& 2  \\ \bottomrule
 	\end{tabular}
@@
 Proportionalities: 1:67,7,9 2:42,14,67, 3:33,33,33
-
-%\subsection{ Heading Here}
-%This is some code.
-%\lstinputlisting[language=JavaScript]{code/examples/example.js}
-
-%\section{Conclusion}
-%Write your conclusion here. And here is a citation:
-%\textcite{sigfridsson2}
-
-%And another one here (\textcite{sigfridsson})
-
-%\section{Source code}
-%\lstinputlisting[language=JavaScript]{code/test.js}
 

### 2017-03-21 fptp/index.ts
Linted

@@ -13,7 +13,7 @@ export default function calculateWinners(input: number[][], seats: number) {
 
     let results: Result[] = []
     // Loops over prefrences and adds/increments result
-    for (var i = 0; i < firstPrefrences.length; i++) {
+    for (let i = 0; i < firstPrefrences.length; i++) {
         // Finds index in results array of candidate at i
         let index = results.findIndex(obj => obj.cand === firstPrefrences[i])
         // If candidate is not added to results
@@ -21,7 +21,7 @@ export default function calculateWinners(input: number[][], seats: number) {
             results.push({ cand: firstPrefrences[i], votes: 1 })
         } else {
             // Increment count if already added in results
-            results[index].votes += 1;
+            results[index].votes += 1
         }
     }
 

### 2017-03-21 generator/ballots.ts

@@ -5,7 +5,7 @@ import { Ideology, IdeologyWithProbabilities } from './interfaces'
 function generateBallots(numberOfBallots: number, prob: number[], candidates: number[]): number[][] {
     // Create temp array combining probability and possib
     let temp: number[][] = []
-    for (var i = 0; i < candidates.length; i++) {
+    for (let i = 0; i < candidates.length; i++) {
         temp.push([prob[i], candidates[i]])
     }
 
@@ -29,7 +29,7 @@ function generateBallots(numberOfBallots: number, prob: number[], candidates: nu
 
     let ballots: number[][] = []
 
-    for (var i = 0; i < numberOfBallots; i++) {
+    for (let i = 0; i < numberOfBallots; i++) {
         const votes = distributeVotes(temp)
         ballots.push(votes)
         //console.log(temp)
@@ -42,7 +42,7 @@ function generateBallots(numberOfBallots: number, prob: number[], candidates: nu
 export function createAllBallots(ideologies: Ideology[], ideologyProbabilities: IdeologyWithProbabilities[], ballots: number): number[][] {
     let result: number[][] = []
 
-    for (var i = 0; i < ideologies.length; i++) {
+    for (let i = 0; i < ideologies.length; i++) {
         const ideology = ideologies[i]
         const ideologyProbability = ideologyProbabilities[i]
 
@@ -63,7 +63,7 @@ function distributeVotes(temp: number[][]): number[] {
     while (index > 0) {
         const rand = Math.random()
         // Loops through the temp array
-        for (var i = 0; i < candidates.length; i++) {
+        for (let i = 0; i < candidates.length; i++) {
             // Gets the value of the party size
             const val = candidates[i][0]
             // The first value that is greater than the random number 

### 2017-03-21 generator/candidates.ts

@@ -15,8 +15,9 @@ export function createCandidates(numberOfCandidates: number, ideologies: Ideolog
 
             // Loops through all ideologies
             for (let ideologyIndex = 0; ideologyIndex < tempIdeologies.length; ideologyIndex++) {
-                if(numberOfCandidates <= 0)
+                if(numberOfCandidates <= 0) {
                     break
+                }
                 
                 // Current ideology in loop
                 const ideology = tempIdeologies[ideologyIndex]
@@ -50,13 +51,15 @@ export function assignProbabilityToIdeology(ideologies: Ideology[], candidates: 
     let result: IdeologyWithProbabilities[] = []
 
     // Loops through each ideology
-    for (var ideologyIndex = 0; ideologyIndex < ideologies.length; ideologyIndex++) {
+    for (let ideologyIndex = 0; ideologyIndex < ideologies.length; ideologyIndex++) {
         let ideology = ideologies[ideologyIndex]
         // Maps parties and sets the size according to ideology
         const withProbabilities = candidates.map(candidate => {
             if (candidate.ideology === ideologyIndex) {
                 // Increases probability of voting for party aligned with ideology
-                return candidate.size * 8 * (ideology.ideologyPower**2)
+                if (candidate.size) {
+                    return candidate.size * 8 * (ideology.ideologyPower**2)
+                }
             } else {
                 return candidate.size
             }
@@ -79,7 +82,7 @@ export function assignProbabilityToIdeology(ideologies: Ideology[], candidates: 
 // Assigns relative sizes to all parties based on their ideologies
 function assignCandidateSizes(candidates: Candidate[], ideologies: IdeologyWithCandidates[]): Candidate[] {
     // Loops through all ideologies
-    for (var ideologyIndex = 0; ideologyIndex < ideologies.length; ideologyIndex++) {
+    for (let ideologyIndex = 0; ideologyIndex < ideologies.length; ideologyIndex++) {
         const ideology = ideologies[ideologyIndex]
         // Calculates a distribution of sizes of parties within an ideology
         let ideologySizeList = calculateDistribution(ideology.numberOfCandidates, ideology.candidatePower)
@@ -88,7 +91,9 @@ function assignCandidateSizes(candidates: Candidate[], ideologies: IdeologyWithC
         candidates = candidates.map((candidate) => {
             if (candidate.ideology === ideologyIndex) {
                 // Shifts the size from the array
-                const size = ideologySizeList.shift() * ideology.size
[…]

### 2017-03-21 schulze/index.ts

@@ -19,18 +19,18 @@ export default function calculateResult(input: number[][], seats: number): numbe
     let c = input[0].length
 
     // Fills p with a bunch of zeroes
-    for (var i = 0; i < c; i++) {
+    for (let i = 0; i < c; i++) {
         p[i] = {}
-        for (var j = 0; j < c; j++) {
+        for (let j = 0; j < c; j++) {
             if (i !== j) {
                 p[i][j] = 0
             }
         }
     }
 
-    // Computing strongest path strength. Variant of the Floyd-Warshall algorithm
-    for (var i = 0; i < c; i++) {
-        for (var j = 0; j < c; j++) {
+    // Computing strongest path strength. letiant of the Floyd-Warshall algorithm
+    for (let i = 0; i < c; i++) {
+        for (let j = 0; j < c; j++) {
             if (i !== j) {
                 if (d[i][j] > d[j][i]) {
                     p[i][j] = d[i][j]
@@ -41,10 +41,10 @@ export default function calculateResult(input: number[][], seats: number): numbe
         }
     }
 
-    for (var i = 0; i < c; i++) {
-        for (var j = 0; j < c; j++) {
+    for (let i = 0; i < c; i++) {
+        for (let j = 0; j < c; j++) {
             if (i !== j) {
-                for (var k = 0; k < c; k++) {
+                for (let k = 0; k < c; k++) {
                     if (i !== k && j !== k) {
                         p[j][k] = Math.max(p[j][k], Math.min(p[j][i], p[i][k]))
                     }
@@ -64,17 +64,17 @@ function getPairs(ballots: number[][]): PairMap {
     let p = {}
 
     // Loops throug all ballots
-    for (var k = 0; k < ballots.length; k++) {
-        var ballot = ballots[k];
+    for (let k = 0; k < ballots.length; k++) {
+        let ballot = ballots[k]
         // Temp array that stores which candidates are prefered over current candidate in the loop
         let preferred: number[] = []
         //Loops through each ballot
-        for (var i = 0; i < ballot.length; i++) {
-            var vote = ballot[i];
+        for (let i = 0; i < ballot.length; i++) {
+            let vote = ballot[i]
             // Loops through the preferred array
-            for (var j = 0; j < preferred.length; j++) {
+            for (let j = 0; j < preferred.length; j++) {
                 // Current preferred vote
-                let preferredVote = preferred[j];
+                let preferredVote = preferred[j]
[…]

### 2017-03-21 stv/candidate.ts

@@ -5,8 +5,8 @@ export default class CandidateNode {
     public children: CandidateNode[]
 
     constructor(cand: number, count: number) {
-        this.cand = cand;
-        this.count = count;
+        this.cand = cand
+        this.count = count
         this.children = []
     }
 
@@ -23,7 +23,7 @@ export default class CandidateNode {
         children = children.concat(otherChildren.filter(child => children.indexOf(child) < 0))
 
         // Loops through children and pushes them to new node
-        for (var i = 0; i < children.length; i++) {
+        for (let i = 0; i < children.length; i++) {
             newNode.children.push(addChildren(this.children, other.children, children[i]))
         }
 
@@ -49,13 +49,14 @@ function addChildren(aChildren: CandidateNode[], bChildren: CandidateNode[], chi
     // A has the child and B has the child
     const aHas = aChildren.some(obj => obj.cand === child)
     const bHas = bChildren.some(obj => obj.cand === child)
-    let aIndex, bIndex;
+    let aIndex, bIndex
     // Finds index of child if they exist in array
-    if (aHas)
-        aIndex = aChildren.findIndex(item => item.cand == child)
-    if (bHas)
-        bIndex = bChildren.findIndex(item => item.cand == child)
-
+    if (aHas) {
+        aIndex = aChildren.findIndex(item => item.cand === child)
+    }
+    if (bHas) {
+        bIndex = bChildren.findIndex(item => item.cand === child)
+    }
     /*
     If they both have the child, add the trees together
     Else return the node that exclusively has the child

### 2017-03-21 stv/election.ts

@@ -20,7 +20,7 @@ export function runElection(input: number[][], seats: number): Result {
         // Check for winners
         let newWinners: number[] = []
         // Loops through tree
-        for (var i = 0; i < tree.length; i++) {
+        for (let i = 0; i < tree.length; i++) {
             const cand = tree[i]
             // If the count of candidate is greater than quota and the candidate is not a winner
             if(cand.count >= quota && !winners.includes(cand.cand)){
@@ -39,7 +39,7 @@ export function runElection(input: number[][], seats: number): Result {
         // Loop while there is a surplus of votes for a candidate
         while(isSurplus(tree, quota)) {
             // Loop through tree 
-            for (var i = 0; i < tree.length; i++) {
+            for (let i = 0; i < tree.length; i++) {
                 const cand = tree[i]
                 if(cand.count >= quota) {
                     // Transfer the surplus
@@ -57,8 +57,8 @@ export function runElection(input: number[][], seats: number): Result {
         // Checks if there are an equal number of candidates left as seats to be elected. If so, elect all
         let allSeatsFilled = false
         if (tree.length === seats) {
-            for (var i = 0; i < tree.length; i++) {
-                var cand = tree[i];
+            for (let i = 0; i < tree.length; i++) {
+                let cand = tree[i]
                 if (!winners.includes(cand.cand)) {
                     allSeatsFilled = true
                     winners = [...winners, cand.cand]
@@ -72,9 +72,10 @@ export function runElection(input: number[][], seats: number): Result {
         // Eliminate lowest ranked
         // Finds the lowest ranked candidate. This is a bad algorithm I will need to fix later.
         let lowestRanked = 0
-        for (var i = 0; i < tree.length; i++) {
-            if (tree[i].count < tree[lowestRanked].count)
+        for (let i = 0; i < tree.length; i++) {
+            if (tree[i].count < tree[lowestRanked].count) {
                 lowestRanked = i
+            }
         }
         log.push(`Eliminated candidate ${tree[lowestRanked].cand}`)
         // Eliminates candidate

### 2017-03-21 stv/tree.ts

@@ -22,7 +22,7 @@ export function buildTree(ballots: number[][]): CandidateNode[] {
                 level.push(new CandidateNode(cand, 0))
             }
             // Find index of current candidate in tree
-            const candIndex = level.findIndex(item => item.cand == cand)
+            const candIndex = level.findIndex(item => item.cand === cand)
             // Increment the count for the node
             level[candIndex].count += 1
             // Move down one level
@@ -85,7 +85,7 @@ export function transferSurplus(candNumber: number, tree: CandidateNode[], quota
 function distribute(nodeList: CandidateNode[], tree: CandidateNode[], winners: number[]): CandidateNode[] {
     // Loops through each candidate node in the list
     for (let i = 0; i < nodeList.length; i++) {
-        let cand = nodeList[i];
+        let cand = nodeList[i]
         // Find if candidate is in the tree and/or is a winner
         let itExistsInTree = tree.some(obj => obj.cand === cand.cand)
         let isWinner = winners.includes(cand.cand)

### 2017-03-21 test.ts

@@ -24,12 +24,11 @@ const ideologies: Ideology[] = [{
     ideologyPower: 0.6
 }]
 
-
 //let input = [[0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [2, 0, 1, 4, 3], [2, 0, 1, 4, 3], [2, 0, 1, 4, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 1, 0, 3, 4], [2, 1, 0, 3, 4], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2]]
 
 let results: Array<{ stv: number[], fptp: number[], schulze: number[], }> = []
 
-for (var j = 0; j < 1000; j++) {
+for (let j = 0; j < 1000; j++) {
     console.log(j)
     let input = generateBallots(ideologies, candidates, ballots)
 
@@ -54,7 +53,7 @@ interface FormattedResults {
 let formattedResults: FormattedResults = { stv: [], fptp: [], schulze: [] }
 
 for (let i = 0; i < results.length; i++) {
-    let election = results[i];
+    let election = results[i]
     formattedResults.fptp = [...addVotes(candidates, election.fptp, formattedResults.fptp)]
[…]

### 2017-03-22 paper/paper.tex
Testing preformance gains

@@
 \end{figure}
+\begin{figure}[H]
+	\centering
+	\begin{tikzpicture}
+		\begin{axis}[
+			ybar stacked,
+			width = 0.9\textwidth,
+			height = 0.5\textwidth,
+			legend style={at={(0.5,-0.25)},
+			anchor=north,legend columns=-1},
+      x tick style = transparent,
+			ylabel = {First prefrence votes},
+			xlabel = {Candidate},
+			ymajorgrids = true,
+      ymin = 0,
+			yticklabel={\pgfmathprintnumber\tick\%}
+      ]
+			\addplot coordinates
+			{(0, 27)(1, 0)(2, 0)(3, 17)(4, 0)(5, 0)(6, 0)(7, 0)(8, 0)};
+			\addplot coordinates
+			{(0, 0)(1, 27)(2, 0)(3, 0)(4, 41)(5, 0)(6, 56)(7, 0)(8, 0)};
+			\addplot coordinates
+			{(0, 0)(1, 0)(2, 89)(3, 0)(4, 0)(5, 79)(6, 0)(7, 79)(8, 85)};
+			\legend{Ideology 1, Ideology 2, Ideology 3}
+		\end{axis}
+	\end{tikzpicture}
+	\caption{Example distribution of first-preference votes in scenario 4}
+	\label{fig:example of scenario 4}
+\end{figure}
 
@@
 An example of a ballot can be seen in figure \ref{fig:stv ballot}.	This means that there is more data available for determining the result of the election which the method can take advantage of.
-Votes are, if needed, transfered between choices within a ballot, hence the name Single Transferable Vote.
+Votes are, if needed, transferred between choices within a ballot, hence the name Single Transferable Vote.
 The method relies on the concept of a quota, the number of votes you need to be elected.
@@
 If a candidate receives equal or more votes than the quota, he/she is elected.
-If the number of votes exceed the quota, a fraction of the votes are transfered to the next choice on the ballots that voted for the elected candidate.
+If the number of votes exceed the quota, a fraction of the votes are transferred to the next choice on the ballots that voted for the elected candidate.
 This process is repeated until there are no candidates with more votes than the quota.
-If there still are seats yet to be filled, the candidate with fewest votes is eliminated and his/her votes are transfered to the next choice on those ballots.
+If there still are seats yet to be filled, the candidate with fewest votes is eliminated and his/her votes are transferred to the next choice on those ballots.
 This process is repeated until all seats are filled.
@@
 \end{figure}
+
+\begin{figure}[H]
+	\centering
+	\begin{tikzpicture}
+		\begin{axis}[
+			ybar,
+			width = 0.9\textwidth,
+			height = 0.5\textwidth,
+			legend style={at={(0.5,-0.25)},
+			anchor=north,legend columns=-1},
+      x tick style = transparent,
+			ylabel = {Elections won},
+			xlabel = {Candidate},
+			ymajorgrids = true,
+			every axis plot/.append style={draw=none,fill,no markers},
+      ymin = 0,
+			symbolic x coords={0,1,2,3,4,5,6,7,8},
+			bar width=0.25cm
+      ]
+			\addplot coordinates
+			{(0, 0)(1, 0)(2, 737)(3, 0)(4, 0)(5, 738)(6, 0)(7, 743)(8, 782)};
+			\addplot coordinates
+			{(0, 0)(1, 0)(2, 756)(3, 0)(4, 0)(5, 737)(6, 0)(7, 736)(8, 771)};
+			\addplot coordinates
+			{(0, 0)(1, 0)(2, 766)(3, 0)(4, 0)(5, 752)(6, 0)(7, 746)(8, 736)};
+			\legend{FPTP, STV, Schulze}
+			\end{axis}
+	\end{tikzpicture}
+	\caption{Results in scenario 4}
+	\label{fig:scenario 4 result}
+\end{figure}
+
 \begin{table}[H]

### 2017-03-22 generator/ballots.ts

@@ -39,14 +39,13 @@ function generateBallots(numberOfBallots: number, prob: number[], candidates: nu
     return ballots
 }
 
-export function createAllBallots(ideologies: Ideology[], ideologyProbabilities: IdeologyWithProbabilities[], ballots: number): number[][] {
+export function createAllBallots(ideologyProbabilities: IdeologyWithProbabilities[], ballots: number): number[][] {
     let result: number[][] = []
 
-    for (let i = 0; i < ideologies.length; i++) {
-        const ideology = ideologies[i]
-        const ideologyProbability = ideologyProbabilities[i]
+    for (let i = 0; i < ideologyProbabilities.length; i++) {
+        const ideology = ideologyProbabilities[i]
 
-        const arrOfBallots = generateBallots(ideology.size*ballots, ideologyProbability.probabilities , ideologyProbability.candidates)
+        const arrOfBallots = generateBallots(ideology.size*ballots, ideology.probabilities , ideology.candidates)
 
         result = result.concat(arrOfBallots)
     }

### 2017-03-22 generator/candidates.ts

@@ -70,7 +70,7 @@ export function assignProbabilityToIdeology(ideologies: Ideology[], candidates: 
         // IDK why I have it here. Not needed but who knows. Creates array of 1,2,3...
         const candidateList = Array(candidates.length).fill(0).map((val, index) => index)
         // Assigns values to ideology
-        result = [...result, {probabilities: normalized, candidates: candidateList}]
+        result = [...result, {size: ideology.size, probabilities: normalized, candidates: candidateList}]
         //ideologies[ideologyIndex] = Object.assign({}, ideology, {probabilities: normalized, parties: partyList})
 
     }
@@ -92,7 +92,7 @@ function assignCandidateSizes(candidates: Candidate[], ideologies: IdeologyWithC
             if (candidate.ideology === ideologyIndex) {
                 // Shifts the size from the array
                 let shift = ideologySizeList.shift()
-                const size: number = shift ? ideology.size : 0
+                const size: number = shift ? shift*ideology.size : 0
                 
                 // Creates a new object and returns it to the array
                 const newCandidate = Object.assign({}, candidate, {size})

### 2017-03-22 generator/index.ts

@@ -6,12 +6,16 @@ import { Ideology, IdeologyWithProbabilities } from './interfaces'
 import { createCandidates, assignProbabilityToIdeology } from './candidates'
 import { createAllBallots } from './ballots'
 
-export default function generateBallots(ideologies: Ideology[], numberOfcandidates: number, numberOfBallots: number): number[][] {
+
+export function generateBallots(ideologies: IdeologyWithProbabilities[], numberOfBallots: number): number[][] {
+
+    const result = createAllBallots(ideologies, numberOfBallots)
+    
+    return result
+}
+
+export function createIdeologyProbabilities(ideologies: Ideology[], numberOfcandidates: number): IdeologyWithProbabilities[] {
     const candidates = createCandidates(numberOfcandidates, ideologies)
 
-    const ideologyProbabilities: IdeologyWithProbabilities[] = assignProbabilityToIdeology(ideologies, candidates)
-
-    const result = createAllBallots(ideologies, ideologyProbabilities, numberOfBallots)
-
-    return result
+    return assignProbabilityToIdeology(ideologies, candidates)
 }

### 2017-03-22 generator/interfaces.ts

@@ -13,6 +13,7 @@ export interface IdeologyWithCandidates {
 }
 
 export interface IdeologyWithProbabilities {
+    size: number,
     probabilities: number[],
     candidates: number[]
 }

### 2017-03-22 test.ts

@@ -1,5 +1,5 @@
-import { Ideology } from './generator/interfaces'
-import generateBallots from './generator'
+import { Ideology, IdeologyWithProbabilities } from './generator/interfaces'
+import { createIdeologyProbabilities, generateBallots} from './generator'
 
 import fptp from './fptp'
 import { runElection as stv } from './stv'
@@ -28,13 +28,15 @@ const ideologies: Ideology[] = [{
 
 let results: Array<{ stv: number[], fptp: number[], schulze: number[], }> = []
 
+let ideologyData: IdeologyWithProbabilities[] = createIdeologyProbabilities(ideologies, candidates)
+let start = Date.now()
 for (let j = 0; j < 1000; j++) {
     console.log(j)
-    let input = generateBallots(ideologies, candidates, ballots)
-
+    let input = generateBallots(ideologyData, ballots)
     results.push({ stv: stv(input, seats).winners, fptp: fptp(input, seats), schulze: schulze(input, seats) })
 }
 
+console.log(`Done loop. Took ${(Date.now()-start)/1000} s`)
 interface FormattedResults {
     stv: Array<{
         candidate: number,
@@ -127,7 +129,7 @@ console.log(standardDeviations)
 
[…]

### 2017-03-27 paper/paper.tex
Wrote outline for conclusion

@@
 
-\begin{figure}[H]
-	\centering
-	\begin{tikzpicture}
-		\begin{axis}[
-			ybar,
-			width = 0.9\textwidth,
-			height = 0.5\textwidth,
-			legend style={at={(0.5,-0.25)},
-			anchor=north,legend columns=-1},
-      x tick style = transparent,
-			ylabel = {Elections won},
-			xlabel = {Candidate},
-			ymajorgrids = true,
-			every axis plot/.append style={draw=none,fill,no markers},
-      ymin = 0,
-			symbolic x coords={0,1,2,3,4,5,6,7,8},
-			bar width=0.25cm
-      ]
-			\addplot coordinates
-			{(0, 0)(1, 0)(2, 737)(3, 0)(4, 0)(5, 738)(6, 0)(7, 743)(8, 782)};
-			\addplot coordinates
-			{(0, 0)(1, 0)(2, 756)(3, 0)(4, 0)(5, 737)(6, 0)(7, 736)(8, 771)};
-			\addplot coordinates
-			{(0, 0)(1, 0)(2, 766)(3, 0)(4, 0)(5, 752)(6, 0)(7, 746)(8, 736)};
-			\legend{FPTP, STV, Schulze}
-			\end{axis}
-	\end{tikzpicture}
-	\caption{Results in scenario 4}
-	\label{fig:scenario 4 result}
-\end{figure}
-
 \begin{table}[H]
@@
 \end{table}
+Proportionalities: 1:67,7,9 2:42,14,67, 3:33,33,33
 
-%[ 469.99669029568, 471.40452079103, 471.16899539573 ]
 \section{Conclusion}
-Proportionalities: 1:67,7,9 2:42,14,67, 3:33,33,33
+The results obtained in the three different scenarios provide some insight into the varying properties of the different voting systems.
+Each of the scenarios showed different behaviors for the different methods.
+For instance, the methods provided practically the same result in scenario 3 but wildly varying results in scenario 2.
+While the testing method used in this paper may not have been the most robust way of comparing the voting methods, several conclusions can be drawn from the data.
+I outline them in 4 points below.
+\begin{itemize}
+	\item Schulze did not seem like a proportional voting method in multi-seat elections.
+	\item In single-seat elections, Schulze and STV (and IRV in extension) seemed to provide similar results.
+	\item FPTP did not seem like a very proportional method in close elections.
+	\item STV seems to be the most proportional method out of the 3 tested, but is not without its flaws.
+\end{itemize}
+Summary:
+There is no perfect voting system.
+Generally, if you want proportional representation (which in a democracy you want), STV will likely be the best method to use out of the methods covered in this paper.
+Modeling of data needs more work, as well as including other methods (such as ...). More research is needed.
 

### 2017-04-02 paper/paper.tex
Added pdf
Reorganized project and fixed referencing

@@
 
-\addbibresource{sample.bib}
+\addbibresource{references.bib}
 
@@
 \end{figure}
-\begin{figure}[H]
-	\centering
-	\begin{tikzpicture}
-		\begin{axis}[
-			ybar stacked,
-			width = 0.9\textwidth,
-			height = 0.5\textwidth,
-			legend style={at={(0.5,-0.25)},
-			anchor=north,legend columns=-1},
-      x tick style = transparent,
-			ylabel = {First prefrence votes},
-			xlabel = {Candidate},
-			ymajorgrids = true,
-      ymin = 0,
-			yticklabel={\pgfmathprintnumber\tick\%}
-      ]
-			\addplot coordinates
-			{(0, 27)(1, 0)(2, 0)(3, 17)(4, 0)(5, 0)(6, 0)(7, 0)(8, 0)};
-			\addplot coordinates
-			{(0, 0)(1, 27)(2, 0)(3, 0)(4, 41)(5, 0)(6, 56)(7, 0)(8, 0)};
-			\addplot coordinates
-			{(0, 0)(1, 0)(2, 89)(3, 0)(4, 0)(5, 79)(6, 0)(7, 79)(8, 85)};
-			\legend{Ideology 1, Ideology 2, Ideology 3}
-		\end{axis}
-	\end{tikzpicture}
-	\caption{Example distribution of first-preference votes in scenario 4}
-	\label{fig:example of scenario 4}
-\end{figure}
-
 \pagebreak
@@
 \subsubsection{Description}
-The Schulze Method is a method used mainly to determine results in a single-winner election but can also be used to provide rankings and elect multiple candidates in a single election.
+The Schulze Method is a method used mainly to determine results in a single-winner election but can also be used to provide rankings and elect multiple candidates in a single election \autocite{Schulze2011}.
 Ballots are identical to those of the single transferable vote, see figure \ref{fig:stv ballot} on page \pageref{fig:stv ballot}.
@@
 There are multiple ways of resolving the tie, one of them being the Schulze Method.
+\ref{}
 
@@
 for $i$ from 1 to $C$\\
-\tab for $j$ form 1 to $C$\\
+\tab for $j$ from 1 to $C$\\
 \tab\tab if ($i \ne j$)\\
@@
 \end{table}
-Proportionalities: 1:67,7,9 2:42,14,67, 3:33,33,33
-
 \section{Conclusion}
@@
 I outline them in 4 points below.
-\begin{itemize}
-	\item Schulze did not seem like a proportional voting method in multi-seat elections.
-	\item In single-seat elections, Schulze and STV (and IRV in extension) seemed to provide similar results.
-	\item FPTP did not seem like a very proportional method in close elections.
-	\item STV seems to be the most proportional method out of the 3 tested, but is not without its flaws.
-\end{itemize}
+\begin{enumerate}
+	\item Schulze did not seem like a proportional voting method in multi-seat elections. ...
+	\item In single-seat elections, Schulze and STV (and IRV in extension) seemed to provide similar results. ...
+	\item FPTP did not seem like a very proportional method in close elections. ...
+	\item STV seems to be the most proportional method out of the 3 tested, but is not without its flaws. ...
+\end{enumerate}
 Summary:
@@
 
+Todo:
+\begin{itemize}
+	\item Write theory
+	\item Add references where needed
+	\item Explain metrics used to evaluate results
+	\item Cut down on explanation of fptp
+	\item Write abstract
+	\item Finish summary
+\end{itemize}
+
 \pagebreak
@@
 
-\section{Appendix}
-First-past-the-post program
-
 \end{document}

### 2017-04-02 stv/election.ts

@@ -6,7 +6,7 @@ interface Result {
 }
 
 // Calculates election result in an STV election
-export function runElection(input: number[][], seats: number): Result {
+export default function runElection(input: number[][], seats: number): Result {
     let winners: number[] = []
     let log: string[] = []
     // Droop quota

### 2017-04-02 stv/index.ts

@@ -1,2 +1,3 @@
-export { runElection } from './election'
+import stv from './election'
+export default stv
 

### 2017-04-02 testing/standardDeviation.ts

@@ -1,4 +1,4 @@
-export function findStandardDeviation(numbers: number[]): number {
+export default function (numbers: number[]): number {
     let n = numbers.length
     let s = (numbers.reduce((a,b) => a+b)**2)/n
     let sSquared = numbers.map(a => a**2).reduce((a,b) => a+b)

### 2017-04-02 testing/test.ts

@@ -1,9 +1,39 @@
-import { Ideology, IdeologyWithProbabilities } from './generator/interfaces'
-import { createIdeologyProbabilities, generateBallots} from './generator'
+// This file was used in doing the testing needed to obtain results for the paper
 
-import fptp from './fptp'
-import { runElection as stv } from './stv'
-import schulze from './schulze'
+
+import { Ideology, IdeologyWithProbabilities } from '../generator/interfaces'
+import { createIdeologyProbabilities, generateBallots} from '../generator'
+import getStandardDeviation from './standardDeviation'
+
+import fptp from '../fptp'
+import stv  from '../stv'
+import schulze from '../schulze'
+
+interface Result {
+    stv: number[], 
+    fptp: number[], 
+    schulze: number[]
+}
+
+interface FormattedResults {
+    stv: {
+        candidate: number,
+        wins: number
+    }[],
+    fptp: {
+        candidate: number,
+        wins: number
+    }[],
+    schulze:{
+        candidate: number,
+        wins: number
+    }[]
+}
+
+interface Candidate {
+    candidate: number,
+    wins: number
+}
 
 
 const ballots = 500
@@ -26,31 +56,20 @@ const ideologies: Ideology[] = [{
 
[…]

### 2017-04-19 paper/paper.tex
Fixed a reference error
Got everything working on new distro

@@
 The full ballot generation program can be found in the \Code{/generator/} folder.
-The goal of the program is to produce ballots that rank every candidate in order of preference (see figure \ref{fig:stv ballot} on page \pageref{fig:stv ballot}).
+The goal of the program is to produce ballots that rank every candidate in order of preference (see figure~\ref{fig:stv ballot} on page~\pageref{fig:stv ballot}).
 The program represents each voter in a population as belonging to a certain ideology.
@@
 The scenario is built around electing one candidate out of eight.
-The spread of votes within ideologies is flat and all ideologies are "weak".
+The spread of votes within ideologies is flat and all ideologies are ``weak''.
 This means that the general spread of votes will be even.
-An example of the distribution of first-preference votes generated in this scenario can be seen in figure \ref{fig:example of scenario 1}.
-The full configuration object can be seen in code example \ref{lst:scenario 1}.
+An example of the distribution of first-preference votes generated in this scenario can be seen in figure~\ref{fig:example of scenario 1}.
+The full configuration object can be seen in code example~\ref{lst:scenario 1}.
 \codeblock{code/generator/scenario1.ts}{lst:scenario 1}{Configuration object for scenario 1}
@@
 It features a normal spread of votes between candidates.
-An example distribution of first-preference votes generated in this scenario can be seen in figure \ref{fig:example of scenario 2}.
-The full configuration can be seen in code example \ref{lst:scenario 2}.
+An example distribution of first-preference votes generated in this scenario can be seen in figure~\ref{fig:example of scenario 2}.
+The full configuration can be seen in code example~\ref{lst:scenario 2}.
 \codeblock{code/generator/scenario2.ts}{lst:scenario 2}{Scenario 2}
@@
 It features a steep spread of votes between candidates.
-An example distribution of first-preference votes generated in this scenario can be seen in figure \ref{fig:example of scenario 3}.
-The full configuration can be seen in code example \ref{lst:scenario 3}.
+An example distribution of first-preference votes generated in this scenario can be seen in figure~\ref{fig:example of scenario 3}.
+The full configuration can be seen in code example~\ref{lst:scenario 3}.
 \codeblock{code/generator/scenario3.ts}{lst:scenario 3}{Scenario 3}
@@
 \subsubsection{Implementation}
-The first-past-the-post program is implemented in a single file. The inputs of the program can be seen in code example \ref{lst:fptp inputs}.
+The first-past-the-post program is implemented in a single file. The inputs of the program can be seen in code example~\ref{lst:fptp inputs}.
 \codeblock{code/fptp/inputs.ts}{lst:fptp inputs}{Inputs for FPTP program}
@@
 Then the algorithm loops over the ballots and gets the sum of votes for each candidate.
-This process is shown in code example \ref{lst:fptp processing}.
+This process is shown in code example~\ref{lst:fptp processing}.
 \codeblock{code/fptp/processing.ts}{lst:fptp processing}{Processing and formatting of data}
-The results array is sorted and sliced to only include the $N$ candidates with most votes as seen in code example \ref{lst:fptp result calculation}.
+The results array is sorted and sliced to only include the $N$ candidates with most votes as seen in code example~\ref{lst:fptp result calculation}.
 \codeblock{code/fptp/result.ts}{lst:fptp result calculation}{Finding and returning winning candidates}
@@
 For the sake of simplicity, in this implementation, all candidates must be ranked at unique and linear values.
-An example of a ballot can be seen in figure \ref{fig:stv ballot}.	This means that there is more data available for determining the result of the election which the method can take advantage of.
+An example of a ballot can be seen in figure~\ref{fig:stv ballot}.	This means that there is more data available for determining the result of the election which the method can take advantage of.
 Votes are, if needed, transferred between choices within a ballot, hence the name Single Transferable Vote.
@@
 Every candidate is a top-level node with an attribute showing the number of current votes for the candidate.
-Each node has child nodes representing the next preferences of the voters for that particular candidate, see figure \ref{fig:tree structure}.
+Each node has child nodes representing the next preferences of the voters for that particular candidate, see figure~\ref{fig:tree structure}.
 It is easy to manipulate branches via recursion.
@@
 In order to eliminate and transfer surplus votes from any candidate node $A$, the children of $A$ are passed into the distribute function.
-In the case of transferring surplus votes, the votes for each child node is first multiplied by $\frac{\text{surplus votes}}{\text{total votes}}$ as outlined in the pseudocode in section \ref{alg:stv psuedocode}.
+In the case of transferring surplus votes, the votes for each child node is first multiplied by $\frac{\text{surplus votes}}{\text{total votes}}$ as outlined in the pseudocode in section~\ref{alg:stv psuedocode}.
 The full source code for functions that manipulate the tree structure can be found in \Code{/stv/tree.ts}.
@@
 The Schulze Method is a method used mainly to determine results in a single-winner election but can also be used to provide rankings and elect multiple candidates in a single election \autocite{Schulze2011}.
-Ballots are identical to those of the single transferable vote, see figure \ref{fig:stv ballot} on page \pageref{fig:stv ballot}.
+Ballots are identical to those of the single transferable vote, see figure \ref{fig:stv ballot} on page~\pageref{fig:stv ballot}.
 The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate wins.
@@
 There are multiple ways of resolving the tie, one of them being the Schulze Method.
-\ref{}
 
@@
 \codeblock{code/schulze/maps.ts}{lst:schulze maps}{Data representation}
-The program then runs the algorithm outlined in the pseudocode in section \ref{alg:schulze psuedocode}.
+The program then runs the algorithm outlined in the pseudocode in section~\ref{alg:schulze psuedocode}.
 \codeblock{code/schulze/algorithm.ts}{lst:schulze algorithm}{Main algorithm}
@@
 This means that there is not an obvious winner present.
-This can be seen from the first-preference votes in the scenario seen in figure \ref{fig:example of scenario 1}.
-The full result in this scenario can be seen in figure \ref{fig:scenario 1 results}.
+This can be seen from the first-preference votes in the scenario seen in figure~\ref{fig:example of scenario 1}.
+The full result in this scenario can be seen in figure~\ref{fig:scenario 1 results}.
 The outlier in this scenario seems to be the fptp method, electing candidate 0 more often than both other methods.
-Key metrics for the results in this scenario can be found in table \ref{tab:scenario 1 result}.
+Key metrics for the results in this scenario can be found in table~\ref{tab:scenario 1 result}.
 Although the misrepresentation metric is not entirely accurate, especially when few seats are elected, it shows that fptp is not entirely representative.
@@
 Scenario 2 featured 9 candidates of which 3 were to be elected.
-The distribution of votes was "normal", and as seen in figure \ref{fig:example of scenario 2}, the election is very close with many candidates having a similar percentage of first-preference votes.
+The distribution of votes was ``normal'', and as seen in figure~\ref{fig:example of scenario 2}, the election is very close with many candidates having a similar percentage of first-preference votes.
 The results obtained in scenario 2 are very interesting.
@@
 The STV result showed less misrepresentation than the FPTP result, which was to be expected since the method has access to more data of any voter's preferences.
-The results in scenario 2 can be observed in figure \ref{fig:scenario 2 result} and the key metrics can be seen in table \ref{tab:scenario 2 result}.
+The results in scenario 2 can be observed in figure~\ref{fig:scenario 2 result} and the key metrics can be seen in table~\ref{tab:scenario 2 result}.
 \begin{figure}
@@
 The distribution of votes was steep.
-This can be seen by the first-preference votes in figure \ref{fig:example of scenario 3}.
+This can be seen by the first-preference votes in figure~\ref{fig:example of scenario 3}.
 The results obtained with each method in this scenario are practically identical.
 From this, it can be inferred that the results of the methods converge as the preferences in a population become more clear.
-The results obtained in this scenario can be seen in figure \ref{fig:scenario 3 result}.
-The key metrics can be found in table \ref{tab:scenario 3 result}.
+The results obtained in this scenario can be seen in figure~\ref{fig:scenario 3 result}.
+The key metrics can be found in table~\ref{tab:scenario 3 result}.
 \begin{figure}[H]
@@
 Generally, if you want proportional representation (which in a democracy you want), STV will likely be the best method to use out of the methods covered in this paper.
-Modeling of data needs more work, as well as including other methods (such as ...). More research is needed.
+Modeling of data needs more work, as well as including other methods (such as \ldots). More research is needed.
 
@@
 
+Hellosssssssss
+
 \pagebreak
 
-\printbibliography
+\printbibliography{}
 

### 2017-04-19 paper/paper.tex
Fixed typos

@@
 Most importantly Typescript has optional static type checking.
-Sample code in typescript can be seen in code example \ref{lst:typescript example}.
+Sample code in typescript can be seen in code example~\ref{lst:typescript example}.
 \codeblock{code/typescriptexample.ts}{lst:typescript example}{Basic Typescript syntax}
@@
       x tick style = transparent,
-			ylabel = {First prefrence votes},
+			ylabel = {First preference votes},
 			xlabel = {Candidate},
@@
 
-The main process of the program is found in the \Code{stv/election.ts} file and runs the process defined in the pseudocode in section \ref{alg:stv psuedocode} on page \pageref{alg:stv psuedocode}.
+The main process of the program is found in the \Code{stv/election.ts} file and runs the process defined in the pseudocode in section~\ref{alg:stv psuedocode} on page~\pageref{alg:stv psuedocode}.
 
@@
 The Schulze Method is a method used mainly to determine results in a single-winner election but can also be used to provide rankings and elect multiple candidates in a single election \autocite{Schulze2011}.
-Ballots are identical to those of the single transferable vote, see figure \ref{fig:stv ballot} on page~\pageref{fig:stv ballot}.
+Ballots are identical to those of the single transferable vote, see figure~\ref{fig:stv ballot} on page~\pageref{fig:stv ballot}.
 The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate wins.
-As mentioned, this method relies on comparing the preferences of every candidate to one another as shown in table \ref{tab:pairwise comparison matrix}.
+As mentioned, this method relies on comparing the preferences of every candidate to one another as shown in table~\ref{tab:pairwise comparison matrix}.
 If there is a Condorcet winner the process is simple: declare the Condorcet winner a winner and run another iteration without that candidate.
@@
 An efficient and relatively simple way to compute this problem is via the Floyd-Warshall algorithm which is used in the implementation.
-See \ref{lst:schulze algorithm} for the full algorithm.
+See~\ref{lst:schulze algorithm} for the full algorithm.
 
@@
 
-Hellosssssssss
+Hello
 

### 2017-04-19 fptp/index.ts

@@ -6,19 +6,19 @@ interface Result {
 // Calculates the winners in a First-past-the-post election
 export default function calculateWinners(input: number[][], seats: number) {
 
-    // Maps input to first prefrences
-    let firstPrefrences = input.map(el => {
+    // Maps input to first preferences
+    let firstPreferences = input.map(el => {
         return el[0]
     })
 
     let results: Result[] = []
-    // Loops over prefrences and adds/increments result
-    for (let i = 0; i < firstPrefrences.length; i++) {
+    // Loops over preferences and adds/increments result
+    for (let i = 0; i < firstPreferences.length; i++) {
         // Finds index in results array of candidate at i
-        let index = results.findIndex(obj => obj.cand === firstPrefrences[i])
+        let index = results.findIndex(obj => obj.cand === firstPreferences[i])
         // If candidate is not added to results
         if (index === -1) {
-            results.push({ cand: firstPrefrences[i], votes: 1 })
+            results.push({ cand: firstPreferences[i], votes: 1 })
         } else {
             // Increment count if already added in results
             results[index].votes += 1

### 2017-04-19 generator/ballots.ts

@@ -3,7 +3,7 @@ import { Ideology, IdeologyWithProbabilities } from './interfaces'
 
 // Generates the ballots, essentially the output of the program
 function generateBallots(numberOfBallots: number, prob: number[], candidates: number[]): number[][] {
-    // Create temp array combining probability and possib
+    // Create temp array combining probability and candidate number
     let temp: number[][] = []
     for (let i = 0; i < candidates.length; i++) {
         temp.push([prob[i], candidates[i]])

### 2017-04-19 generator/candidates.ts

@@ -27,7 +27,7 @@ export function createCandidates(numberOfCandidates: number, ideologies: Ideolog
                 if ((size === 0 ? 1 : size) > ideology.numberOfCandidates) {
                     ideology.numberOfCandidates++
                     numberOfCandidates--
-                    // Pushes thae new party to the array
+                    // Pushes the new party to the array
                     candidates.push({ ideology: ideologyIndex, size: undefined })
                 }
             }
@@ -123,7 +123,7 @@ function normalize(array: (number | undefined)[]): number[] {
 
 // Calculates the distribution of votes as a negative exponential distribution
 function calculateDistribution (candidates: number, k:number): number[] {
-    // Adjusts the constant to lety more and set 0.5 as the default
+    // Adjusts the constant to change more and set 0.5 as the default
     const adjustedK = (k**2)*0.5
     // Defines the range of the distribution where y > 0.01
     const xLimit = fy(0.01, adjustedK)
@@ -140,7 +140,7 @@ function calculateXValues(candidates: number, k: number, stepSize: number, x: nu
         return result
     } else {
         result.push(fx(x, k))
-        // Recusive call with decremented number of parties and incremented x value
+        // Recursive call with decremented number of parties and incremented x value
         return calculateXValues(candidates-1, k, stepSize, x+stepSize, result)
     }
 }

### 2017-04-19 generator/index.ts

@@ -14,8 +14,8 @@ export function generateBallots(ideologies: IdeologyWithProbabilities[], numberO
     return result
 }
 
-export function createIdeologyProbabilities(ideologies: Ideology[], numberOfcandidates: number): IdeologyWithProbabilities[] {
-    const candidates = createCandidates(numberOfcandidates, ideologies)
+export function createIdeologyProbabilities(ideologies: Ideology[], numberOfCandidates: number): IdeologyWithProbabilities[] {
+    const candidates = createCandidates(numberOfCandidates, ideologies)
 
     return assignProbabilityToIdeology(ideologies, candidates)
 }

### 2017-04-19 schulze/index.ts

@@ -11,7 +11,7 @@ export default function calculateResult(input: number[][], seats: number): numbe
     // Gets the pairs of candidates and their count
     // Ex 120 votes prefer a > b
 
-    // d[i][j] gives the number of ballots prefering candidate i > j
+    // d[i][j] gives the number of ballots preferring candidate i > j
     let d: PairMap = getPairs(input)
     // o[i][j] stores the strongest path between candidate i and j
     let p: PairMap = {}
@@ -28,7 +28,7 @@ export default function calculateResult(input: number[][], seats: number): numbe
         }
     }
 
-    // Computing strongest path strength. letiant of the Floyd-Warshall algorithm
+    // Computing strongest path strength. variant of the Floyd-Warshall algorithm
     for (let i = 0; i < c; i++) {
         for (let j = 0; j < c; j++) {
             if (i !== j) {
@@ -59,14 +59,14 @@ export default function calculateResult(input: number[][], seats: number): numbe
     return result
 }
 
-// Gets the pairwise comparison between all candidates and the number of prefrences. Ex. 120 ballots prefer a > b
+// Gets the pairwise comparison between all candidates and the number of preferences. Ex. 120 ballots prefer a > b
 function getPairs(ballots: number[][]): PairMap {
     let p = {}
 
-    // Loops throug all ballots
+    // Loops through all ballots
     for (let k = 0; k < ballots.length; k++) {
         let ballot = ballots[k]
-        // Temp array that stores which candidates are prefered over current candidate in the loop
+        // Temp array that stores which candidates are preferred over current candidate in the loop
         let preferred: number[] = []
         //Loops through each ballot
         for (let i = 0; i < ballot.length; i++) {

### 2017-04-19 stv/candidate.ts

@@ -31,7 +31,7 @@ export default class CandidateNode {
     
     }
 
-    // Multiplies votes for the candidate and its children. Returns a new node. Used when transfering votes.
+    // Multiplies votes for the candidate and its children. Returns a new node. Used when transferring votes.
     multiply(factor: number): CandidateNode {
         // New node to return
         let newNode = new CandidateNode(this.cand, this.count * factor)

### 2017-04-19 stv/election.ts

@@ -50,7 +50,7 @@ export default function runElection(input: number[][], seats: number): Result {
         }
         if (hadSurplus.length > 0) {
             // If someone had surplus, loop back to beginning
-            log.push(`Transfered surplus from ${hadSurplus.filter((item, index, array) => array.indexOf(item) === index).join(', ')}`)
+            log.push(`Transferred surplus from ${hadSurplus.filter((item, index, array) => array.indexOf(item) === index).join(', ')}`)
             continue
         }
 

### 2017-04-20 paper/code/fptp/processing.ts
More typos

@@ -1,5 +1,5 @@
 let results: Result[] = []
-// Loops over prefrences and adds/increments result
+// Loops over preferences and adds/increments result
 for (var i = 0; i < firstPrefrences.length; i++) {
     // Finds index in results array of candidate at i
     let index = results.findIndex(obj => obj.cand === firstPrefrences[i])

### 2017-04-20 paper/code/generator/ideologyConfig.ts

@@ -5,7 +5,7 @@ const ideologyConfig: Ideology[] = [{
     // Large -> steep spread, Small -> flat spread
     candidatePower: 0.2,
     // How inclined voters of this ideology are to vote for a candidate of this ideology
-    // Higer -> more inclined
+    // Higher -> more inclined
     ideologyPower: 1.2
 }, {
 //  ...

### 2017-04-20 paper/code/schulze/maps.ts

@@ -1,4 +1,4 @@
-// d[i][j] gives the number of ballots prefering i > j
+// d[i][j] gives the number of ballots preferring i > j
 let d: PairMap = getPairs(input)
 // o[i][j] stores the strongest path between i and j
 let p: PairMap = {}

### 2017-04-21 schulze/index.ts
More typos

@@ -75,7 +75,7 @@ function getPairs(ballots: number[][]): PairMap {
             for (let j = 0; j < preferred.length; j++) {
                 // Current preferred vote
                 let preferredVote = preferred[j]
-                // Gets the index of where preferredvote > vote are stored
+                // Gets the index of where preferred vote > vote are stored
                 p[preferredVote] = p[preferredVote] || {}
 
                 p[preferredVote][vote] = p[preferredVote][vote] + 1 || 1

### 2017-04-21 stv/tree.ts

@@ -42,17 +42,17 @@ function hasCandidateNode(level: CandidateNode[], cand: number): boolean {
 export function eliminate(lowestRanked: number, tree: CandidateNode[], winners: number[]): CandidateNode[] {
     // New tree
     let newTree = [...tree]
-    // Save the children for transfering
+    // Save the children for transferring
     let children = newTree[lowestRanked].children
     // Remove node from array
     newTree = [ ...newTree.slice(0, lowestRanked), ...newTree.slice(lowestRanked +1) ]
-    // Distribute the children onto the tree i.e transfering
+    // Distribute the children onto the tree i.e transferring
     return distribute(children, newTree, winners)
 }
 
 // Checks if any candidate has surplus votes
 export function isSurplus(tree: CandidateNode[], quota: number): boolean {
-    // Maps array and compares count to quota and then reduces to find if any comparison retured true.
+    // Maps array and compares count to quota and then reduces to find if any comparison returned true.
     let surplus = tree.map(cand => (cand.count > quota)).reduce((a,b) => a || b)
     return surplus
 }
@@ -67,10 +67,10 @@ export function transferSurplus(candNumber: number, tree: CandidateNode[], quota
     const surplusFrac = surplusVotes / totalVotes
     const nonSurplusFrac = 1 - surplusFrac
 
-    // Multiplies values in surplus branch to decrese to be equal to quota
+    // Multiplies values in surplus branch to decrease to be equal to quota
     tree[candIndex] = tree[candIndex].multiply(nonSurplusFrac)
     
-    // Maps over all the children, multiplies their brances by the surplus fraction and returns.
+    // Maps over all the children, multiplies their branches by the surplus fraction and returns.
     let transferChildren = tree[candIndex].children.map(child => {
         child = child.multiply(surplusFrac)
         return child

### 2017-05-10 paper/paper.tex
More typos
Added description of metrics

@@
 \subsubsection{Scenario 1}
+\label{sec:method-scenario1}
 The scenario is built around electing one candidate out of eight.
@@
 \subsubsection{Scenario 2}
+\label{sec:method-scenario2}
 The second scenario elects 3 candidates out of 9 total.
@@
 \subsubsection{Scenario 3}
+\label{sec:method-scenario3}
 The second scenario elects 3 candidates out of 9 total.
@@
 \end{figure}
+\section{Metrics for evaluating results}
+Three metrics will be used for comparing the results obtained in the different scenarios.
+The results obtained with each voting method will be compared against the other methods.
+Comparisons to the configuration files outlined in Sections~\ref{sec:method-scenario1} -~\ref{sec:method-scenario3}.
+\subsection{Standard deviation}
+The standard deviation of the outcomes represents the variance in outcome due to the pseudorandom nature of the generator program.
+The standard deviation is calculated according to equation~\ref{eq:standard-deviation}.
+\begin{equation}
+	\label{eq:standard-deviation}
+	\sigma ={\sqrt {{\frac {1}{N}}\sum _{i=1}^{N}(x_{i}-\mu )^{2}}},{\rm {\ \ where\ \ }}\mu ={\frac {1}{N}}\sum _{i=1}^{N}x_{i}.
+\end{equation}
+\subsection{Misrepresentation}
+The misrepresentation metric gives an idea of how \textit{proportional} the outcomes of a certain voting method in any scenario is.
+The level of proportionality of a result is a measure of how closely the preferences of a population are matched with the result.
+Higher proportionality means that the outcome more closely resembles the preferences of the voters.
+The method of calculating the misrepresentation used in this paper is defined as follows:
+\begin{enumerate}
+	\item Calculate what theoretical election outcome would be the most proportionate based on the configuration file used to generate the ballots.\label{enum:theoretical}
+	\item Compare the actual outcomes of a certain method with the theoretical result obtained in Step \ref{enum:theoretical}.
+	\begin{enumerate}
+		\item Calculate the difference between the measured and theoretical percentage for each ideology.
+		\item Sum all the differences.
+	\end{enumerate}
+\end{enumerate}
+\subsection{Most likely winners}
+Shows what candidates, given a certain scenario, are most likely to win in a particular method.
 \pagebreak
@@
 \codeblock{code/fptp/inputs.ts}{lst:fptp inputs}{Inputs for FPTP program}
-The ballot data is first mapped to only include first preferences.
-Then the algorithm loops over the ballots and gets the sum of votes for each candidate.
-This process is shown in code example~\ref{lst:fptp processing}.
-\codeblock{code/fptp/processing.ts}{lst:fptp processing}{Processing and formatting of data}
-The results array is sorted and sliced to only include the $N$ candidates with most votes as seen in code example~\ref{lst:fptp result calculation}.
-\codeblock{code/fptp/result.ts}{lst:fptp result calculation}{Finding and returning winning candidates}
+The program sums all the first-preference votes for each candidate and elects the ones with most votes, in accordance with specified amount of seats.
 \subsection{Single transferable vote}
@@
 In order to eliminate and transfer surplus votes from any candidate node $A$, the children of $A$ are passed into the distribute function.
-In the case of transferring surplus votes, the votes for each child node is first multiplied by $\frac{\text{surplus votes}}{\text{total votes}}$ as outlined in the pseudocode in section~\ref{alg:stv psuedocode}.
+In the case of transferring surplus votes, the votes for each child node is first multiplied by $\frac{\text{surplus votes}}{\text{total votes}}$ as outlined in the pseudocode in Section~\ref{alg:stv psuedocode}.
 The full source code for functions that manipulate the tree structure can be found in \Code{/stv/tree.ts}.
-
-The main process of the program is found in the \Code{stv/election.ts} file and runs the process defined in the pseudocode in section~\ref{alg:stv psuedocode} on page~\pageref{alg:stv psuedocode}.
-
+The main process of the program is found in the \Code{stv/election.ts} file and runs the process defined in the pseudocode in Section~\ref{alg:stv psuedocode} on page~\pageref{alg:stv psuedocode}.
 \subsection{Schulze}
@@
 \codeblock{code/schulze/maps.ts}{lst:schulze maps}{Data representation}
-The program then runs the algorithm outlined in the pseudocode in section~\ref{alg:schulze psuedocode}.
+The program then runs the algorithm outlined in the pseudocode in Section~\ref{alg:schulze psuedocode}.
 \codeblock{code/schulze/algorithm.ts}{lst:schulze algorithm}{Main algorithm}
@@
 Method & Standard deviation & Misrepresentation & Most likely winners \\ \midrule
-FPTP & 223 & 67\% & 2 \\
-STV & 315 & 7\% & 2 \\
-Schulze & 313 & 9\% & 2 \\ \bottomrule
+FPTP & 223 & 66 & 2 \\
+STV & 315 & 8 & 2 \\
+Schulze & 313 & 9 & 2 \\ \bottomrule
 \end{tabular}
@@
 Method & Standard deviation & Misrepresentation & Most likely winners \\ \midrule
-FPTP & 418 & 42\% & 0, 2 \& 5 \\
-STV & 388 & 14\% & 1, 2 \& 5 \\
-Schulze & 393 & 67\% & 2, 5 \& 7  \\ \bottomrule
+FPTP & 418 & 50 & 0, 2 \& 5 \\
+STV & 388 & 47 & 1, 2 \& 5 \\
+Schulze & 393 & 100 & 2, 5 \& 7  \\ \bottomrule
 \end{tabular}
@@
 		Method & Standard deviation & Misrepresentation & Most likely winners \\ \midrule
-		FPTP & 470 & 33\% & 0, 1 \& 2 \\
-		STV & 471 & 33\% & 0, 1 \& 2 \\
-		Schulze & 471 & 33\% & 0, 1 \& 2  \\ \bottomrule
+		FPTP & 470 & 0 & 0, 1 \& 2 \\
+		STV & 471 & 0 & 0, 1 \& 2 \\
+		Schulze & 471 & 0 & 0, 1 \& 2  \\ \bottomrule
 	\end{tabular}
@@
 
-Hello
+Hello world
 

### 2017-05-11 paper/paper.tex
Wrote basic theory

@@
 \section{Theory}
-Theory will be here some day
+One would think that by testing all different voting systems and by setting up good criteria for how to evaluate them, it would be possible to come to a definitive conclusion of what system should be used.
+However, this is not the case.
+By setting up different mathematical criteria for how a voting system shall behave, it is impossible to satisfy all criteria simultaneously.
+This is what several theorems, most notably Arrow's Impossibility theorem outlined in 1950, show \autocite{arrow1950difficulty}.
+This means that any decision regarding choice of electoral system is a balance of their strengths and weaknesses.
+Simply put: there is no perfect voting system and never will be.
+This does however not mean that all voting systems are equally efficient, elegant or accurate.
+
+There are several ways of evaluating voting methods that are used.
+One is the mathematical approach of evaluating what criteria are important to meet and finding elegant methods that satisfy them.
+Another is by testing and finding probabilities that some criteria are broken — A method that fails to meet a certain criteria only in very few cases is perhaps not that big of a problem.
+A third way of evaluating methods is not by mathematical criteria, but other metrics such as voter satisfaction or how likely someone is to vote tactically.
+\subsection{Definitions}
+\begin{itemize}
+	\item A \textit{candidate} is someone a voter can vote to elect. Can also be considered as being parties that a voter can vote for.
+	\item An \textit{election} is an event in which voters cast ballots to vote on candidates
+	\item A \textit{seat} is something a candidate can be elected to. A candidate may for example be elected to hold a seat of parliament.
+	\item An \textit{ideology} is a group that both candidates and voters can identify with. They split the whole voting population into several blocks.
+\end{itemize}  
 \pagebreak
@@
 \end{figure}
-\section{Metrics for evaluating results}
+\subsection{Metrics for evaluating results}
 Three metrics will be used for comparing the results obtained in the different scenarios.
@@
 Comparisons to the configuration files outlined in Sections~\ref{sec:method-scenario1} -~\ref{sec:method-scenario3}.
-\subsection{Standard deviation}
+\subsubsection{Standard deviation}
 The standard deviation of the outcomes represents the variance in outcome due to the pseudorandom nature of the generator program.
@@
 \end{equation}
-\subsection{Misrepresentation}
+\subsubsection{Misrepresentation}
 The misrepresentation metric gives an idea of how \textit{proportional} the outcomes of a certain voting method in any scenario is.
@@
 \end{enumerate}
-\subsection{Most likely winners}
+\subsubsection{Most likely winners}
 Shows what candidates, given a certain scenario, are most likely to win in a particular method.

### 2017-05-12 paper/paper.tex
Finalizing before opposition

@@
 \begin{abstract}
-	The abstract text goes here.
 \end{abstract}
@@
 They are used to show common preferences within a population, for example what politician a population wants to see elected.
-Several types of systems have been designed and there are a myriad of variations of those systems.
+Several types of systems have been designed for this purpose and there are a myriad of variations of those systems.
 They range from simple methods such as “most votes win” to complex processes that can only be practically carried out by a computer.
@@
 By setting up different mathematical criteria for how a voting system shall behave, it is impossible to satisfy all criteria simultaneously.
-This is what several theorems, most notably Arrow's Impossibility theorem outlined in 1950, show \autocite{arrow1950difficulty}.
+This is what several theorems, most notably \textit{Arrow's Impossibility Theorem} show \autocite{arrow1950difficulty}.
 This means that any decision regarding choice of electoral system is a balance of their strengths and weaknesses.
@@
 There are several ways of evaluating voting methods that are used.
-One is the mathematical approach of evaluating what criteria are important to meet and finding elegant methods that satisfy them.
+One is the mathematical approach of evaluating what criteria are important to meet and finding methods that satisfy them.
 Another is by testing and finding probabilities that some criteria are broken — A method that fails to meet a certain criteria only in very few cases is perhaps not that big of a problem.
@@
 \section{Methodology}
-All voting methods have been implemented in Typescript – mostly due to the author having previous experience with JavaScript.
+All voting algorithms have been implemented in Typescript – mostly due to the author having previous experience with JavaScript.
 Typescript is a superset of JavaScript with multiple extra features.
 Most importantly Typescript has optional static type checking.
-Sample code in typescript can be seen in code example~\ref{lst:typescript example}.
+Sample code written in Typescript can be seen in code example~\ref{lst:typescript example}.
 \codeblock{code/typescriptexample.ts}{lst:typescript example}{Basic Typescript syntax}
 \subsection{Modeling test data}
+\label{sec:vote-generation}
 In order to test the methods and their implementations, test data is needed.
-There are cases where extensive election data is published, such as in Maltese elections, but full ballot data, which is needed for the implementations has not been found.
-Instead, the implementations will be tested with data generated from a simple computer algorithm.
-The algorithm used in this paper is highly primitive, as modeling preferences within a population is far beyond this paper.
-The full ballot generation program can be found in the \Code{/generator/} folder.
+There are cases where extensive election data is published, such as in Maltese elections, but full ballot data, which is needed as input for the implementations used in this paper has not been found.
+Instead, the algorithms will be tested with data generated from a simple computer program.
+The algorithm used for this purpose in this paper is highly primitive, as modeling preferences within a population is far beyond the scope of this paper.
+The full ballot generation program can be found in the \Code{/generator} folder.
 The goal of the program is to produce ballots that rank every candidate in order of preference (see figure~\ref{fig:stv ballot} on page~\pageref{fig:stv ballot}).
-The program represents each voter in a population as belonging to a certain ideology.
+The program incorporates the idea of an \textit{ideology} where each candidate is assigned one.
 Each ideology has has a list of weighted preferences indicating how a voter for this ideology is likely to vote.
@@
 	\item Based on the base size of each candidate, a probability-list of voting for each candidate is created for every ideology.
-An ideology's probability-list represents how a voter aligned the ideology is expected to vote.
+An ideology's probability-list represents how a voter aligned the ideology is likely to vote.
 	\item It creates a certain number of individual ballots.
-Each ballot is given an ideology and creates its own list preferences based via weighted random number generation according to the probability-list of the assigned ideology.
+Each ballot is given an ideology and creates its own list preferences via weighted random number generation according to the probability-list of its assigned ideology.
 \end{enumerate}
-The output of the program is a set of ballots, where each ballot is an ordered set of preferences.
+The output of the program is a set of ballots, where each ballot is an ordered set of preferences between candidates.
 The implementation is highly arbitrary and all constants in the program even more so.
 However, expanding on the generator program would be beyond the scope of this project.
-The program works in that it is possible to control variables to test for different election scenarios.
+The vote generation algorithm is an attempt to provide more realistic voting data than what is achieved by a purely random allocation of votes.
+The program also allows for the possibility to control the data by changing the input variables.
+This makes it possible to test different election scenarios.
 \subsection{Constructing test scenarios}
@@
 Instead, 3 arbitrary test scenarios will be used.
-The election will be simulated 1000 times for each scenario and the election data will then run through the different voting methods and the results will be compared.
+An election will be simulated 1000 times for each scenario and the election data will then run through the different voting algorithms and the results will be compared.
 The simulation scenarios are arbitrary but should allow for comparison of the different voting methods.
@@
 The scenario is built around electing one candidate out of eight.
-The spread of votes within ideologies is flat and all ideologies are ``weak''.
-This means that the general spread of votes will be even.
+The spread of votes within ideologies is flat and all ideologies are so called ``weak''.
+This means that the general spread of votes between candidates will be even.
 An example of the distribution of first-preference votes generated in this scenario can be seen in figure~\ref{fig:example of scenario 1}.
@@
 	\end{tikzpicture}
-	\caption{Example distribution of first-preference votes in scenario 1}
+	\caption{Example distribution of first-preference votes in scenario 1. Avreages of 10 simulations.}
 \label{fig:example of scenario 1}
@@
 	\end{tikzpicture}
-	\caption{Example distribution of first-preference votes in scenario 2}
+	\caption{Example distribution of first-preference votes in scenario 2. Avreages of 10 simulations.}
 \label{fig:example of scenario 2}
@@
 	\end{tikzpicture}
-	\caption{Example distribution of first-preference votes in scenario 3}
+	\caption{Example distribution of first-preference votes in scenario 3. Avreages of 10 simulations.}
 \label{fig:example of scenario 3}
@@
 The results obtained with each voting method will be compared against the other methods.
-Comparisons to the configuration files outlined in Sections~\ref{sec:method-scenario1} -~\ref{sec:method-scenario3}.
+Comparisons to the configuration files outlined in Sections~\ref{sec:method-scenario1} -~\ref{sec:method-scenario3} will also be made.
 \subsubsection{Standard deviation}
-The standard deviation of the outcomes represents the variance in outcome due to the pseudorandom nature of the generator program.
+The standard deviation of the outcomes represents the variance in outcome due to the pseudorandom nature of the generator program outlined in Section~\ref{sec:vote-generation}.
 The standard deviation is calculated according to equation~\ref{eq:standard-deviation}.
@@
 	\item Calculate what theoretical election outcome would be the most proportionate based on the configuration file used to generate the ballots.\label{enum:theoretical}
-	\item Compare the actual outcomes of a certain method with the theoretical result obtained in Step \ref{enum:theoretical}.
+	\item Compare the actual outcomes of a certain method with the theoretical result obtained in Step~\ref{enum:theoretical}.
 	\begin{enumerate}
@@
 The first-past-the-post voting method is a method designed for electing one or several candidates out of a set of candidates.
-Each voter has one (1) vote which may be allocated to any candidate.
-In a first-past-the-post election the N candidates with most votes get elected.
+Each voter has one (1) vote that may be allocated to any candidate.
+In a FPTP election the N candidates with most votes get elected.
 \subsubsection{Justification}
@@
 \subsubsection{Implementation}
-The first-past-the-post program is implemented in a single file. The inputs of the program can be seen in code example~\ref{lst:fptp inputs}.
+The first-past-the-post program is implemented in a single file (\Code{/fptp/index.ts}). The inputs of the program can be seen in code example~\ref{lst:fptp inputs}.
 \codeblock{code/fptp/inputs.ts}{lst:fptp inputs}{Inputs for FPTP program}
@@
 \subsubsection{Description}
-The Single Transferable Vote method is a more complicated algorithm than the first-past-the-post method.
-Voters are given ballots where they are supposed to rank candidates in order.
-The specific rules for if you need to rank all candidates or rank several candidates at the same value not can vary.
-For the sake of simplicity, in this implementation, all candidates must be ranked at unique and linear values.
-An example of a ballot can be seen in figure~\ref{fig:stv ballot}.	This means that there is more data available for determining the result of the election which the method can take advantage of.
-Votes are, if needed, transferred between choices within a ballot, hence the name Single Transferable Vote.
-The method relies on the concept of a quota, the number of votes you need to be elected.
-The Droop-Quota, defined as $(\frac{\text{total valid poll}}{\text{seats} + 1})+1$, is often used.
-If a candidate receives equal or more votes than the quota, he/she is elected.
-If the number of votes exceed the quota, a fraction of the votes are transferred to the next choice on the ballots that voted for the elected candidate.
-This process is repeated until there are no candidates with more votes than the quota.
-If there still are seats yet to be filled, the candidate with fewest votes is eliminated and his/her votes are transferred to the next choice on those ballots.
-This process is repeated until all seats are filled.
-The process can become quite complex with many ballots and transferring fractional votes.
-A computer is therefore essential in order to resolve large scale elections.
+The Single Transferable Vote (STV) is a more complicated voting system than the first-past-the-post method.
+STV is a multi-seat election method, although it can be used for single-seat elections too.
+STV becomes equivalent to the Instant-runoff voting method (IRV) in single-seat elections.
+In an STV election, voters are given ballots in which they are supposed to rank candidates in order.
+The specific rules for wether one needs to rank all candidates or just a few not can vary.
+For the sake of simplicity, all candidates must be ranked at unique and linear values in this implementation.
+An example of an STV ballot can be seen in figure~\ref{fig:stv ballot}.
+By having voters convey more information in a ballot, there is more data available that the method can take advantage of.
 \begin{figure}
@@
 \end{figure}
+
+Using this data, votes are transferred between candidates within a ballot in the method, hence the name Single Transferable Vote.
+The method relies on the concept of a quota, which is the number of votes you need to be elected.
+The Droop-Quota, defined as $(\frac{\text{total valid poll}}{\text{seats} + 1})+1$, is often used and is the one implemented in this paper.
+If a candidate receives equal or more votes than the quota, he/she is elected.
+If the number of votes for a candidate exceed the quota, a fraction of his/her votes are transferred to the next choice on the ballots that voted for that particular candidate.
+This process is repeated until there are no candidates with more votes than the quota.
+If there still are seats yet to be filled, the candidate with fewest votes is eliminated and his/her votes are transferred to the next choice on the ballots which supported the candidate.
+This process is repeated until all seats are filled.
+The process can become quite complex with many ballots and transferring of fractional votes.
+A computer is therefore essential to resolve large scale elections.
 \subsubsection{Justification}
@@
 \tab $k \coloneqq$ index of smallest $votes_{i}$ \\
-\tab eliminate $votes_{k}$ and distribute all next-preference votes for candidate $k$ \tab into $votes$\\
+\tab eliminate $votes_{k}$ and distribute all next-preference votes for candidate \\
+\tab $k$ into $votes$\\
 end while
@@
 Each node has child nodes representing the next preferences of the voters for that particular candidate, see figure~\ref{fig:tree structure}.
-It is easy to manipulate branches via recursion.
+It is easy to manipulate branches via recursive functions.
 Merging and multiplying branches is used when transferring votes from one candidate node to another.
@@
 \subsubsection{Description}
-The Schulze Method is a method used mainly to determine results in a single-winner election but can also be used to provide rankings and elect multiple candidates in a single election \autocite{Schulze2011}.
-Ballots are identical to those of the single transferable vote, see figure~\ref{fig:stv ballot} on page~\pageref{fig:stv ballot}.
+The Schulze Method is a method used mainly to determine results in single-winner elections but can also be used to provide rankings and elect multiple candidates in a single election \autocite{Schulze2011}.
+Ballots are identical to those of the single transferable vote (see figure~\ref{fig:stv ballot} on page~\pageref{fig:stv ballot}).
 The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate wins.
@@
 However, there can be Condorcet ties, where there is no Condorcet winner.
-There are multiple ways of resolving the tie, one of them being the Schulze Method.
+There are multiple methods used for resolving Condorcet ties, with one of them being the Schulze Method.
 
@@
 An efficient and relatively simple way to compute this problem is via the Floyd-Warshall algorithm which is used in the implementation.
-See~\ref{lst:schulze algorithm} for the full algorithm.
+See Code Example~\ref{lst:schulze algorithm} for the full algorithm.
 
@@
 let $p[i,j]$ be the strength of the strongest path from candidate $i$ to candidate $j$\\
+let $C$ be the number of candidates
 for $i$ from 1 to $C$\\
@@
 The output of the program is a list of winners.
-The program first creates the matrices for both the preferences and paths between candidates.
-\codeblock{code/schulze/maps.ts}{lst:schulze maps}{Data representation}
+The program first creates the matrices for both the preferences and paths between candidates as seen in Code Example~\ref{lst:schulze-mapsb}.
+\codeblock{code/schulze/maps.ts}{lst:schulze-maps}{Data representation}
 The program then runs the algorithm outlined in the pseudocode in Section~\ref{alg:schulze psuedocode}.
@@
 \subsection{Scenario 1}
+\label{sec:resuls-scenario1}
 Scenario 1 featured 8 candidates where one was to be elected.
@@
 This means that there is not an obvious winner present.
-This can be seen from the first-preference votes in the scenario seen in figure~\ref{fig:example of scenario 1}.
+This can be seen from the first-preference votes in the scenario seen in figure~\ref{fig:example of scenario 1} on Page~\pageref{fig:example of scenario 1}.
 The full result in this scenario can be seen in figure~\ref{fig:scenario 1 results}.
-The outlier in this scenario seems to be the fptp method, electing candidate 0 more often than both other methods.
+The outlier in this scenario seems to be the FPTP method, electing candidate 0 more often than both other methods.
 Key metrics for the results in this scenario can be found in table~\ref{tab:scenario 1 result}.
 Although the misrepresentation metric is not entirely accurate, especially when few seats are elected, it shows that fptp is not entirely representative.
-The STV and Schulze method seem to return very similar results.
-\begin{figure}
+The STV and Schulze method seem to produce very similar results.
+\begin{figure}[H]
 	\centering
@@
 
-\begin{table}
+\begin{table}[H]
 \centering
@@
 \subsection{Scenario 2}
+\label{sec:resuls-scenario2}
 Scenario 2 featured 9 candidates of which 3 were to be elected.
-The distribution of votes was ``normal'', and as seen in figure~\ref{fig:example of scenario 2}, the election is very close with many candidates having a similar percentage of first-preference votes.
+The distribution of votes was ``normal'', and as seen in figure~\ref{fig:example of scenario 2} on page~\ref{fig:example of scenario 2}, the election is very close with many candidates having a similar percentage of first-preference votes.
 The results obtained in scenario 2 are very interesting.
@@
 The Schulze method also tended to underrepresent ideology 2.
-It instead overrepresented ideology 2, electing 3 candidates of ideology 2 in 50\% of elections.
+It instead overrepresented ideology 3, electing 3 candidates of ideology 3 in 50\% of elections.
 This indicates that the Schulze method is not a representative method in a multi-seat election.
@@
 The results in scenario 2 can be observed in figure~\ref{fig:scenario 2 result} and the key metrics can be seen in table~\ref{tab:scenario 2 result}.
-\begin{figure}
+\begin{figure}[H]
 	\centering
@@
 \subsection{Scenario 3}
+\label{sec:resuls-scenario3}
 Scenario 3 featured 9 candidates of which 3 were to be elected.
-The distribution of votes was steep.
-This can be seen by the first-preference votes in figure~\ref{fig:example of scenario 3}.
+The distribution of votes was  ``steep''.
+This can be seen by the first-preference votes in figure~\ref{fig:example of scenario 3} on Page~\pageref{fig:example of scenario 3}.
 The results obtained with each method in this scenario are practically identical.
@@
 The results obtained in the three different scenarios provide some insight into the varying properties of the different voting systems.
-Each of the scenarios showed different behaviors for the different methods.
+Each of the methods showed different behavior in the different scenarios.
 For instance, the methods provided practically the same result in scenario 3 but wildly varying results in scenario 2.
 While the testing method used in this paper may not have been the most robust way of comparing the voting methods, several conclusions can be drawn from the data.
-I outline them in 4 points below.
+They are outlined in 4 points below.
 \begin{enumerate}
-	\item Schulze did not seem like a proportional voting method in multi-seat elections. ...
-	\item In single-seat elections, Schulze and STV (and IRV in extension) seemed to provide similar results. ...
-	\item FPTP did not seem like a very proportional method in close elections. ...
-	\item STV seems to be the most proportional method out of the 3 tested, but is not without its flaws. ...
+	\item Schulze did not seem like a proportional voting method in multi-seat elections.\label{num:conclusion-schulze}
+
+	As seen from the results obtained in scenario 2, which can be seen in Section~\ref{sec:resuls-scenario2}, the Schulze Method heavily overrepresented candidates from ideology 1 (candidates 3, 5 \& 7).
+While ideology 1 in fact was the most popular ideology, a more proportionate way of representing the electorate in the scenario would have been to grant one seat to each ideology.
+The Schulze tended to elect candidates from the strongest ideology only, instead of electing candidates from all ideologies in a more proportionate manner.
+This is not a problem in a single-seat election, as can be seen in the results of scenario 1 in Section~\ref{sec:resuls-scenario1}, which was a single-seat elections, where the Schulze Method simply elected the most popular candidate.
+	\item In single-seat elections, Schulze and STV (and IRV in extension) seemed to provide similar results.
+
+	As seen in the results of scenario 1 outlined in Section~\ref{sec:resuls-scenario1}, both Schulze and STV produced nearly identical results, while the results from FPTP deviated slightly.
+While the methods work very differently, the results in these methods seem to behave similarly in single-seat elections.
+	\item FPTP did not seem like a very proportional method in close elections.
+
+	FPTP preformed considerably worse at being representative than the other methods.
+This was true for both close single- and multi-seat elections, excluding The Schulze Method in scenario 2 (see Point~\ref{num:conclusion-schulze}).
+At the core, both the STV and Schulze Method have more data to use for determining winners than what FPTP does.
+The FPTP method only has access to first-preference votes which does not convey as much information as a ballot listing all candidates in order of preference does.
+	\item STV seems to be the most proportional method out of the 3 tested, but is not without its flaws.
+
+	STV provided the most proportionate results overall of all three methods tested.
+However, as it goes with voting system, it has several flaws.
+It is for example possible to increase the chance of a candidate winning by lowering him/her on a ballot, and vice versa.
+STV is the only multi-seat proportional voting system tested in this paper, and the results obtained reinforce its position as just that.
 \end{enumerate}
-Summary:
-There is no perfect voting system.
-Generally, if you want proportional representation (which in a democracy you want), STV will likely be the best method to use out of the methods covered in this paper.
-Modeling of data needs more work, as well as including other methods (such as \ldots). More research is needed.
+While there is no perfect voting system, they all preform differently.
+From the conclusions outlined above, a decision of what system to use between the three voting systems used in this paper can be taken.
+Generally, if a proportional representation is desired (which in a democracy it usually is), STV will likely be the most appropriate method to use.
+In single-seat elections, the Schulze Method should also be considered.
+FPTP is the simplest method to both use and understand, but cannot be considered a proportionate voting method.
 
-Todo:
-\begin{itemize}
-	\item Write theory
-	\item Add references where needed
-	\item Explain metrics used to evaluate results
-	\item Cut down on explanation of fptp
-	\item Write abstract
-	\item Finish summary
-\end{itemize}
+While the findings of this paper are hardly revolutionary, the nature of the three voting systems used in this paper and their behavior is experimentally evaluated.
+The paper also provides implementations of all voting methods in both TypeScript and JavaScript.
 
-Hello world
-
+The key area for furthering this work would be in data collection or creation.
+A more sophisticated procedure for generating test data could be developed and run with more extensive test scenarios.
+Data from the real world could also be collected in actual elections and run through the different algorithms to test them.
+One could also write software that generates lots of scenarios with different parameters and analyzes how they differ automatically.
+Since the source code for this paper is open source under the MIT license, anyone can freely copy, modify and build on this work.
+This also makes for an open and transparent voting method where every voter can audit the system in use.
 \pagebreak

### 2017-05-12 paper/paper.tex
Improvements

@@
 \input{config.tex}
+
+\usepackage{dirtree}
 
@@
 Taking a collective decision as a population is difficult.
-To solve this issue, voting systems with defined rules are used.
+To solve this issue, various voting systems with defined rules are used.
 They are used to show common preferences within a population, for example what politician a population wants to see elected.
@@
 The purpose of this essay is to evaluate differences and similarities in terms of election results in three different voting systems: Single Transferable Vote (STV), First-Past-The-Post (FPTP) and the Schulze Method.
-This paper will only be examining and discussing differences and similarities in the results of the methods, not touching on how practically feasible the methods might be in actual election.
+This paper will only be examining and discussing differences and similarities in the results of the methods, not touching on how practically feasible the methods might be in actual elections.
 \pagebreak
@@
 Simply put: there is no perfect voting system and never will be.
-This does however not mean that all voting systems are equally efficient, elegant or accurate.
+This does, however, not mean that all voting systems are equally efficient, elegant or accurate.
 
-There are several ways of evaluating voting methods that are used.
+There are several ways of evaluating voting methods.
 One is the mathematical approach of evaluating what criteria are important to meet and finding methods that satisfy them.
-Another is by testing and finding probabilities that some criteria are broken — A method that fails to meet a certain criteria only in very few cases is perhaps not that big of a problem.
+Another is by testing and finding probabilities that some criteria are broken — A method that fails to meet a certain criterion only in very few cases is perhaps not a big problem.
 A third way of evaluating methods is not by mathematical criteria, but other metrics such as voter satisfaction or how likely someone is to vote tactically.
@@
 \begin{itemize}
-	\item A \textit{candidate} is someone a voter can vote to elect. Can also be considered as being parties that a voter can vote for.
-	\item An \textit{election} is an event in which voters cast ballots to vote on candidates
+	\item A \textit{candidate} is someone a voter can vote for to elect. It can also be considered as being a party that a voter can vote for.
+	\item An \textit{election} is an event in which voters cast ballots to vote for candidates
 	\item A \textit{seat} is something a candidate can be elected to. A candidate may for example be elected to hold a seat of parliament.
-	\item An \textit{ideology} is a group that both candidates and voters can identify with. They split the whole voting population into several blocks.
+	\item An \textit{ideology} is a group that both candidates and voters can identify with. They split the whole voting population into several blocks. Several candidates can belong to one ideology.
 \end{itemize}  
@@
 Typescript is a superset of JavaScript with multiple extra features.
-Most importantly Typescript has optional static type checking.
+Most importantly, Typescript has optional static type checking.
 Sample code written in Typescript can be seen in code example~\ref{lst:typescript example}.
@@
 There are cases where extensive election data is published, such as in Maltese elections, but full ballot data, which is needed as input for the implementations used in this paper has not been found.
-Instead, the algorithms will be tested with data generated from a simple computer program.
-The algorithm used for this purpose in this paper is highly primitive, as modeling preferences within a population is far beyond the scope of this paper.
+Instead, the algorithms will be tested with data generated from a simple ballot-generating computer program.
+The program used for this purpose in this paper is highly primitive, as modeling preferences within a population is far beyond the scope of this paper.
 The full ballot generation program can be found in the \Code{/generator} folder.
@@
 \begin{enumerate}
-	\item It relates each candidate to an ideology based on the size of the ideology. A larger ideology has more candidates.
-	\item It assigns a base size for each candidate.
-Each ideology has a different spread of votes generated by a negative exponential function with a different constant.
-The size of each candidate is then multiplied with the size of their ideology and normalized.
-This gives a base size of all candidates.
-	\item Based on the base size of each candidate, a probability-list of voting for each candidate is created for every ideology.
-An ideology's probability-list represents how a voter aligned the ideology is likely to vote.
+	\item It assigns each candidate to an ideology based on the size of the ideology. A larger ideology has more candidates.
+	\item It creates a base ``strength'' to each candidate.
+Within each ideology, every candidate is assigned its relative strength.
+The relative strength is generated by a negative exponential function with a different constant (based on the \Code{candidatePower}).
+The strength of each candidate is then multiplied by the size of their ideology and then normalized.
+This gives a base strength of all candidates.
+This simulates the probability for vote from a non-ideological voter for a particular candidate.
+	\item Based on the base strength of each candidate, a probability distribution of votes for each candidate is created for each ideology.
+This process takes  the  \Code{ideologyPower} constant into account.
+An ideology's probability distribution represents how a voter aligned with the ideology is likely to vote.
+A strong ideology may thus attract votes from voters aligned with another ideology.
 	\item It creates a certain number of individual ballots.
-Each ballot is given an ideology and creates its own list preferences via weighted random number generation according to the probability-list of its assigned ideology.
+Each ballot is given an ideology and based on the probability distribution of that particular ideology, it creates its own list of preferences for candidates.
+This is done via weighed random number generation.
 \end{enumerate}
 The output of the program is a set of ballots, where each ballot is an ordered set of preferences between candidates.
-The implementation is highly arbitrary and all constants in the program even more so.
+The implementation is highly arbitrary and as are all constants.
 However, expanding on the generator program would be beyond the scope of this project.
@@
 \subsection{Constructing test scenarios}
-Constructing test scenarios is difficult task.
-Due to there being so many variables both in real elections and the simulated elections in the generator program, it makes it practically impossible to control all variables.
+Constructing test scenarios, ie.\ election conditions, is difficult task.
+Due to there being so many variables both in real elections and the simulated elections in the generator program, it makes it practically impossible to control for all variables.
 Instead, 3 arbitrary test scenarios will be used.
-An election will be simulated 1000 times for each scenario and the election data will then run through the different voting algorithms and the results will be compared.
-The simulation scenarios are arbitrary but should allow for comparison of the different voting methods.
-All simulations will have 3 ideologies and 500 voters.
+An election will be run 1000 times for each scenario and the election data will then processed by each voting algorithm and the results will be compared.
+The three simulation scenarios are arbitrary but should allow for comparison of the different voting methods.
+All simulations will have three ideologies and 500 ballots.
 \subsubsection{Scenario 1}
@@
 The scenario is built around electing one candidate out of eight.
-The spread of votes within ideologies is flat and all ideologies are so called ``weak''.
+The spread of votes within ideologies is ``flat'' and all ideologies are so called ``weak''.
 This means that the general spread of votes between candidates will be even.
@@
 The second scenario elects 3 candidates out of 9 total.
-It features a normal spread of votes between candidates.
+The parameters are set to produce a ``normal'' spread of votes between candidates.
 An example distribution of first-preference votes generated in this scenario can be seen in figure~\ref{fig:example of scenario 2}.
@@
 The misrepresentation metric gives an idea of how \textit{proportional} the outcomes of a certain voting method in any scenario is.
-The level of proportionality of a result is a measure of how closely the preferences of a population are matched with the result.
-Higher proportionality means that the outcome more closely resembles the preferences of the voters.
+The level of proportionality of a result is a measure of how closely the preferences of a population in terms of ideology are matched with the result.
+Higher proportionality means that the election outcome more closely resembles the ideological preferences of the voters.
 The method of calculating the misrepresentation used in this paper is defined as follows:
 \begin{enumerate}
-	\item Calculate what theoretical election outcome would be the most proportionate based on the configuration file used to generate the ballots.\label{enum:theoretical}
+	\item Calculate what theoretical election outcome would be the most proportionate in terms of ideology based on the configuration file used to generate the ballots.\label{enum:theoretical}
 	\item Compare the actual outcomes of a certain method with the theoretical result obtained in Step~\ref{enum:theoretical}.
@@
 \subsubsection{Description}
-The first-past-the-post voting method is a method designed for electing one or several candidates out of a set of candidates.
-Each voter has one (1) vote that may be allocated to any candidate.
+The first-past-the-post voting method is a method designed for electing one or several (N) candidates out of a set of candidates.
+Each voter has one vote that may be allocated to any candidate.
 In a FPTP election the N candidates with most votes get elected.
@@
 The first-past-the-post method is widely used in for example the United Kingdom and United States.
-Comparisons with this method can also be easily made.
+Comparisons with this method can also easily be made.
 \subsubsection{Pseudocode}
@@
 In an STV election, voters are given ballots in which they are supposed to rank candidates in order.
-The specific rules for wether one needs to rank all candidates or just a few not can vary.
+The specific rules for wether one needs to rank all candidates or just a few can vary.
 For the sake of simplicity, all candidates must be ranked at unique and linear values in this implementation.
@@
 
-Using this data, votes are transferred between candidates within a ballot in the method, hence the name Single Transferable Vote.
-The method relies on the concept of a quota, which is the number of votes you need to be elected.
+Using this data, votes are transferred between candidates within a ballot, hence the name Single Transferable Vote.
+The method relies on the concept of a quota, which is the number of votes one needs to be elected.
 The Droop-Quota, defined as $(\frac{\text{total valid poll}}{\text{seats} + 1})+1$, is often used and is the one implemented in this paper.
@@
 \subsubsection{Implementation}
-The single transferable vote algorithm uses a tree structure to represent the state of the election.
+The STV algorithm uses a tree structure to represent the state of the election.
 Every candidate is a top-level node with an attribute showing the number of current votes for the candidate.
@@
 The Schulze Method is a method used mainly to determine results in single-winner elections but can also be used to provide rankings and elect multiple candidates in a single election \autocite{Schulze2011}.
-Ballots are identical to those of the single transferable vote (see figure~\ref{fig:stv ballot} on page~\pageref{fig:stv ballot}).
+Ballots are identical to those of the Single Transferable Vote (see figure~\ref{fig:stv ballot} on page~\pageref{fig:stv ballot}).
 The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate wins.
@@
 The Schulze Method also provides a linear ranking between all candidates, for example that $E > B > A > C > D$.
-By selecting the $N$ top candidates you can use the method for a multi-seat election.
+By selecting the $N$ top candidates one can use the method for a multi-seat election.
 As the process can become very complex as the number of candidates grow, a computer is needed to resolve large elections.
@@
 The output of the program is a list of winners.
-The program first creates the matrices for both the preferences and paths between candidates as seen in Code Example~\ref{lst:schulze-mapsb}.
+The program first creates the matrices for both the preferences and paths between candidates as seen in Code Example~\ref{lst:schulze-maps}.
 \codeblock{code/schulze/maps.ts}{lst:schulze-maps}{Data representation}
@@
 \label{sec:resuls-scenario1}
-Scenario 1 featured 8 candidates where one was to be elected.
-Vote spread was flat, meaning that votes tend to be diverse in their preferences.
+Scenario 1 featured eight candidates where one was to be elected.
+Vote spread was flat, meaning that votes tended to be diverse in their preferences.
 This means that there is not an obvious winner present.
@@
 Key metrics for the results in this scenario can be found in table~\ref{tab:scenario 1 result}.
-Although the misrepresentation metric is not entirely accurate, especially when few seats are elected, it shows that fptp is not entirely representative.
+The misrepresentation metric show that FPTP is not entirely representative.
 The STV and Schulze method seem to produce very similar results.
@@
 \label{sec:resuls-scenario2}
-Scenario 2 featured 9 candidates of which 3 were to be elected.
+Scenario 2 featured nine candidates of which three were to be elected.
 The distribution of votes was ``normal'', and as seen in figure~\ref{fig:example of scenario 2} on page~\ref{fig:example of scenario 2}, the election is very close with many candidates having a similar percentage of first-preference votes.
@@
 \label{sec:resuls-scenario3}
-Scenario 3 featured 9 candidates of which 3 were to be elected.
+Scenario 3 featured nine candidates of which three were to be elected.
 The distribution of votes was  ``steep''.
@@
 \begin{enumerate}
-	\item Schulze did not seem like a proportional voting method in multi-seat elections.\label{num:conclusion-schulze}
+	\item Schulze did not seem to be a proportional voting method in multi-seat elections.\label{num:conclusion-schulze}
 
@@
 While the methods work very differently, the results in these methods seem to behave similarly in single-seat elections.
-	\item FPTP did not seem like a very proportional method in close elections.
+	\item FPTP did not seem to be a very proportional method in close elections.
 
@@
 While there is no perfect voting system, they all preform differently.
-From the conclusions outlined above, a decision of what system to use between the three voting systems used in this paper can be taken.
+From the conclusions outlined above, a decision can be taken about what system analyzed in this paper to be used.
 Generally, if a proportional representation is desired (which in a democracy it usually is), STV will likely be the most appropriate method to use.
@@
 
-While the findings of this paper are hardly revolutionary, the nature of the three voting systems used in this paper and their behavior is experimentally evaluated.
-The paper also provides implementations of all voting methods in both TypeScript and JavaScript.
+While the findings of this paper are hardly revolutionary, the nature of the three voting systems explored in this paper and their behavior is experimentally evaluated.
+The paper also provides implementations of all voting methods in both Typescript and JavaScript.
 
@@
 One could also write software that generates lots of scenarios with different parameters and analyzes how they differ automatically.
-Since the source code for this paper is open source under the MIT license, anyone can freely copy, modify and build on this work.
+Since the source code for this paper is open sourced under the MIT License, anyone can freely copy, modify and build on this work.
 This also makes for an open and transparent voting method where every voter can audit the system in use.
@@
 \printbibliography{}
+\pagebreak
+\begin{appendices}
+\section{Code}
+The full source code for this project can be found at \url{https://github.com/adriansalamon/gymnasiearbete} and is open sourced under the MIT License.
+In order to run any of the implementations, the Typescript files need to be compiled to JavaScript files using the Typescript Compiler.
+Then the code can be executed using Node.js.
+Code Example \ref{lst:project-example} shows an example of how to run an election.
+\codeblock{code/projectExample.ts}{lst:project-example}{Example of how to run a Schulze Election with the code.}
+All source code is commented and includes extensive use type annotations to help with orientation. The full project structure can be seen in Figure~\ref{fig:project-structure}.
+\begin{figure}[H]
+\dirtree{%
+.1 /.
+.2 fptp/.
+.3 index.ts.
+.2 generator/.
+.3 ballots.ts.
+.3 index.ts.
+.3 candidates.ts.
+.3 interfaces.ts.
+.2 schulze/.
+.3 index.ts.
+.2 stv/.
+.3 candidate.ts.
+.3 tree.ts.
+.3 election.ts.
+.3 index.ts.
+.2 testing/.
+.3 standardDeviation.ts.
+.3 test.ts.
+.2 .gitignore.
+.2 LICENSE.txt.
+.2 package.json.
+.2 README.md.
+.2 tsconfig.json.
+}
+\caption{Project structure}
+\label{fig:project-structure}
+\end{figure}
+
+\end{appendices}
 

### 2017-05-12 paper/code/projectExample.ts

@@ -1,0 +1,4 @@
+import schulze from '/path/to/schulze'
+const ballots = [[0,1,2],[2,1,0],[0,2,1]]
+const seats = 1
+const electionWinners = schulze(ballots, seats)

### 2017-05-12 schulze/index.ts

@@ -1,5 +1,3 @@
-//let fakeData = [[0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 2, 1, 4, 3], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [0, 3, 4, 2, 1], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [1, 4, 3, 0, 2], [2, 0, 1, 4, 3], [2, 0, 1, 4, 3], [2, 0, 1, 4, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 0, 4, 1, 3], [2, 1, 0, 3, 4], [2, 1, 0, 3, 4], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [3, 2, 4, 1, 0], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2], [4, 1, 0, 3, 2]]
-
 interface PairMap {
     [key: number]: {
         [key: number]: number

### 2017-05-12 testing/standardDeviation.ts

@@ -1,3 +1,4 @@
+// Calculates the standard deviation of an array of numbers
 export default function (numbers: number[]): number {
     let n = numbers.length
     let s = (numbers.reduce((a,b) => a+b)**2)/n

### 2017-05-13 paper/paper.tex
Cleaned up project

@@
 \begin{appendices}
-\section{Code}
-The full source code for this project can be found at \url{https://github.com/adriansalamon/gymnasiearbete} and is open sourced under the MIT License.
-In order to run any of the implementations, the Typescript files need to be compiled to JavaScript files using the Typescript Compiler.
-Then the code can be executed using Node.js.
-Code Example \ref{lst:project-example} shows an example of how to run an election.
-\codeblock{code/projectExample.ts}{lst:project-example}{Example of how to run a Schulze Election with the code.}
-All source code is commented and includes extensive use type annotations to help with orientation. The full project structure can be seen in Figure~\ref{fig:project-structure}.
+\section{Code implementation}
 \begin{figure}[H]
@@
 .3 index.ts.
-.2 testing/.
-.3 standardDeviation.ts.
-.3 test.ts.
 .2 .gitignore.
@@
 .2 tsconfig.json.
+.2 tslint.json.
 }
@@
 \end{figure}
+The full source code for this project can be found at \url{https://github.com/adriansalamon/gymnasiearbete} and is open sourced under the MIT License.
+In order to run any of the implementations, the Typescript files (\Code{.ts}) need to be compiled to JavaScript files (\Code{.js}) using the Typescript Compiler.
+Then the code can be executed using Node.js.
+Code Example \ref{lst:project-example} shows an example of how to run an election.
+\codeblock{code/projectExample.ts}{lst:project-example}{Example of how to run a Schulze Election with the code.}
+All source code is commented and includes extensive use type annotations to help with orientation. The full project structure can be seen in Figure~\ref{fig:project-structure}.
 

### 2017-05-13 testing/standardDeviation.ts

@@ -1,13 +1,0 @@
-// Calculates the standard deviation of an array of numbers
-export default function (numbers: number[]): number {
-    let n = numbers.length
-    let s = (numbers.reduce((a,b) => a+b)**2)/n
-    let sSquared = numbers.map(a => a**2).reduce((a,b) => a+b)
-
-    let d = sSquared - s
-
-    let standardDeviation = (d/(n))**0.5
-
-    return standardDeviation
-}
-

### 2017-05-13 testing/testing.ts

@@ -1,177 +1,0 @@
-// This file was used in doing the testing needed to obtain results for the paper
-
-
-import { Ideology, IdeologyWithProbabilities } from '../generator/interfaces'
-import { createIdeologyProbabilities, generateBallots} from '../generator'
-import getStandardDeviation from './standardDeviation'
-
-import fptp from '../fptp'
-import stv  from '../stv'
-import schulze from '../schulze'
-
-interface Result {
-    stv: number[], 
-    fptp: number[], 
-    schulze: number[]
-}
-
-interface FormattedResults {
-    stv: {
-        candidate: number,
-        wins: number
-    }[],
-    fptp: {
-        candidate: number,
-        wins: number
-    }[],
-    schulze:{
-        candidate: number,
-        wins: number
-    }[]
-}
-
-interface Candidate {
-    candidate: number,
-    wins: number
-}
-
-
-const ballots = 500
-
-const candidates = 9
-const seats = 3
-const ideologies: Ideology[] = [{
-    size: 0.2,
-    candidatePower: 1.8,
-    ideologyPower: 0.6
-}, {
-    size: 0.3,
-    candidatePower: 1.6,
-    ideologyPower: 0.6
-}, {
-    size: 0.5,
-    candidatePower: 2,
-    ideologyPower: 0.6
-}]
-
[…]

### 2017-05-13 paper/paper.tex
Added references

@@
 \begin{abstract}
+	I heard that it's good to have lots of references in the abstract.
 \end{abstract}
@@
 They are used to show common preferences within a population, for example what politician a population wants to see elected.
-Several types of systems have been designed for this purpose and there are a myriad of variations of those systems.
+Several types of systems have been designed for this purpose and there are a myriad of variations of those systems \autocite{fairvoteND}.
 They range from simple methods such as “most votes win” to complex processes that can only be practically carried out by a computer.
@@
 
-There are several ways of evaluating voting methods.
-One is the mathematical approach of evaluating what criteria are important to meet and finding methods that satisfy them.
+There are several ways of evaluating voting methods \autocite{green-armytageND}.
+One is the mathematical approach of evaluating what criteria are important to meet and finding methods that satisfy them \autocite{woodwall1994}.
 Another is by testing and finding probabilities that some criteria are broken — A method that fails to meet a certain criterion only in very few cases is perhaps not a big problem.
@@
 Sample code written in Typescript can be seen in code example~\ref{lst:typescript example}.
+The full source code with instructions for how to run the code can be found in Appendix~\ref{sec:conde implementation}.
 \codeblock{code/typescriptexample.ts}{lst:typescript example}{Basic Typescript syntax}
@@
 The misrepresentation metric gives an idea of how \textit{proportional} the outcomes of a certain voting method in any scenario is.
-The level of proportionality of a result is a measure of how closely the preferences of a population in terms of ideology are matched with the result.
+The level of proportionality of a result is a measure of how closely the preferences of a population in terms of ideology are matched with the result \autocite{king200}.
 Higher proportionality means that the election outcome more closely resembles the ideological preferences of the voters.
@@
 Each voter has one vote that may be allocated to any candidate.
-In a FPTP election the N candidates with most votes get elected.
+In a FPTP election the N candidates with most votes get elected \autocite{wilkinson2017}.
 \subsubsection{Justification}
 The method is simple and can easily be understood.
-The first-past-the-post method is widely used in for example the United Kingdom and United States.
+The first-past-the-post method is widely used in for example the United Kingdom and United States \autocite{aceND}.
 Comparisons with this method can also easily be made.
@@
 \subsubsection{Description}
-The Single Transferable Vote (STV) is a more complicated voting system than the first-past-the-post method.
+The Single Transferable Vote (STV) is a more complicated voting system than the first-past-the-post method \autocite{electotal-reform-society2015}.
 STV is a multi-seat election method, although it can be used for single-seat elections too.
@@
 If there still are seats yet to be filled, the candidate with fewest votes is eliminated and his/her votes are transferred to the next choice on the ballots which supported the candidate.
-This process is repeated until all seats are filled.
+This process is repeated until all seats are filled \autocite{king200}.
 The process can become quite complex with many ballots and transferring of fractional votes.
@@
 STV is an established voting method in use in several countries.
-It is used for parliamentary elections in Ireland, Malta and Australia as well as being used in local and regional elections across the world.
+It is used for parliamentary elections in Ireland, Malta and Australia as well as being used in local and regional elections across the world \autocite{tideman1995single}.
 \subsubsection{Pseudocode}
@@
 Ballots are identical to those of the Single Transferable Vote (see figure~\ref{fig:stv ballot} on page~\pageref{fig:stv ballot}).
-The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate wins.
+The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate  \autocite{johnson2005}.
 As mentioned, this method relies on comparing the preferences of every candidate to one another as shown in table~\ref{tab:pairwise comparison matrix}.
@@
 The difficult problem in this method is finding the strongest path between candidates.
-The problem is called the widest path problem in graph theory.
-An efficient and relatively simple way to compute this problem is via the Floyd-Warshall algorithm which is used in the implementation.
+The problem is known as the widest path problem in graph theory.
+An efficient and relatively simple way to compute this problem is via the Floyd-Warshall algorithm which is used in the implementation \autocite{wikipedia2017warshall}.
 See Code Example~\ref{lst:schulze algorithm} for the full algorithm.
@@
 \subsubsection{Justification}
-The Schulze method is used by multiple organizations around the world.
+The Schulze method is used by multiple organizations around the world \autocite{wikipedia2017schulze2}.
 It has been used by various software organizations such as The Wikimedia Foundation, The Debian Project and Ubuntu.
@@
 
-\printbibliography{}
+\printbibliography[
+heading=bibintoc,
+title={References}
+]
 \pagebreak
@@
 \section{Code implementation}
+\label{sec:conde implementation}
 \begin{figure}[H]
@@
 \end{figure}
-The full source code for this project can be found at \url{https://github.com/adriansalamon/gymnasiearbete} and is open sourced under the MIT License.
+The full source code for this project can be found at \url{https://github.com/adriansalamon/gymnasiearbete}.
+It is open sourced under the MIT License.
 In order to run any of the implementations, the Typescript files (\Code{.ts}) need to be compiled to JavaScript files (\Code{.js}) using the Typescript Compiler.

### 2017-05-13 paper/paper.tex
Final for opposition

@@
 \begin{abstract}
-	I heard that it's good to have lots of references in the abstract.
+	\noindent Various voting methods are in use across the world.
+They range from simple processes that everyone can understand to complex mathematical systems.
+This essay examines differences and similarities of the behavior of three voting methods: the Single Transferable Vote (STV), first-past-the-post (FPTP), and Schulze Method.
+This is done by implementing each voting method in Typescript and then running election data into them.
+This paper provides descriptions, pseudocode and implementations of each method.
+A program to generate voting results was developed in order to test the voting methods.
+The methods are evaluated in both singe-seat and multi-seat elections.
+No revolutionary results are presented, but the behavior of each method is evaluated experimentally.
+Several conclusions are drawn about the behavior of the methods, including to what degree the different methods provided proportionate results.
+\end{abstract}
+\renewcommand{\abstractname}{Referat}
+\pagebreak
+\begin{abstract}
+  \begin{center}
+  	\textbf{Mjukvaruimplementationer och analys av tre valsystem}  
+  \end{center} 
+  \noindent Flera valsystem används i världen.
+De kan vara allt ifrån enkla processer som alla kan förstå till komplexa matematiska system.
+Denna uppsats undersöker skillnader och likheter mellan tre valsystem: Enkel Överförbar Röst, Majoritetsval och Schulze-metoden.
+Detta genom att implementera alla valsystem i Typescript och testa de med olika valdata.
+Denna uppsats innehåller beskrivningar, pseudokod samt en implementationer för alla valsystem.
+Ett program för att generera valdata utvecklades för att testa de olika systemen.
+Valsystemen testades i både enmans- och flermansval.
+Inga revolutionerande resultat presenteras, men varje systems beteende undersökts experimentellt.
+Flera slutsatser dras från de olika systemens beteende, inklusive hur proportionella resultat systemen producerade.
 \end{abstract}
@@
 Then the code can be executed using Node.js.
-Code Example \ref{lst:project-example} shows an example of how to run an election.
+Code Example~\ref{lst:project-example} shows an example of how to run an election.
 \codeblock{code/projectExample.ts}{lst:project-example}{Example of how to run a Schulze Election with the code.}

### 2017-05-13 paper/paper.tex
Typo

@@
   \begin{center}
-  	\textbf{Mjukvaruimplementationer och analys av tre valsystem}  
+  	\noindent \textbf{Mjukvaruimplementationer och analys av tre valsystem}  
   \end{center} 
@@
 Detta genom att implementera alla valsystem i Typescript och testa de med olika valdata.
-Denna uppsats innehåller beskrivningar, pseudokod samt en implementationer för alla valsystem.
+Denna uppsats innehåller beskrivningar, pseudokod samt implementationer för alla valsystem.
 Ett program för att generera valdata utvecklades för att testa de olika systemen.

### 2017-05-14 paper/paper.tex
Reference error
Made formatting  nicer

@@
 This paper will only be examining and discussing differences and similarities in the results of the methods, not touching on how practically feasible the methods might be in actual elections.
-\pagebreak
 \section{Theory}
@@
 \end{itemize}  
-\pagebreak
 \section{Methodology}
@@
 Shows what candidates, given a certain scenario, are most likely to win in a particular method.
-\pagebreak
 \section{Specification of voting methods}
@@
 \subsubsection{Justification}
-The Schulze method is used by multiple organizations around the world \autocite{wikipedia2017schulze2}.
+The Schulze method is used by multiple organizations around the world \autocite{wikipedia2017schulze}.
 It has been used by various software organizations such as The Wikimedia Foundation, The Debian Project and Ubuntu.
@@
 let $d[i,j]$ be the number of ballots that prefer candidate $i$ to candidate $j$\\
-let $p[i,j]$ be the strength of the strongest path from candidate $i$ to candidate $j$\\
-let $C$ be the number of candidates
+let $p[i,j]$ be the strength of the strongest path from candidate $i$ to $j$\\
 for $i$ from 1 to $C$\\
@@
 The output of the program is a list of winners.
-The program first creates the matrices for both the preferences and paths between candidates as seen in Code Example~\ref{lst:schulze-maps}.
+Data representation can be seen in Code Example~\ref{lst:schulze-maps}.
 \codeblock{code/schulze/maps.ts}{lst:schulze-maps}{Data representation}
@@
 The results in scenario 2 can be observed in figure~\ref{fig:scenario 2 result} and the key metrics can be seen in table~\ref{tab:scenario 2 result}.
+\begin{table}[H]
+\centering
+\caption{Key metrics for result in scenario 2}
+\label{tab:scenario 2 result}
+\begin{tabular}{@{}lccc@{}}
+\toprule
+Method & Standard deviation & Misrepresentation & Most likely winners \\ \midrule
+FPTP & 418 & 50 & 0, 2 \& 5 \\
+STV & 388 & 47 & 1, 2 \& 5 \\
+Schulze & 393 & 100 & 2, 5 \& 7  \\ \bottomrule
+\end{tabular}
+\end{table}
 \begin{figure}[H]
@@
 
-\begin{table}[H]
-\centering
-\caption{Key metrics for result in scenario 2}
-\label{tab:scenario 2 result}
-\begin{tabular}{@{}lccc@{}}
-\toprule
-Method & Standard deviation & Misrepresentation & Most likely winners \\ \midrule
-FPTP & 418 & 50 & 0, 2 \& 5 \\
-STV & 388 & 47 & 1, 2 \& 5 \\
-Schulze & 393 & 100 & 2, 5 \& 7  \\ \bottomrule
-\end{tabular}
-\end{table}
 % [ 418.13628234977, 388.17206952015, 393.25535950293 ]
@@
 The key metrics can be found in table~\ref{tab:scenario 3 result}.
+\begin{table}[H]
+	\centering
+	\caption{Key metrics for result in scenario 3}
+\label{tab:scenario 3 result}
+	\begin{tabular}{@{}lccc@{}}
+		\toprule
+		Method & Standard deviation & Misrepresentation & Most likely winners \\ \midrule
+		FPTP & 470 & 0 & 0, 1 \& 2 \\
+		STV & 471 & 0 & 0, 1 \& 2 \\
+		Schulze & 471 & 0 & 0, 1 \& 2  \\ \bottomrule
+	\end{tabular}
+\end{table}
 \begin{figure}[H]
@@
 \end{figure}
-
-\begin{table}[H]
-	\centering
-	\caption{Key metrics for result in scenario 3}
-\label{tab:scenario 3 result}
-	\begin{tabular}{@{}lccc@{}}
-		\toprule
-		Method & Standard deviation & Misrepresentation & Most likely winners \\ \midrule
-		FPTP & 470 & 0 & 0, 1 \& 2 \\
-		STV & 471 & 0 & 0, 1 \& 2 \\
-		Schulze & 471 & 0 & 0, 1 \& 2  \\ \bottomrule
-	\end{tabular}
-\end{table}
 \section{Conclusion}

### 2017-05-14 paper/code/stv/distribute.ts

@@ -1,4 +1,4 @@
-// Distributes a list of nodes onto the tree. Returns a new tree.
+// Distributes nodes onto the tree. Returns new tree.
 function distribute(nodeList: CandidateNode[], tree: CandidateNode[], winners: number[]): CandidateNode[] {
     // Loops through each candidate node in the list
     for (let i = 0; i < nodeList.length; i++) {

### 2017-05-15 paper/paper.tex
Fixed missing word

@@
 Ballots are identical to those of the Single Transferable Vote (see figure~\ref{fig:stv ballot} on page~\pageref{fig:stv ballot}).
-The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate  \autocite{johnson2005}.
+The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate will win \autocite{johnson2005}.
 As mentioned, this method relies on comparing the preferences of every candidate to one another as shown in table~\ref{tab:pairwise comparison matrix}.

### 2017-05-18 paper/presentation.tex
Added presentation

\documentclass[xcolor=table]{beamer}

\mode<presentation>
{
  \usetheme{Madrid}      % or try Darmstadt, Madrid, Warsaw, ...
  \usecolortheme{beaver} % or try albatross, beaver, crane, ...
  \usefonttheme{professionalfonts}
  \setbeamertemplate{navigation symbols}{}
}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{tikz}
\usepackage{pgfplots}
\graphicspath{ {images/} }
\pgfplotsset{compat=1.14}

\title[Analysis of 3 voting systems]{Software implementations and analysis of three voting systems}
\author{Adrian Salamon}
\institute[Kungsholmens gymn.]{Kungsholmens gymnasium}
\date{\today}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\section{Introduction}
\begin{frame}{Introduction}
\begin{itemize}
    \item What is a voting system?
    \item Have been interested in voting systems and wanted to test them
    \item Testing 3 methods
    \begin{itemize}
        \item First-past-the-post (FPTP)
        \item Single Transferable Vote (STV)
        \item Schulze method
    \end{itemize}
    \item Everything is done by programming
\end{itemize}

\end{frame}

\section{Voting systems}
\subsection{First-past-the-post}
\begin{frame}{First-past-the-post (FPTP)}
\begin{itemize}
    \item Simple majority system
    \item ``Most votes win'' and ``One person, one vote''
    \item Used widely in the Anglo-Saxon world
\end{itemize}
\centering
Example: Elect 2 from this sample:
\begin{overprint}
    \onslide<1> 
\begin{figure}[H]
	\centering
	\begin{tikzpicture}
		\begin{axis}[
			ybar stacked,
			width = 0.7\textwidth,
			height = 0.4\textwidth,
			legend style={at={(0.5,-0.25)},
			anchor=north,legend columns=-1},
      x tick style = transparent,
			ylabel = {Votes},
			xlabel = {Candidate},
			ymajorgrids = true,
      ymin = 0,
			yticklabel={\pgfmathprintnumber\tick\%}
      ]
			\addplot coordinates
			{(0, 20)(1, 19)(2, 22)(3, 11)(4, 8)(5, 12)(6, 8)};
		\end{axis}
	\end{tikzpicture}
\end{figure}
    \onslide<2>
\begin{figure}[H]
	\centering
	\begin{tikzpicture}
		\begin{axis}[
			ybar stacked,
			width = 0.7\textwidth,
			height = 0.4\textwidth,
			legend style={at={(0.5,-0.25)},
			anchor=north,legend columns=-1},
      x tick style = transparent,
			ylabel = {Votes},
			xlabel = {Candidate},
			ymajorgrids = true,
      ymin = 0,
			yticklabel={\pgfmathprintnumber\tick\%}
      ]
			\addplot coordinates
			{(0, 0)(1, 19)(2, 0)(3, 11)(4, 8)(5, 12)(6, 8)};
            \addplot coordinates
			{(0, 20)(1, 0)(2, 22)(3, 0)(4, 0)(5, 0)(6, 0)};
		\end{axis}
	\end{tikzpicture}
\end{figure}
\end{overprint}

\end{frame}

\subsection{Single Transferable Vote}
\begin{frame}{Single Transferable Vote (STV)}
\begin{itemize}
    \item Uses ballots where voters rank candidates in order
    \item Uses this data to transfer votes between candidates within a ballot
    \item A quota/threshold is defined
    \item If a candidate exceeds threshold, excess votes are transferred
    \item If no candidate reaches threshold, the candidate with fewest votes gets eliminated and his/her votes are transferred
\end{itemize}
\begin{figure}
	\centering
	\includegraphics[height=80px]{ballot}
\label{fig:stv ballot}
\end{figure}
\end{frame}
\subsection{Schulze method}
\begin{frame}{Schulze method}
\begin{itemize}
    \item Is a \textit{Condorcet method}
    \item Compares all candidates in pairwise comparisons
    \item If any candidate wins every pairwise comparison, he/she is the Condorcet winner
    \item If there is no such candidate, path strengths are calculated and compared
\end{itemize}
\begin{table}
\centering
\begin{tabular}{l|c|c|c|c|c|}
\cline{2-6}
 & \multicolumn{1}{l|}{A} & \multicolumn{1}{l|}{B} & \multicolumn{1}{l|}{C} & \multicolumn{1}{l|}{D} & \multicolumn{1}{l|}{E} \\ \hline
\multicolumn{1}{|l|}{A} & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}17 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{DDFFDD}35 & \cellcolor[HTML]{DDFFDD}30 \\ \hline
\multicolumn{1}{|l|}{B} & \cellcolor[HTML]{DDFFDD}33 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}24 & \cellcolor[HTML]{DDFFDD}47 & \cellcolor[HTML]{DDFFDD}36 \\ \hline
\multicolumn{1}{|l|}{C} & \cellcolor[HTML]{DDFFDD}36 & \cellcolor[HTML]{DDFFDD}26 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{DDFFDD}40 & \cellcolor[HTML]{DDFFDD}42 \\ \hline
\multicolumn{1}{|l|}{D} & \cellcolor[HTML]{FFDDDD}15 & \cellcolor[HTML]{FFDDDD}3 & \cellcolor[HTML]{FFDDDD}10 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}18 \\ \hline
\multicolumn{1}{|l|}{E} & \cellcolor[HTML]{FFDDDD}20 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{FFDDDD}8 & \cellcolor[HTML]{DDFFDD}32 & \cellcolor[HTML]{9B9B9B} \\ \hline
\end{tabular}
\end{table}
\end{frame}

\section{Methodology}
\subsection{Vote generation}
\begin{frame}{Generation of vote data}
\begin{itemize}
    \item No publicly available election data was found
    \item A program to create elections was developed
    \item Better than random data
    \item Includes the concept of an ``ideology'' that split the population.
    \item The program takes a simple configuration object and generates an election result
    \item Three election scenarios were tested, each based on a different configuration object
\end{itemize}

\end{frame}
\subsection{Implementations}
\begin{frame}{Programming implementations}
\begin{itemize}
    \item Everything was implemented in Typescript and tested.
    \item All code is open sourced under the MIT licence and available on Github.
    \item Added 5547 thousand lines and deleted 3305 thousand lines
    \item \url{https://github.com/adriansalamon/gymnasiearbete}
\end{itemize}
\end{frame}

\section{Results and conclusions}
\subsection{Example of Results}
\begin{frame}{Example of results}
\begin{figure}[H]
	\centering
	\begin{tikzpicture}
		\begin{axis}[
			ybar,
			width = 1\textwidth,
			height = 0.7\textheight,
			legend style={at={(0.5,-0.25)},
			anchor=north,legend columns=-1},
      x tick style = transparent,
			ylabel = {Elections won},
			xlabel = {Candidate},
			ymajorgrids = true,
			every axis plot/.append style={draw=none,fill,no markers},
      ymin = 0,
			symbolic x coords={0,1,2,3,4,5,6,7,8},
			bar width=0.25cm
      ]
			\addplot coordinates
			{(0, 973)(1, 267)(2, 1000)(3, 0)(4, 12)(5, 743)(6, 0)(7, 5)(8, 0)};
			\addplot coordinates
			{(0, 456)(1, 808)(2, 1000)(3, 0)(4, 33)(5, 703)(6, 0)(7, 0)(8, 0)};
			\addplot coordinates
			{(0, 338)(1, 160)(2, 1000)(3, 0)(4, 0)(5, 1000)(6, 0)(7, 502)(8, 0)};
			\legend{FPTP, STV, Schulze}
		\end{axis}
	\end{tikzpicture}
\end{figure}

\end{frame}
\subsection{Conclusions}
\begin{frame}{Conclusions}
I made 4 conclusions:
\begin{itemize}
    \item Schulze did not seem to be a proportional voting method in multi-seat elections
    \item In single-seat elections, Schulze and STV seemed to provide similar results
    \item FPTP did not seem to be a very proportional method in close elections
    \item STV seems to be the most proportional method out of the 3 tested, but is not without its flaws
\end{itemize}
\end{frame}

\subsection{Further work}
\begin{frame}{Further work}
\begin{itemize}
    \item Create more and better test data. Maybe even real election data.
    \item Test more election methods
    \item Since all code is open source, anyone can freely copy and modify it to further build on the work presented in this paper.
    \item The implementations provided in this paper can also be used for other projects such as online voting websites.
\end{itemize}

\end{frame}

\end{document}

### 2017-05-19 generator/index.ts
Created gh-branch

@@ -1,21 +1,0 @@
-/*
-    By Adrian Salamon
-*/
-
-import { Ideology, IdeologyWithProbabilities } from './interfaces'
-import { createCandidates, assignProbabilityToIdeology } from './candidates'
-import { createAllBallots } from './ballots'
-
-
-export function generateBallots(ideologies: IdeologyWithProbabilities[], numberOfBallots: number): number[][] {
-
-    const result = createAllBallots(ideologies, numberOfBallots)
-    
-    return result
-}
-
-export function createIdeologyProbabilities(ideologies: Ideology[], numberOfCandidates: number): IdeologyWithProbabilities[] {
-    const candidates = createCandidates(numberOfCandidates, ideologies)
-
-    return assignProbabilityToIdeology(ideologies, candidates)
-}

### 2017-05-22 paper/images/tree.tex
Final touches on the paper

\begin{tikzpicture}[]

\node [align=left,circle, draw](A) at (0,0) {candidate: 0 \\ votes: 38};
\node [align=left,circle, draw](B) at (3.5,0) {candidate: 1 \\ votes: 17};
\node [align=left,circle, draw](C) at (7,0) {candidate: 2 \\ votes: 22};

\node [align=left,circle, draw,] (Aa) at (-1.6,-2.5) {\footnotesize candidate: 1 \\ \footnotesize votes: 11};
\node [align=left,circle, draw,] (Ab) at (0.1,-2.6) { };
\node [align=left,circle, draw,] (Ac) at (0.7,-2.6) { };
\node [align=left,circle, draw,] (Ad) at (1.3,-2.6) { };

\node [align=left,circle, draw,] (Ba) at (2.6,-2.6) { };
\node [align=left,circle, draw,] (Bb) at (3.2,-2.6) { };
\node [align=left,circle, draw,] (Bc) at (3.8,-2.6) { };
\node [align=left,circle, draw,] (Bd) at (4.4,-2.6) { };

\node [align=left,circle, draw,] (Ca) at (6.1,-2.6) { };
\node [align=left,circle, draw,] (Cb) at (6.7,-2.6) { };
\node [align=left,circle, draw,] (Cc) at (7.3,-2.6) { };
\node [align=left,circle, draw,] (Cd) at (7.9,-2.6) { };

\node [align=left,circle, draw,] (Aaa) at (-1,-4.5) { };
\node [align=left,circle, draw,] (Aab) at (-1.6,-4.5) { };
\node [align=left,circle, draw,] (Aac) at (-2.2,-4.5) { };

\draw (A) -- (Aa);
\draw (A) -- (Ab);
\draw (A) -- (Ac);
\draw (A) -- (Ad);

\draw (B) -- (Ba);
\draw (B) -- (Bb);
\draw (B) -- (Bc);
\draw (B) -- (Bd);

\draw (C) -- (Ca);
\draw (C) -- (Cb);
\draw (C) -- (Cc);
\draw (C) -- (Cd);

\draw (Aa) -- (Aaa);
\draw (Aa) -- (Aab);
\draw (Aa) -- (Aac);

\end{tikzpicture}

### 2017-05-22 paper/paper.tex
Final touches on the paper

--- 2017-05-14 paper/paper.tex
@@
 They range from simple processes that everyone can understand to complex mathematical systems.
-This essay examines differences and similarities of the behavior of three voting methods: the Single Transferable Vote (STV), first-past-the-post (FPTP), and Schulze Method.
-This is done by implementing each voting method in Typescript and then running election data into them.
+This essay examines differences and similarities of the behavior of three voting methods: the single transferable vote (STV), first-past-the-post (FPTP), and Schulze method.
+This is done by implementing each voting method in Typescript, a programming language, and then running election data into them.
 This paper provides descriptions, pseudocode and implementations of each method.
@@
 The methods are evaluated in both singe-seat and multi-seat elections.
-No revolutionary results are presented, but the behavior of each method is evaluated experimentally.
+No new findings are presented, but the behavior of each method is evaluated experimentally.
 Several conclusions are drawn about the behavior of the methods, including to what degree the different methods provided proportionate results.
 \end{abstract}
-\renewcommand{\abstractname}{Referat}
+\renewcommand{\abstractname}{Sammanfattning}
 \pagebreak
@@
 Denna uppsats undersöker skillnader och likheter mellan tre valsystem: Enkel Överförbar Röst, Majoritetsval och Schulze-metoden.
-Detta genom att implementera alla valsystem i Typescript och testa de med olika valdata.
+Detta genom att implementera alla valsystem i programmeringsspråket Typescript och testa de med olika valdata.
 Denna uppsats innehåller beskrivningar, pseudokod samt implementationer för alla valsystem.
@@
 Valsystemen testades i både enmans- och flermansval.
-Inga revolutionerande resultat presenteras, men varje systems beteende undersökts experimentellt.
+Inga nya upptäckter presenteras, men varje systems beteende undersökts experimentellt.
 Flera slutsatser dras från de olika systemens beteende, inklusive hur proportionella resultat systemen producerade.
@@
 \subsection{Purpose}
-The purpose of this essay is to evaluate differences and similarities in terms of election results in three different voting systems: Single Transferable Vote (STV), First-Past-The-Post (FPTP) and the Schulze Method.
+The purpose of this essay is to evaluate differences and similarities in terms of election results in three different voting systems: single transferable vote (STV), first-past-the-post (FPTP) and the Schulze method.
 This paper will only be examining and discussing differences and similarities in the results of the methods, not touching on how practically feasible the methods might be in actual elections.
@@
 All voting algorithms have been implemented in Typescript – mostly due to the author having previous experience with JavaScript.
-Typescript is a superset of JavaScript with multiple extra features.
+Typescript is a programming language developed my Microsoft.
+The language is superset of JavaScript with multiple extra features.
 Most importantly, Typescript has optional static type checking.
-Sample code written in Typescript can be seen in code example~\ref{lst:typescript example}.
+Sample code written in Typescript can be seen in Code Example~\ref{lst:typescript example}.
 The full source code with instructions for how to run the code can be found in Appendix~\ref{sec:conde implementation}.
-\codeblock{code/typescriptexample.ts}{lst:typescript example}{Basic Typescript syntax}
+\codeblock{code/typescriptexample.ts}{lst:typescript example}{Basic Typescript syntax.}
 \subsection{Modeling test data}
@@
 The program used for this purpose in this paper is highly primitive, as modeling preferences within a population is far beyond the scope of this paper.
-The full ballot generation program can be found in the \Code{/generator} folder.
-The goal of the program is to produce ballots that rank every candidate in order of preference (see figure~\ref{fig:stv ballot} on page~\pageref{fig:stv ballot}).
+The full ballot generation program can be found in the \Code{generator/} folder.
+The goal of the program is to produce ballots that rank every candidate in order of preference (see Figure~\ref{fig:stv ballot} on page~\pageref{fig:stv ballot}).
 The program incorporates the idea of an \textit{ideology} where each candidate is assigned one.
@@
 A single configuration object is used to create all ideologies.
-\codeblock{code/generator/ideologyConfig.ts}{lst:ideology configuration}{Configuration object for creating ideologies}
+\codeblock{code/generator/ideologyConfig.ts}{lst:ideology configuration}{Configuration object for creating ideologies.
+Allows for changing the variables to produce different types of electorates and election circumstances.
+Used to test the methods in different circumstances.}
 The program then works via 4 major steps:
@@
 This means that the general spread of votes between candidates will be even.
-An example of the distribution of first-preference votes generated in this scenario can be seen in figure~\ref{fig:example of scenario 1}.
-The full configuration object can be seen in code example~\ref{lst:scenario 1}.
-\codeblock{code/generator/scenario1.ts}{lst:scenario 1}{Configuration object for scenario 1}
+An example of the distribution of first-preference votes generated in this scenario can be seen in Figure~\ref{fig:example of scenario 1}.
+The full configuration object can be seen in Code Example~\ref{lst:scenario 1}.
+\codeblock{code/generator/scenario1.ts}{lst:scenario 1}{Configuration object for scenario 1. It features 8 candidates, 1 seat to be elected, and a relatively even spread of votes.}
 \begin{figure}[H]
@@
 The parameters are set to produce a ``normal'' spread of votes between candidates.
-An example distribution of first-preference votes generated in this scenario can be seen in figure~\ref{fig:example of scenario 2}.
-The full configuration can be seen in code example~\ref{lst:scenario 2}.
-\codeblock{code/generator/scenario2.ts}{lst:scenario 2}{Scenario 2}
+An example distribution of first-preference votes generated in this scenario can be seen in Figure~\ref{fig:example of scenario 2}.
+The full configuration can be seen in Code Example~\ref{lst:scenario 2}.
+\codeblock{code/generator/scenario2.ts}{lst:scenario 2}{Configuration object for scenario 2. It features 9 candidates, 3 seats to be elected, and a ``normal'' spread of votes.}
 \begin{figure}[H]
@@
 \label{sec:method-scenario3}
-The second scenario elects 3 candidates out of 9 total.
+The third scenario elects 3 candidates out of 9 total.
 It features a steep spread of votes between candidates.
-An example distribution of first-preference votes generated in this scenario can be seen in figure~\ref{fig:example of scenario 3}.
-The full configuration can be seen in code example~\ref{lst:scenario 3}.
-\codeblock{code/generator/scenario3.ts}{lst:scenario 3}{Scenario 3}
+An example distribution of first-preference votes generated in this scenario can be seen in Figure~\ref{fig:example of scenario 3}.
+The full configuration can be seen in Code Example~\ref{lst:scenario 3}.
+\codeblock{code/generator/scenario3.ts}{lst:scenario 3}{Configuration object for scenario 3. It features 9 candidates, 3 seats to be elected, and a steep spread of votes.}
 \begin{figure}[H]
@@
 The standard deviation of the outcomes represents the variance in outcome due to the pseudorandom nature of the generator program outlined in Section~\ref{sec:vote-generation}.
-The standard deviation is calculated according to equation~\ref{eq:standard-deviation}.
+The standard deviation is calculated according to Equation~\ref{eq:standard-deviation}.
 \begin{equation}
@@
 Each voter has one vote that may be allocated to any candidate.
-In a FPTP election the N candidates with most votes get elected \autocite{wilkinson2017}.
+In a FPTP election the N candidates with most votes get elected.
+\autocite{wilkinson2017}
 \subsubsection{Justification}
@@
 \subsubsection{Implementation}
-The first-past-the-post program is implemented in a single file (\Code{/fptp/index.ts}). The inputs of the program can be seen in code example~\ref{lst:fptp inputs}.
-\codeblock{code/fptp/inputs.ts}{lst:fptp inputs}{Inputs for FPTP program}
+The first-past-the-post program is implemented in a single file (\Code{fptp/index.ts}). The inputs of the program can be seen in Code Example~\ref{lst:fptp inputs}.
+\codeblock{code/fptp/inputs.ts}{lst:fptp inputs}{Inputs for FPTP program.}
 The program sums all the first-preference votes for each candidate and elects the ones with most votes, in accordance with specified amount of seats.
@@
 \subsubsection{Description}
-The Single Transferable Vote (STV) is a more complicated voting system than the first-past-the-post method \autocite{electotal-reform-society2015}.
+The single transferable vote (STV) is a more complicated voting system than the first-past-the-post method.
 STV is a multi-seat election method, although it can be used for single-seat elections too.
@@
 For the sake of simplicity, all candidates must be ranked at unique and linear values in this implementation.
-An example of an STV ballot can be seen in figure~\ref{fig:stv ballot}.
+An example of an STV ballot can be seen in Figure~\ref{fig:stv ballot}.
 By having voters convey more information in a ballot, there is more data available that the method can take advantage of.
+\autocite{electotal-reform-society2015}
 \begin{figure}
 	\centering
-	\includegraphics[height=140px]{ballot}
-	\caption{Sample STV ballot}
+	\input{images/ballot.tex}
+	\caption{Sample STV ballot. A voter fills in all candidates in order of preference.}
 \label{fig:stv ballot}
@@
 
-Using this data, votes are transferred between candidates within a ballot, hence the name Single Transferable Vote.
+Using this data, votes are transferred between candidates within a ballot, hence the name single transferable vote.
 The method relies on the concept of a quota, which is the number of votes one needs to be elected.
@@
 If there still are seats yet to be filled, the candidate with fewest votes is eliminated and his/her votes are transferred to the next choice on the ballots which supported the candidate.
-This process is repeated until all seats are filled \autocite{king200}.
+This process is repeated until all seats are filled.
 The process can become quite complex with many ballots and transferring of fractional votes.
 A computer is therefore essential to resolve large scale elections.
+\autocite{king200}
 \subsubsection{Justification}
@@
 Every candidate is a top-level node with an attribute showing the number of current votes for the candidate.
-Each node has child nodes representing the next preferences of the voters for that particular candidate, see figure~\ref{fig:tree structure}.
+Each node has child nodes representing the next preferences of the voters for that particular candidate, see Figure~\ref{fig:tree structure}.
 It is easy to manipulate branches via recursive functions.
@@
 	\centering
-	\includegraphics[height=200px]{Tree}
-	\caption{Simplified and shortened version of the tree structure. Each candidate is a top-level node with children, signifying the preferences of the voters for that candidate.}
+	\input{images/tree.tex}
+	\caption{Simplified and shortened version of the tree structure.
+Each candidate is a top-level node with child-nodes, signifying the next preferences of the voters for that candidate.
+The tree represents the full state of the election.}
 \label{fig:tree structure}
 \end{figure}
-\codeblock{code/stv/candidateNode.ts}{lst:stv candidate node}{The CandidateNode class}
+\codeblock{code/stv/candidateNode.ts}{lst:stv candidate node}{The CandidateNode class. Includes a list of child nodes and methods to manipulate the node.}
 With the \Code{add()} and \Code{multiply()} functions it is possible to recursively modify branches.
@@
 Both functions rely on the \Code{distribute()} function which is used to distribute a set of nodes onto the tree.
-\codeblock{code/stv/distribute.ts}{lst:stv distribute function}{The distribute function}
+\codeblock{code/stv/distribute.ts}{lst:stv distribute function}{The distribute function. Main method used to manipulate the state of the election.}
 In order to eliminate and transfer surplus votes from any candidate node $A$, the children of $A$ are passed into the distribute function.
 In the case of transferring surplus votes, the votes for each child node is first multiplied by $\frac{\text{surplus votes}}{\text{total votes}}$ as outlined in the pseudocode in Section~\ref{alg:stv psuedocode}.
-The full source code for functions that manipulate the tree structure can be found in \Code{/stv/tree.ts}.
+The full source code for functions that manipulate the tree structure can be found in \Code{stv/tree.ts}.
 The main process of the program is found in the \Code{stv/election.ts} file and runs the process defined in the pseudocode in Section~\ref{alg:stv psuedocode} on page~\pageref{alg:stv psuedocode}.
@@
 \subsubsection{Description}
-The Schulze Method is a method used mainly to determine results in single-winner elections but can also be used to provide rankings and elect multiple candidates in a single election \autocite{Schulze2011}.
-Ballots are identical to those of the Single Transferable Vote (see figure~\ref{fig:stv ballot} on page~\pageref{fig:stv ballot}).
-The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate  \autocite{johnson2005}.
-As mentioned, this method relies on comparing the preferences of every candidate to one another as shown in table~\ref{tab:pairwise comparison matrix}.
+The Schulze method is a method used mainly to determine results in single-winner elections but can also be used to provide rankings and elect multiple candidates in a single election.
+Ballots are identical to those of the single transferable vote (see Figure~\ref{fig:stv ballot} on page~\pageref{fig:stv ballot}).
+The method is compliant with the Condorcet Criterion, which means that if there is a candidate who the majority prefers in a pairwise comparison with every other candidate, that candidate will win  As mentioned, this method relies on comparing the preferences of every candidate to one another as shown in Table~\ref{tab:pairwise comparison matrix}.
 If there is a Condorcet winner the process is simple: declare the Condorcet winner a winner and run another iteration without that candidate.
@@
 However, there can be Condorcet ties, where there is no Condorcet winner.
-There are multiple methods used for resolving Condorcet ties, with one of them being the Schulze Method.
+There are multiple methods used for resolving Condorcet ties, with one of them being the Schulze method.
+\autocite{johnson2005}
 
-The Schulze Method resolves ties by investigating possible paths between candidates.
-For example, if out of a total of 50 ballots 30 ballots prefer $B>A$, 28 ballots prefer $A>C$ and 27 ballots prefer $C>B$, a path from $A$ to $B$ can be created by going $A \rightarrow C \rightarrow B$.
+The Schulze method resolves ties by investigating possible paths between candidates.
+For example, if out of a total of 50 ballots 30 ballots prefer $B>A$ ($A$ over $B$), 28 ballots prefer $A>C$ and 27 ballots prefer $C>B$, a path from $A$ to $B$ can be created by going $A \rightarrow C \rightarrow B$.
 The path is said to have the $strength$ of the weakest link in the path.
@@
 By finding the strongest path between all nodes a result can be obtained where $p[X,Y] \geq p[Y,X]$ which means that candidate $X$ wins.
-The Schulze Method also provides a linear ranking between all candidates, for example that $E > B > A > C > D$.
+The Schulze method also provides a linear ranking between all candidates, for example that $E > B > A > C > D$.
 By selecting the $N$ top candidates one can use the method for a multi-seat election.
 As the process can become very complex as the number of candidates grow, a computer is needed to resolve large elections.
+\autocite{Schulze2011}
 
@@
 An efficient and relatively simple way to compute this problem is via the Floyd-Warshall algorithm which is used in the implementation \autocite{wikipedia2017warshall}.
-See Code Example~\ref{lst:schulze algorithm} for the full algorithm.
+See Code Example~\ref{lst:schulze algorithm} on page~\pageref{lst:schulze algorithm} for the full algorithm.
 
@@
 \centering
-\caption{Pairwise comparison matrix used in the Schulze method. For example, 17 ballots prefer $A>B$ and 33 ballots prefer $B>A$.}
+\caption{Pairwise comparison matrix used in the Schulze method. $d$[$X$,$Y$] detonates the number of ballots that prefer candiate $X$ over $Y$.}
 \begin{tabular}{l|c|c|c|c|c|}
 \cline{2-6}
- & \multicolumn{1}{l|}{A} & \multicolumn{1}{l|}{B} & \multicolumn{1}{l|}{C} & \multicolumn{1}{l|}{D} & \multicolumn{1}{l|}{E} \\ \hline
-\multicolumn{1}{|l|}{A} & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}17 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{DDFFDD}35 & \cellcolor[HTML]{DDFFDD}30 \\ \hline
-\multicolumn{1}{|l|}{B} & \cellcolor[HTML]{DDFFDD}33 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}24 & \cellcolor[HTML]{DDFFDD}47 & \cellcolor[HTML]{DDFFDD}36 \\ \hline
-\multicolumn{1}{|l|}{C} & \cellcolor[HTML]{DDFFDD}36 & \cellcolor[HTML]{DDFFDD}26 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{DDFFDD}40 & \cellcolor[HTML]{DDFFDD}42 \\ \hline
-\multicolumn{1}{|l|}{D} & \cellcolor[HTML]{FFDDDD}15 & \cellcolor[HTML]{FFDDDD}3 & \cellcolor[HTML]{FFDDDD}10 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}18 \\ \hline
-\multicolumn{1}{|l|}{E} & \cellcolor[HTML]{FFDDDD}20 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{FFDDDD}8 & \cellcolor[HTML]{DDFFDD}32 & \cellcolor[HTML]{9B9B9B} \\ \hline
+ & \multicolumn{1}{l|}{\small $d$[$*$,$A$]} & \multicolumn{1}{l|}{\small $d$[$*$,$B$]} & \multicolumn{1}{l|}{\small $d$[$*$,$C$]} & \multicolumn{1}{l|}{\small $d$[$*$,$D$]} & \multicolumn{1}{l|}{\small $d$[$*$,$E$]} \\ \hline
+\multicolumn{1}{|l|}{\small $d$[$A$,$*$]} & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}17 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{DDFFDD}35 & \cellcolor[HTML]{DDFFDD}30 \\ \hline
+\multicolumn{1}{|l|}{\small $d$[$B$,$*$]} & \cellcolor[HTML]{DDFFDD}33 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}24 & \cellcolor[HTML]{DDFFDD}47 & \cellcolor[HTML]{DDFFDD}36 \\ \hline
+\multicolumn{1}{|l|}{\small $d$[$C$,$*$]} & \cellcolor[HTML]{DDFFDD}36 & \cellcolor[HTML]{DDFFDD}26 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{DDFFDD}40 & \cellcolor[HTML]{DDFFDD}42 \\ \hline
+\multicolumn{1}{|l|}{\small $d$[$D$,$*$]} & \cellcolor[HTML]{FFDDDD}15 & \cellcolor[HTML]{FFDDDD}3 & \cellcolor[HTML]{FFDDDD}10 & \cellcolor[HTML]{9B9B9B} & \cellcolor[HTML]{FFDDDD}18 \\ \hline
+\multicolumn{1}{|l|}{\small $d$[$E$,$*$]} & \cellcolor[HTML]{FFDDDD}20 & \cellcolor[HTML]{FFDDDD}14 & \cellcolor[HTML]{FFDDDD}8 & \cellcolor[HTML]{DDFFDD}32 & \cellcolor[HTML]{9B9B9B} \\ \hline
 \end{tabular}
@@
 \subsubsection{Implementation}
-The Schulze Method is implemented within the file \Code{schulze/index.ts}.
+The Schulze method is implemented within the file \Code{schulze/index.ts}.
 It takes two inputs: a list of ballots and the number of seats to be elected.
@@
 Data representation can be seen in Code Example~\ref{lst:schulze-maps}.
-\codeblock{code/schulze/maps.ts}{lst:schulze-maps}{Data representation}
-The program then runs the algorithm outlined in the pseudocode in Section~\ref{alg:schulze psuedocode}.
-\codeblock{code/schulze/algorithm.ts}{lst:schulze algorithm}{Main algorithm}
-\section{Evaluation of results}
+\codeblock{code/schulze/maps.ts}{lst:schulze-maps}{Data representation in the Schulze algorithm.}
+The program uses these inputs and runs the algorithm outlined in the pseudocode in Section~\ref{alg:schulze psuedocode}.
+The Typescript implementation of this algorithm is detailed in Code Example~\ref{lst:schulze algorithm}.
+\codeblock{code/schulze/algorithm.ts}{lst:schulze algorithm}{Main algorithm for calculating the outcome in the Schulze method. Variant of the Floyd-Warshall algorithm.}
+\section{Results}
 \subsection{Scenario 1}
@@
 This means that there is not an obvious winner present.
-This can be seen from the first-preference votes in the scenario seen in figure~\ref{fig:example of scenario 1} on Page~\pageref{fig:example of scenario 1}.
-The full result in this scenario can be seen in figure~\ref{fig:scenario 1 results}.
+This can be seen from the first-preference votes in the scenario seen in Figure~\ref{fig:example of scenario 1} on page~\pageref{fig:example of scenario 1}.
+The full result in this scenario can be seen in Figure~\ref{fig:scenario 1 results}.
 The outlier in this scenario seems to be the FPTP method, electing candidate 0 more often than both other methods.
-Key metrics for the results in this scenario can be found in table~\ref{tab:scenario 1 result}.
+Key metrics for the results in this scenario can be found in Table~\ref{tab:scenario 1 result}.
 The misrepresentation metric show that FPTP is not entirely representative.
@@
 	\end{tikzpicture}
-	\caption{Results in scenario 1}
+	\caption{Results in scenario 1.}
 \label{fig:scenario 1 results}
@@
 \centering
-\caption{Key metrics for result in scenario 1}
+\caption{Key metrics for result in scenario 1.}
 \label{tab:scenario 1 result}
@@
 Scenario 2 featured nine candidates of which three were to be elected.
-The distribution of votes was ``normal'', and as seen in figure~\ref{fig:example of scenario 2} on page~\ref{fig:example of scenario 2}, the election is very close with many candidates having a similar percentage of first-preference votes.
-The results obtained in scenario 2 are very interesting.
-FPTP tended to underrepresent candidate 1, and elected a candidate from ideology 2 only in 28\% of elections, despite the ideology theoretically having 30\% of popular support.
+The distribution of votes was ``normal'', and as seen in Figure~\ref{fig:example of scenario 2} on page~\pageref{fig:example of scenario 2}, the election is very close with many candidates having a similar percentage of first-preference votes.
+In this scenario, FPTP tended to underrepresent candidate 1, and elected a candidate from ideology 2 only in a minority of elections, despite the ideology theoretically having 30\% of popular support.
 The Schulze method also tended to underrepresent ideology 2.
-It instead overrepresented ideology 3, electing 3 candidates of ideology 3 in 50\% of elections.
-This indicates that the Schulze method is not a representative method in a multi-seat election.
-The STV result showed less misrepresentation than the FPTP result, which was to be expected since the method has access to more data of any voter's preferences.
-The results in scenario 2 can be observed in figure~\ref{fig:scenario 2 result} and the key metrics can be seen in table~\ref{tab:scenario 2 result}.
+It instead overrepresented ideology 3, electing 3 candidates of ideology 3 in half of the elections.
+The STV result showed less misrepresentation than the FPTP result.
+The results in scenario 2 can be observed in Figure~\ref{fig:scenario 2 result} and the key metrics can be seen in Table~\ref{tab:scenario 2 result}.
 \begin{table}[H]
 \centering
-\caption{Key metrics for result in scenario 2}
+\caption{Key metrics for result in scenario 2.}
 \label{tab:scenario 2 result}
@@
 	\end{tikzpicture}
-	\caption{Results in scenario 2}
+	\caption{Results in scenario 2.}
 \label{fig:scenario 2 result}
@@
 % [ 418.13628234977, 388.17206952015, 393.25535950293 ]
-\subsection{Scenario 3}
+\subsection{Scenario 3} 50\%
 \label{sec:resuls-scenario3}
@@
 The distribution of votes was  ``steep''.
-This can be seen by the first-preference votes in figure~\ref{fig:example of scenario 3} on Page~\pageref{fig:example of scenario 3}.
+This can be seen by the first-preference votes in Figure~\ref{fig:example of scenario 3} on page~\pageref{fig:example of scenario 3}.
 The results obtained with each method in this scenario are practically identical.
-From this, it can be inferred that the results of the methods converge as the preferences in a population become more clear.
-The results obtained in this scenario can be seen in figure~\ref{fig:scenario 3 result}.
-The key metrics can be found in table~\ref{tab:scenario 3 result}.
+The results from this scenario can be seen in Figure~\ref{fig:scenario 3 result}.
+The key metrics can be found in Table~\ref{tab:scenario 3 result}.
 \begin{table}[H]
 	\centering
-	\caption{Key metrics for result in scenario 3}
+	\caption{Key metrics for result in scenario 3.}
 \label{tab:scenario 3 result}
@@
 	\end{tikzpicture}
-	\caption{Results in scenario 3}
+	\caption{Results in scenario 3.}
 \label{fig:scenario 3 result}
 \end{figure}
-\section{Conclusion}
+\section{Discussion}
 The results obtained in the three different scenarios provide some insight into the varying properties of the different voting systems.
@@
 While the testing method used in this paper may not have been the most robust way of comparing the voting methods, several conclusions can be drawn from the data.
-They are outlined in 4 points below.
+They are outlined in 5 points below.
 \begin{enumerate}
@@
 
-	As seen from the results obtained in scenario 2, which can be seen in Section~\ref{sec:resuls-scenario2}, the Schulze Method heavily overrepresented candidates from ideology 1 (candidates 3, 5 \& 7).
+	As seen from the results obtained in scenario 2, which can be seen in Section~\ref{sec:resuls-scenario2}, the Schulze method heavily overrepresented candidates from ideology 1 (candidates 3, 5 \& 7).
 While ideology 1 in fact was the most popular ideology, a more proportionate way of representing the electorate in the scenario would have been to grant one seat to each ideology.
 The Schulze tended to elect candidates from the strongest ideology only, instead of electing candidates from all ideologies in a more proportionate manner.
-This is not a problem in a single-seat election, as can be seen in the results of scenario 1 in Section~\ref{sec:resuls-scenario1}, which was a single-seat elections, where the Schulze Method simply elected the most popular candidate.
+This is not a problem in a single-seat election, as can be seen in the results of scenario 1 in Section~\ref{sec:resuls-scenario1}, which was a single-seat elections, where the Schulze method simply elected the most popular candidate.
 	\item In single-seat elections, Schulze and STV (and IRV in extension) seemed to provide similar results.
@@
 	FPTP preformed considerably worse at being representative than the other methods.
-This was true for both close single- and multi-seat elections, excluding The Schulze Method in scenario 2 (see Point~\ref{num:conclusion-schulze}).
-At the core, both the STV and Schulze Method have more data to use for determining winners than what FPTP does.
+This was true for both close single- and multi-seat elections, excluding The Schulze method in scenario 2 (see point~\ref{num:conclusion-schulze}).
+At the core, both the STV and Schulze method have more data to use for determining winners than what FPTP does.
 The FPTP method only has access to first-preference votes which does not convey as much information as a ballot listing all candidates in order of preference does.
@@
 STV is the only multi-seat proportional voting system tested in this paper, and the results obtained reinforce its position as just that.
+	\item In elections where the population has clear preferences, the three methods provide similar results.
+
+	In election scenario 3, from which results can be seen in Section~\ref{sec:resuls-scenario3}, the three methods tested produced identical results.
+This scenario feautred a steep spread of votes wich meant that the preferences of the population were very clear.
+This can be seen from the distribution of first-preference votes in this scenario, seen in Figure~\ref{fig:example of scenario 3} on page \pageref{fig:example of scenario 3}.
+From this, it can be inferred that the results from the different methods converge as the electorate has clearer preferences.
 \end{enumerate}
-While there is no perfect voting system, they all preform differently.
+While there is no perfect voting system, they all perform differently.
 From the conclusions outlined above, a decision can be taken about what system analyzed in this paper to be used.
 Generally, if a proportional representation is desired (which in a democracy it usually is), STV will likely be the most appropriate method to use.
-In single-seat elections, the Schulze Method should also be considered.
+In single-seat elections, the Schulze method should also be considered.
 FPTP is the simplest method to both use and understand, but cannot be considered a proportionate voting method.
@@
 }
-\caption{Project structure}
+\caption{Project structure.}
 \label{fig:project-structure}
@@
 It is open sourced under the MIT License.
-In order to run any of the implementations, the Typescript files (\Code{.ts}) need to be compiled to JavaScript files (\Code{.js}) using the Typescript Compiler.
+In order to run any of the implementations, the Typescript files (\Code{.ts}) need to be compiled to JavaScript files (\Code{.js}) using the Typescript Transpiler.
 Then the code can be executed using Node.js.

### 2017-05-22 paper/code/schulze/algorithm.ts

@@ -1,4 +1,4 @@
-// Computing strongest path strength. Variant of the Floyd-Warshall algorithm
+// Computing strongest path strength.
 for (var i = 0; i < c; i++) {
     for (var j = 0; j < c; j++) {
         if (i !== j) {

### 2017-05-22 paper/code/stv/distribute.ts

@@ -1,4 +1,4 @@
-// Distributes nodes onto the tree. Returns new tree.
+// Distributes a list of nodes onto the tree. Returns a new tree.
 function distribute(nodeList: CandidateNode[], tree: CandidateNode[], winners: number[]): CandidateNode[] {
     // Loops through each candidate node in the list
     for (let i = 0; i < nodeList.length; i++) {
